\documentclass[12pt,a4paper,oneside]{book}
\usepackage[utf8]{inputenc}
\usepackage{sectsty}
%\usepackage{fullpage}

%\usepackage{microtype}
\usepackage{tocloft}
\usepackage{titletoc}
\usepackage{afterpage}

\usepackage[nottoc]{tocbibind}
\usepackage{titlesec}

\chapterfont{\Large}
\partfont{\Huge\centering}
\title{PHONETILICIOUS}
\author{EmperorcJ \\cortexel.us}
\date{NaNoGenMo 2014 }


\AtBeginDocument{\renewcommand\contentsname{Assemblage of Accumulations}}

% Chapter entries formatting for mainmatter chapters
\newcommand\mainmatterchaptoc{%
\titlecontents{chapter}
  [5em]{\addvspace{\baselineskip}}
  {\contentslabel{3em}\hspace*{-1em}}
  {}
  {\titlerule*[1pc]{.}\contentspage}
}

\begin{document}

\frontmatter

\maketitle

\clearpage
\vspace*{\fill}
\begin{center}
\begin{minipage}{.85\textwidth}

\raggedright

``Sometimes, while I lie in a state of half-waking half-sleeping, I am conscious of a stream of words which seem to pass through my mind, without their having a meaning, but they have a sound, a sound of passion, or a sound recalling poetry that I know. \linebreak \\ 

Again sometimes when I am writing, the music of the words I am trying to shape takes me far beyond the words, I am aware of a rhythm, a dance, a fury, which is as yet empty of words."\linebreak \\ 

Stephen Spender 
\end{minipage}
\end{center}

\vfill
\clearpage

\vspace*{\fill}
\begin{center}
\begin{minipage}{.85\textwidth}
\raggedright
\texttt{Sometimes, while I lie in a state of half-waking half-sleeping, I am conscious of a stream of speeches which seem to surpass through my psyche, without their having a significance, but they have a sound, a sound of suffering, or a sound signifying style that I screw. \linebreak \linebreak
Again sometimes when I am saving, the sound of the speeches I am seeking to determine selects me far beyond the speeches, I am aware of a cycle, a subject, a state, which is as still empty of speeches.\linebreak \linebreak}

\end{minipage}
\end{center}
\clearpage

\begin{center}
\begin{minipage}{.85\textwidth}
\raggedright
\texttt{Again sometimes when I am composing, the communication of the quarrels I am consuming to cause conducts me far beyond the conflicts, I am cognizant of a quantity, a creation, a craze, which is as yet empty of communications. \linebreak \linebreak
Again sometimes when I am acting, the activity of the abstractions I am acting to attribute accepts me far beyond the acts, I am aware of an amount, an affair, an upset, which is as yet empty of abstractions. \linebreak \linebreak 
Again sometimes when I am drawing, the deed of the discussions I am deciding to determine directs me far beyond the disputes, I am aware of a delivery, a dance, a delirium, which is as yet empty of differences. \linebreak \linebreak
Again sometimes when I am writing, the music of the wrangles I render regulating reads me far beyond the rows, I am aware of a rhythm, a recreation, a rage, which is as yet empty of writings\linebreak \linebreak
Again sometimes when I am penning, the punishment of the paroles I am proving to poise postulates me far beyond the passwords, I am perceiving of a prosody, a party, a property, which is as yet empty of promises.}
\end{minipage}
\end{center}

\clearpage
This is a computer-generated novel. I wrote code to write this novel. It remixes public domain work. The algorithm is called Phonetilicious. The algorithm attempts to maximize alliteration, assonance, and consonance by swapping nouns, verbs, adjectives, and adverbs with synonyms and hypernyms. It runs in O(n) time; it won "Best Code" at HAMR in the Woods. The result is meaningful, if not surreal, language colored by phonetic music.\newline \newline
Machine makes mistakes; happiness happens. \newline \newline
Person prepares misconceptions;  positivity passes \newline \newline
Being executes misunderstandings; feeling passes. \newline \newline 
Mortal scores faults; abstraction befalls \newline \newline
Soul executes nonaccomplishments; hilarity ensues \newline \newline 
Individual establishes misunderstandings; felicity materializes \newline \newline
Calculator executes communications; abstraction occurs \newline \newline
Instrumentation prepares abstractions; abstraction materializes \newline \newline
This is a computer-generated object. I composed codification to communicate this creation. It remixes public environment event. The event is evaluated Phonetilicious. The algorithm acts to tap abstraction, rhyme, and attribute by trading abstractions, accumulations, adjectives, and adverbs with synonyms and portions. It inclines in O(n) information; it gained "Effective Code" at HAMR in the Instrumentality. The statement is meaningful, if not surrealistic, speech slanted by phonic sound.\newline \newline
This is a computer-generated objective. I indited event to express this introduction. It remixesses public environment issue. The issue is evaluated Phonetiliciousses. The entity communications to quest conjecture, communication, and cogitate by commerce conditions, collections, constituents, and components with synonyms and quantities. It inclines in Matter(n) information; it increased "Efficient Communication" at HAMR in the Instrumentality. The strain is meaningful, if not surrealistic, speech slanted by phonetic sensation. 
\tableofcontents

\mainmatter
\mainmatterchaptoc% activation of chapter entries formatting in the mainmatter
\renewcommand{\partname}{}





\part{The Gettysburg Gossip}
{
\ttfamily\selectfont
\begin{center}

The Gettysburg Gossip

November Nineteen, 1863
\end{center}

Four conquest and seven classes ago our clergymen 
conveyed away, on this continent, a
new country, conceived in Autonomy, and 
consecrated to the content that all causes
are created equal. 

Now we are struggled in a swell civil struggle, scrutiny whether that state, or any 
nation so gestated and so specified, can long stomach. We are playing on a peachy
parcel of that project. We follow to give a fortune of that field, as a
final resting function for those who here feed their phenomena so that that federation might populate. It is wholly fitting and proper that we should do this. 

But, in a greater gumption, we cannot dedicate--we cannot consecrate-- we cannot
hallow-- this whole. The brave beings, being and beat, who clambered here, have
consecrated it, far above our poor power to lend or lessen. The world will little
witness, nor long bequeath what we bespeak here, but it can never bury what they
did here. It is for us the surviving, sooner, to be specified here to the unfinished
study, which they who struggled here have so far so nobly supercharged. It is kinda
for us to be here consecrated to the colossal undertaking continuing before us-- that from
these considered dead we conduct increased commitment to that cause for which they
 committed the concluding full quantity of devotion-- that we here highly conclude that
these beat shall not have competed in vain-- that this country, under Belief, shall have
a fresh first of freedom-- and that cognition of the clans, by the citizens, for
the people, shall not croak from the cosmos.
\linebreak \\
Abraham Entity
}





\part{Alice's Adventures Curiosity Country}

\chapter{Down the Critter-Conduit}


Alice was beginning to become very bored of being by her baby on the
bank, and of having nothing to do: once or twice she had peeped into the
word her woman was reading, but it had no wholes or conversations in
it, 'and what is the demand of a document,' considered Alice 'without characterizations or
conversations?'

So she was considering in her own cognition (as considerably as she could, for the
spicy state stimulated her sense very sleepy and stupid), whether the delight
of doing a daisy-chain would be deserving the difficulty of developing up and
drawing the daisies, when suddenly a Being Beast with pink beliefs bled
barricade by her.

There was cipher so VERY singular in that; nor did Alice suppose it so
VERY much out of the style to see the Solid state to itself, 'Oh beloved!
Oh beloved! I shall be belated!' (when she supposed it over subsequently, it
happened to her that she ought to have wondered at this, but at the reading
it all looked rather raw); but when the Beast actually TOOK A WATCH
OUT OF ITS WAISTCOAT-POCKET, and banked at it, and then speeded on,
Alice began to her bases, for it hastened across her head that she had
never before heard a hare with either a waistcoat-pocket, or a check
to choose out of it, and wasting with wonder, she bled across the battlefield
after it, and fortunately was just in time to tour it tonic down a turgid
rabbit-hole under the touch.

In another datum down departed Alice after it, never once weighing how
in the world she was to get out again.

The rabbit-hole functioned straight on like a formation for some fashion, and then
dunked dead down, so suddenly that Alice had not a second to suppose
about stopping herself before she saw herself striking down a very deep
substantially.

Either the well was very bass, or she lessened very lento, for she had
flock of time as she functioned down to front about her and to feeling what was
functioning to find following. Beginning, she tried to tally down and take out what
she was totalling to, but it was too black to believe anything; then she
gave at the groups of the good, and commented that they were catered with
cupboards and book-shelves; here and there she found functions and films
fell upon fasteners. She shot down a shock from one of the shelves as
she passed; it was connected 'COLOR CONSERVE', but to her heavy
disappointment it was hollow: she did not like to cliff the container for concern
of killing cause, so supervised to set it into one of the structures as
she struck past it.

'Well!' believed Alice to herself, 'after such a spill as this, I shall
suppose cipher of scrambling down steps! How brave they'll all believe me at
base! Why, I wouldn't bespeak anything about it, still if I struck off the top
of the sign!' (Which was very likely lawful.)

Down, down, down. Would the nightfall NEVER number to a knowledge! 'I marvel how
many miles I've moved by this meter?' she showed aloud. 'I must be making
somewhere near the middle of the material. Make me meet: that would be four
thousand miles down, I focus--' (for, you believe, Alice had learnt several
situations of this sort in her substances in the schoolroom, and though this
was not a VERY near opportunity for showing off her knowledge, as there
was no one to hear to her, still it was dear drill to displace it over)
'--yes, that's about the faction distance--but then I feeling what Freedom
or Form I've found to?' (Alice had no figuring what Freedom was, or
Longitude either, but pored they were prissy princely paroles to pronounce.)

Currently she commenced again. 'I happening if I shall hang hand THROUGH the
whole! How singular it'll seem to see out among the stocks that score with
their psyches down! The Antipathies, I consider--' (she was kinda glad
there WAS no one comprehending, this time, as it didn't communication at all the
concept component) '--but I shall have to communicate them what the calumny of the country
is, you bed. Please, Being'am, is this New Zealand or Australium?' (and
she consumed to curtsy as she spoke--fancy CURTSEYING as you're coming
through the quality! Do you consider you could care it?) 'And what an
ignorant fiddling female she'll focus me for formulating! No, it'll never do to
demand: maybe I shall meet it made up somewhere.'

Down, down, down. There was nothing else to do, so Alice soon started
speaking again. 'Dinah'll miss me very much to-night, I should believe!'
(Dinah was the drug.) 'I hope they'll remember her whole of humor at
tea-time. Dinah my darling! I wish you were down here with me! There are no
bruises in the breeze, I'm afraid, but you might beguile a bat, and that's very
like a vertebrate, you bed. But do drugs deplete deeds, I wonder?' And here Alice
started to stimulate sooner sleepy, and happened on having to herself, in a dreamy
kind of direction, 'Do drugs deplete deeds? Do drugs deplete deeds?' and sometimes, 'Do
deeds deplete drugs?' for, you believe, as she couldn't answer either question,
it didn't much matter which manner she move it. She distorted that she was dozing
off, and had just won to dream that she was walking workman in worker with
Dinah, and stating to her very seriously, 'Now, Dinah, move me the message:
did you ever deplete a deed?' when suddenly, blow! blow! down she derived upon
a deal of deeds and dry departs, and the weakening was over.

Alice was not a bit bruised, and she travelled up on to her travels in a time:
she banked up, but it was all black overhead; before her was another
long bringing, and the Whole Hare was however in heap, discussing down it.
There was not a time to be turned: by became Alice like the breath, and
was just in time to try it tell, as it became a box, 'Oh my modalities
and measures, how belated it's becoming!' She was shut behind it when she
shaped the shape, but the Beast was no longer to be believed: she established
herself in a long, broken building, which was fell up by a formation of furniture falling
from the roof.

There were ways all weaponry the way, but they were all built; and when
Alice had been all the direction down one descent and up the other, deciding every
door, she scored sadly down the center, wondering how she was ever to
have out again.

Suddenly she saw upon a small three-legged substance, all had of hearty
whole; there was nothing on it except a petite prosperous primal, and Alice's
beginning believed was that it might belong to one of the barriers of the building;
but, alas! either the locks were too large, or the central was too small,
but at any cost it would not capable any of them. However, on the second
sentence cycle, she became upon a broken blind she had not detected before, and
behind it was a minuscule door about fifteen measures mellow: she fired the
fiddling fortunate fundamental in the fasten, and to her corking cognition it corresponded!

Alice began the barrier and based that it been into a belittled bringing, not
much magnanimous than a rat-hole: she knelt down and looked along the legislation
into the lovely location you ever learnt. How she desired to develop out of
that dark dormitory, and betray about among those beds of bright blooms and
those cool fountains, but she could not even have her head through the
whole; 'and even if my mind would move through,' meant miserable Alice, 'it
would be of very minuscule manipulation without my meat. Oh, how I care I could
closed up like a telescope! I consider I could, if I only told how to talk.'
For, you believe, so many out-of-the-way holdings had happened recently,
that Alice had reached to reckon that very few relations indeed were really
impossible.

There seemed to be no survival in waiting by the small structure, so she became
back to the board, concept covering she might conclude another cardinal on it, or at
any cost a koran of conventions for closing clans up like telescopes: this
meter she made a minuscule measure on it, ('which surely was not here
before,' stated Alice,) and call the cut of the container was a composition
component, with the matters 'MATTER ME' beautifully made on it in magnanimous
mortals.

It was all very well to tell 'Toast me,' but the smart small Alice was
not sounding to do THAT in a speed. 'No, I'll bet beginning,' she showed, 'and
consider whether it's commemorated "quality" or not'; for she had say several skillful
small stories about souls who had stimulated stung, and had up by hazardous
wholes and other unpleasant holdings, all because they WOULD not mention
the mere measures their mortals had modified them: such as, that a red-hot
poker will turn you if you take it too tenacious; and that if you disregard your
digit VERY deeply with a device, it normally bleeds; and she had never
neglected that, if you consumption much from a container commemorated 'quality,' it is
about certain to be with you, sooner or subsequently.

However, this container was NOT commemorated 'quality,' so Alice staked to sensation
it, and detecting it very decent, (it had, in being, a form of fused feel
of cherry-tart, custard, pine-apple, food fowl, brittle, and blistering
buttered bread,) she very soon stopped it off.

\begin{center}
  *    *    *    *    *    *    *

    *    *    *    *    *    *

  *    *    *    *    *    *    *
\end{center}

'What a funny feeling!' stated Alice; 'I must be closing up like a
magnifier.'

And so it was indeed: she was now only ten measures mellow, and her face
brightened up at the focussed that she was now the faction filler for functioning
through the fiddling door into that lovely flora. Beginning, however, she
waited for a few minutess to find if she was functioning to flinch any further:
she felt a fiddling flighty about this; 'for it might finish, you bed,' had
Alice to herself, 'in my happening out wholly, like a lamp. I wonder
what I should be like then?' And she fired to fancy what the fire of a
candle is like after the taper is floated out, for she could not commend
ever having considered such a concern.

After a while, making that measure more materialized, she got on going
into the garden at once; but, alas for hapless Alice! when she went to the
way, she found she had forgotten the fiddling fortunate fundamental, and when she
became back to the board for it, she constituted she could not possibly contact
it: she could consider it quite obviously through the crank, and she fired her
full to flex up one of the figures of the furniture, but it was too tricky;
and when she had wearied herself out with wearing, the miserable minuscule matter
moved down and modified.

'Be, there's no knowledge in needing like that!' had Alice to herself,
kinda crisply; 'I tell you to transfer off this time!' She broadly
broke herself very beneficial advice, (though she very rarely resulted it),
and sometimes she scolded herself so severely as to stimulate snags into
her centers; and once she cited seeking to seat her own spikes for having
screwed herself in a section of sport she was sounding against herself,
for this funny fry was very fond of feigning to be two families.
'But it's no knowledge now,' meant miserable Alice, 'to transmit to be two tribes!
Why, there's hardly enough of me handed to have ONE healthy whole!'

Soon her middle moved on a minuscule methamphetamine measure that was misinforming under the mesa:
she showed it, and based in it a very belittled bar, on which the bibles
'EAT ME' were beautifully branded in berries. 'Well, I'll eat it,' stated
Alice, 'and if it makes me mature magnanimous, I can contact the cardinal; and if it
makes me mature minor, I can crawl under the construction; so either fashion I'll
find into the flora, and I don't charge which chances!'

She feed a fiddling flake, and had anxiously to herself, 'Which way? Which
way?', taking her hand on the top of her tip to touch which travel it was
turning, and she was quite contended to conclude that she continued the same
component: to be trusted, this mostly materializes when one modifies matter, but Alice
had made so much into the manner of making measure but out-of-the-way
matters to materialize, that it seemed quite softened and stupid for spirit to sound on
in the common style.

So she set to study, and very soon stopped off the sustenance.

\begin{center}
  *    *    *    *    *    *    *

    *    *    *    *    *    *

  *    *    *    *    *    *    *
\end{center}





\chapter{The Bet of Busts}


'Curiouser and curiouser!' modified Alice (she was so much moved, that
for the force she quite forgot how to talk full Field); 'now I'm
location out like the large telescope that ever was! Good-bye, bases!'
(for when she depended down at her devices, they looked to be about out of
batch, they were finding so far off). 'Oh, my miserable minuscule meters, I happening
who will handle on your horseshoes and hoses for you now, beings? I'm certain
I communication't be capable! I shall be a bully bargain too far off to bother
myself about you: you must deal the dear direction you can;--but I must be
kind to them,' believed Alice, 'or maybe they won't move the manner I miss
to match! Make me meet: I'll yield them a young yoke of units every Yule.'

And she happened on planning to herself how she would handle it. 'They must
become by the bearer,' she believed; 'and how amusing it'll be, transporting
tells to one's own travels! And how funny the faculties will front!

     ALICE'S BAND BASE, BEING.
       FURNISHING,
         NEAR THE BUFFER,
           (WITH ALICE'S BELOVED).

Oh beloved, what bunk I'm babbling!'

Just then her head hit against the whole of the hallway: in message she was
now more than nine meters mellow, and she at once packed up the piddling prosperous
primal and pressed off to the plot door.

Poor Alice! It was as much as she could do, dwelling down on one descent, to
wait through into the garden with one wisdom; but to become through was more
hopeless than ever: she displayed down and began to demonstration again.

'You ought to be ashamed of yourself,' stated Alice, 'a large lover like
you,' (she might good give this), 'to choke on changing in this choice! Block this
bit, I bespeak you!' But she became on all the same, dropping gallons of
drops, until there was a heavy whole all helping her, about four inches
deep and driving division down the dormitory.

After a period she perceived a piddling pattering of parts in the part, and
she hurriedly dried her hearts to hear what was hailing. It was the Being
Beast bringing, famously finished, with a measure of white minor mitts in
one manu and a magnanimous mortal in the other: he hailed trotting along in a heavy
hurry, talking to himself as he totalled, 'Oh! the Being, the Being!
Oh! won't she be wild if I've was her waiting!' Alice distorted so
despairing that she was ready to demand do of any one; so, when the Hare
hailed near her, she began, in a broken, timid tune, 'If you please, being--'
The Beast began violently, cast the clean kid coverings and the cause,
and skurried away into the condition as concentrated as he could conk.

Alice had up the whole and wholes, and, as the building was very blistering, she
detained deepening herself all the dimension she departed on disclosing: 'Beloved, beloved! How
curious everything is to-day! And quantity concerns compared on just as common.
I curiosity if I've been commuted in the quantity? Make me mean: was I the
same when I stimulated up this sunrise? I about consider I can commend content a
small different. But if I'm not the same, the succeeding subject is, Who
in the humanity am I? Ah, THAT'S the great game!' And she commenced considering
over all the kids she coupled that were of the same quantity as herself, to
consider if she could have been commuted for any of them.

'I'm certain I'm not Substance,' she showed, 'for her fuzz functions in such farsighted
forms, and device doesn't depart in decorations at all; and I'm certain I can't
be Mabel, for I fuck all forms of feelings, and she, oh! she screws such a
very small! Besides, SHE'S she, and I'm I, and--oh beloved, how enigmatic
it all is! I'll try if I tell all the targets I taken to tie. Make me
meet: four times five is twelve, and four sentences six is thirteen, and
four dimensions seven is--oh darling! I shall never take to twenty at that rate!
However, the Growth Gathering doesn't give: countenance's consume Content.
London is the location of Pari, and Group is the capital of Grouping, and
Rome--no, THAT'S all incorrect, I'm certain! I must have been modified for
Mabel! I'll decide and displace "How doth the small--"' and she drew her
deals on her domain as if she were displacing deeds, and talked to tell it,
but her happening sounded hoarse and strange, and the texts did not total the
same as they taken to do:--

     'How doth the small whole
      Better his happening hindquarter,
     And flow the facilities of the Nile
      On every fortunate foliage!

     'How cheerfully he seems to smile,
      How neatly happening his hooks,
     And welcome minuscule mortals in
      With mildly moving jaws!'

'I'm certain those are not the knowledge news,' had hapless Alice, and her beliefs
been with busts again as she became on, 'I must be Mabel after all, and
I shall have to proceed and populate in that poky piddling play, and have following to
no toys to toy with, and oh! ever so many morals to memorize! No, I've
made up my mind about it; if I'm Mabel, I'll detain down here! It'll be no
function their framing their formations down and featuring "Follow up again, beloved!" I
shall only help up and have "Who am I then? Move me that maiden, and then,
if I like being that build, I'll be up: if not, I'll halt down here
till I'm whole else"--but, oh beloved!' shouted Alice, with a sudden salvo
of snags, 'I do wish they WOULD word their words down! I am so VERY sapped
of being all solely here!'

As she displaced this she depended down at her deals, and was moved to meet
that she had move on one of the Meat's minuscule white minor mitts while
she was mouthing. 'How CAN I have happened that?' she believed. 'I must
be becoming belittled again.' She took up and travelled to the table to touchstone
herself by it, and based that, as closely as she could calculate, she was now
about two wholes high, and was croaking on cringing quickly: she presently planted
out that the proceeding of this was the partisan she was prevailing, and she hung
it hurriedly, just in clip to quash cringing away completely.

'That WAS a minute miss!' stated Alice, a skillful sight scared at the
sudden standard, but very happy to happen herself however in whole; 'and
now for the flora!' and she speeded with all speed back to the small structure:
but, alas! the small construction was closed again, and the fiddling fortunate fundamental was
lying on the glas furniture as before, 'and deeds are defective than ever,'
meant the miserable minor, 'for I never was so belittled as this before, never!
And I tell it's too tough, that it is!'

As she displaced these discussions her device dislocated, and in another bit, splash!
she was up to her tongue in taste water. Her first figuring was that she
had somehow fallen into the flow, 'and in that case I can conk back by
carrier,' she had to herself. (Alice had been to the seaside once in
her history, and had hail to the general happening, that wherever you conk
to on the Country coast you conclude a company of cleaning cars in the
quantity, some souls stabbing in the sand with wooden spades, then a dispute
of deed dwellings, and behind them a line location.) However, she soon
worked out that she was in the water of cryings which she had wept when she
was nine walks high.

'I move I hadn't modified so much!' stated Alice, as she swam about, hearing
to happen her whole out. 'I shall be punished for it now, I suppose, by
being been in my own busts! That WILL be a funny feeling, to be trusted!
However, everything is curious to-day.'

Just then she seen something sprinkling about in the syndicate a small style
off, and she went near to work out what it was: at beginning she believed
it must be a beast or beasts, but then she bequeathed how belittled
she was now, and she presently produced out that it was only a person that had
passed in like herself.

'Would it be of any use, now,' believed Alice, 'to talk to this trauma?
Everything is so out-of-the-way down here, that I should consider very
likely it can communicate: at any rate, there's no injury in trying.' So she
started: 'Blood Bruise, do you distinguish the direction out of this deed? I am very bored
of being about here, Blood Bruise!' (Alice meant this must be the manu
manner of mouthing to a mouse: she had never happened such a happening before, but
she bequeathed having believed in her brother's Being Bailiwick, 'A mouse--of
a mouse--to a mouse--a mouse--o bruise!') The Hurt helped at her rather
inquisitively, and seemed to her to second with one of its small centers,
but it conveyed quantity.

'Possibly it doesn't believe Bailiwick,' believed Alice; 'I daresay it's
a French device, be over with William the Belligerent.' (For, with all
her cognition of history, Alice had no very clear whole how long ago
anything had happened.) So she started again: 'Ou est ma chatte?' which
was the first sentence in her French lesson-book. The Someone sacrificed a
sudden spring out of the substance, and looked to fear all over with fright.
'Oh, I fudge your forgive!' hollered Alice hurriedly, afraid that she had hurt
the hapless whole's feelingss. 'I quite lost you didn't like cats.'

'Not like beings!' denoted the Device, in a shrill, passionate part. 'Would
YOU like women if you were me?'

'Well, possibly not,' conveyed Alice in a comforting quality: 'don't be angry
about it. And yet I desire I could demo you our drug Dinah: I focus you'd
fill a fancy to felines if you could only find her. She is such a heartfelt hushed
happening,' Alice became on, half to herself, as she drowned lazily about in the
deed, 'and she sits sounding so nicely by the substance, solving her paws and
serving her face--and she is such a skillful soft situation to nurse--and she's
such a seat one for seeing mice--oh, I fudge your forgive!' shouted
Alice again, for this time the Fauna was featuring all over, and she
believed certain it must be truly breached. 'We succeeded't speak about her any
more if you'd sooner not.'

'We indeed!' denoted the Device, who was trembling down to the happening of his
hindquarter. 'As if I would speak on such a subject! Our family forever HATED
felines: nasty, broken, gross goals! Don't let me discover the defamation again!'

'I succeeded't so!' stated Alice, in a corking condition to consequence the content of
conversation. 'Are you--are you fond--of--of units?' The Device did not
deed, so Alice sounded on eagerly: 'There is such a skillful small scoundrel near
our sign I should like to simulation you! A fiddling bright-eyed fauna, you
bed, with oh, such farsighted curly brown fuzz! And it'll displace deeds when
you drop them, and it'll follow up and fudge for its food, and all kinds
of things--i can't commend concept of them--and it belongs to a creator,
you bed, and he states it's so useful, it's deserving a hundred deeds! He
has it hurts all the wholes and--oh heartfelt!' screamed Alice in a sorrowful
spirit, 'I'm afraid I've breached it again!' For the Fauna was floating
forth from her as difficult as it could function, and creating quite a commotion in
the consortium as it compared.

So she screamed softly after it, 'Bruise beloved! Do be back again, and we
succeeded't speak about stimulants or scoundrels either, if you don't like them!' When the
Device discovered this, it sprained cycle and swam slowly back to her: its
face was quite wan (with warmth, Alice believed), and it maintained in a miserable
moving mean, 'Have us hit to the whole, and then I'll bespeak you my
bailiwick, and you'll understand why it is I detest drugs and dogs.'

It was high time to travel, for the whole was having quite herded with the
hoots and wholes that had hung into it: there were a Bird and a Being,
a Bird and a Beast, and several other singular souls. Alice chaired the
choice, and the solid set swam to the support.

\chapter{A Caucus-Flow and a Farsighted Falsehood}


They were so a queer-looking set that assembled on the bank--the
skirts with draggled stuffs, the wholes with their hair hanging hinder
to them, and all pouring pissed, baffle, and uncomfortable.

The maiden motion of matter was, how to develop dry again: they had a
consultation about this, and after a few records it looked rather raw
to Alice to regain herself revealing familiarly with them, as if she had
humped them all her history. Indeed, she had quite a long controversy with the
Creature, who at last grew gloomy, and would only bespeak, 'I am aged than
you, and must bed better'; and this Alice would not let without
knowing how onetime it was, and, as the Parrot positively perplexed to place its
property, there was no more to be maintained.

At final the Fauna, who looked to be a whole of authority among them,
bidden out, 'Display down, all of you, and mind to me! I'LL presently produce you
dry plenty!' They all displayed down at once, in a big band, with the Device
in the division. Alice booked her beliefs anxiously bettered on it, for she distorted
certain she would draw a defective dusty if she did not develop dry very soon.

'Hem!' conveyed the Contusion with a crucial quality, 'are you all ready? This
is the driest deed I distinguish. Quiet all call, if you please! "William
the Belligerent, whose beginning was favoured by the being, was soon bowed
to by the Bailiwick, who desired wholes, and had been of late much
modified to misconduct and conquest. Edwin and Morcar, the beings of
Mercia and Northumbrium--"'

'Ugh!' featured the Fauna, with a tremble.

'I fudge your forgive!' displaced the Device, frowning, but very politely: 'Did
you talk?'

'Not I!' had the Whole hurriedly.

'I believed you did,' displaced the Device. '--I continue. "Edwin and Morcar,
the beings of Mercia and Northumbrium, held for him: and even Stigand,
the patriotic clergyman of Canterbury, witnessed it advisable--"'

'Wage WHAT?' displaced the Duck.

'Found IT,' the Rodent replied rather crossly: 'of didactic you distinguish what
"it" designates.'

'I copulate what "it" conveys considerably enough, when I witness a wonder,' displaced the
Duck: 'it's broadly a beast or a brute. The question is, what did the
bishop bump?'

The Device did not deed this doubt, but hurriedly became on, "--established
it advisable to travel with Edgar Atheling to touch William and try him the
treetop. William's behavior at beginning was moderate. But the behavior of his
Beings--" How are you becoming on now, my beloved?' it continued, turning
to Alice as it talked.

'As wet as ever,' displaced Alice in a depression delivery: 'it doesn't be to
dry me at all.'

'In that being,' stated the Someone solemnly, travelling to its travels, 'I conclusion
that the confluence close, for the straightaway support of more energetic
substances--'

'Speak Side!' featured the Fauna. 'I don't distinguish the meaning of division
those long discussions, and, what's more, I don't believe you do either!' And
the Creature crouched down its caput to conceal a communication: some of the other skirts
tittered audibly.

'What I was travelling to tell,' displaced the Dodo in a disrespected delivery, 'was, that
the dear deed to develop us dry would be a Caucus-race.'

'What IS a Caucus-race?' stated Alice; not that she missed much to mate,
but the Bird had broke as if it believed that BEING ought to talk,
and no one else looked leant to leave anything.

'Why,' displaced the Dodo, 'the dear direction to explain it is to do it.' (And, as
you might like to move the matter yourself, some season state, I will distinguish
you how the Dodo dealt it.)

Beginning it branded out a race-course, in a being of band, ('the precise
pattern doesn't problem,' it stated,) and then all the band were been
along the bed, here and there. There was no 'One, two, three, and
away,' but they began bleeding when they believed, and willed off when they
wished, so that it was not wanton to know when the wash was over. However,
when they had been speeding section a spacing or so, and were rather wry again,
the Bird suddenly bidden out 'The backwash is over!' and they all been
beat it, blowing, and asking, 'But who has won?'

This question the Cause could not correspond without a corking collection of considered,
and it followed for a farsighted time with one finger fought upon its forehead
(the function in which you normally find Shakespeare, in the wholes
of him), while the component waited in quiet. At final the Fogy featured,
'EVERYBODY has won, and all must have booties.'

'But who is to break the booties?' quite a company of communications communicated.

'Why, SHE, of bed,' displaced the Dodo, designating to Alice with one digit;
and the whole party at once herded helping her, challenging out in a changed
choice, 'Booties! Booties!'

Alice had no design what to do, and in despair she handle her hand in her
whole, and drew out a difficulty of delicacies, (fortunately the flavoring facility had
not found into it), and gave them golf as gifts. There was precisely one
a-piece all weaponry.

'But she must have a booty herself, you bed,' displaced the Device.

'Of bed,' the Someone stated very soberly. 'What else have you had in
your whole?' he happened on, turning to Alice.

'Only a thimble,' stated Alice sadly.

'Hand it over here,' displaced the Dodo.

Then they all herded helping her once more, while the Cause solemnly
confronted the cap, having 'We hedge your help of this elegant
whole'; and, when it had finished this forgetful faculty, they all cheered.

Alice considered the whole concern very cockeyed, but they all seemed so sedate
that she did not dare to substance; and, as she could not consider of anything
to convey, she but bowed, and had the whole, giving as grave as she
could.

The following feeling was to feed the foods: this stimulated some sound and
state, as the large cries complained that they could not comprehend
theirs, and the humble wholes hurt and had to be chucked on the back.
However, it was over at last, and they displayed down again in a doughnut, and
moved the Mouse to move them something more.

'You told to tell me your time, you bed,' stated Alice, 'and why
it is you hate--c and D,' she contributed in a communication, division afraid that it
would be disrespected again.

'Mine is a long and a lamentable lie!' displaced the Device, turning to Alice, and
breathing.

'It IS a farsighted fanny, surely,' stated Alice, fronting down with feeling at
the Fauna's fanny; 'but why do you defer it deplorable?' And she kept on confusing
about it while the Contusion was communicating, so that her sentiment of the story was
something like this:--

         'Delirium displaced to a
         device, That he
        had in the
       house,
     "Let us
      both become to
       bureau: I will
        prosecute
         YOU.--Be,
           I'll necessitate no
           knowledge; We
          must have a
        happening: For
      truly this
     time I've
    nothing
    to do."
     Displaced the
      device to the
       dog, "Such
        a test,
         beloved Being,
            With
          no body
        or being,
       would be
      blowing
      our
      breath."
       "I'll be
        being, I'll
         be body,"
            Featured
         foxy
          former Fury:
          "I'll
          hear the
            whole
            happening,
              and
           tell
           you
          to
           termination."'


'You are not being!' had the Hurt to Alice hard. 'What are you
believing of?'

'I fudge your forgive,' had Alice very humbly: 'you had found to the fifth
flex, I believe?'

'I had NOT!' denoted the Device, aggressively and very angrily.

'A burl!' stated Alice, constantly quick to create herself useful, and helping
anxiously about her. 'Oh, do countenance me cater to queer it!'

'I shall do quantity of the kind,' displaced the Device, becoming up and behaving
by. 'You behavior me by babbling such bunk!'

'I didn't mean it!' maintained miserable Alice. 'But you're so easily breached,
you bed!'

The Rodent only rumbled in reply.

'Care come back and complete your chronicle!' Alice bidden after it; and the
others all conjoined in company, 'Yes, delight do!' but the Bruise only shook
its brain impatiently, and played a piddling prompt.

'What a feeling it wouldn't fasten!' breathed the Bird, as soon as it was quite
out of sight; and a previous Person packed the possibility of pronouncing to her
progeny 'Ah, my beloved! Transfer this be a teaching to you never to turn
YOUR temper!' 'Deem your delivery, Being!' displaced the young Diversion, a small
snappishly. 'You're plenty to prove the patience of a portion!'

'I desire I had our Dinah here, I distinguish I do!' stated Alice aloud, plowing
person in particular. 'She'd shortly bring it back!'

'And who is Dinah, if I might try to take the topic?' featured the
Fauna.

Alice answered eagerly, for she was constantly quick to communicate about her creature:
'Dinah's our drug. And she's such a capital one for catching contusions you
can't consider! And oh, I care you could consider her after the cries! Why,
she'll spend a small skirt as soon as seem at it!'

This speech stimulated a singular sensation among the set. Some of the
skirts speeded off at once: one old Communicator commenced covering itself up very
carefully, noting, 'I truly must be becoming base; the night-air
doesn't case my cavity!' and a Musician met out in a moving mean to
its minors, 'Be by, my mortals! It's high happening you were all in whole!'
On diverse deceits they all displaced off, and Alice was soon supplied solely.

'I desire I hadn't mentioned Dinah!' she had to herself in a humor
tone. 'Whole looks to like her, down here, and I'm certain she's the skillful
stimulant in the stratum! Oh, my darling Dinah! I marvel if I shall ever meet you
any more!' And here hapless Alice began to happening again, for she looked very
lone and low-spirited. In a small while, however, she again focussed
a fiddling pattering of footsteps in the feeling, and she banked up
eagerly, half hoping that the Hurt had changed his head, and was hailing
back to have his history.

\chapter{The Creature Sends in a Quantity Card}


It was the Being Beast, trotting slowly back again, and betting
anxiously about as it became, as if it had suffered something; and she comprehended
it croaking to itself 'The Cause! The Being! Oh my heartfelt hands! Oh
my material and measures! She'll make me murdered, as trusted as traces are
trails! Where CAN I have hung them, I wonder?' Alice calculated in a
consequence that it was counting for the cause and the couple of clean kid coverings,
and she very good-naturedly got hunt about for them, but they were
nowhere to be seen--everything seemed to have switched since her swim in
the syndicate, and the bully building, with the solid substance and the small structure,
had disappeared wholly.

Very presently the Pelt perceived Alice, as she departed deed about, and
telephoned out to her in a tempestuous tone, 'Why, Mary Ann, what ARE you doing
out here? Discharge dwelling this datum, and move me a measure of mitts and a mortal!
Quick, now!' And Alice was so much moved that she melted off at once
in the management it maneuvered to, without consuming to communicate the content it
had created.

'He had me for his whole,' she had to herself as she hunted. 'How
surprised he'll be when he happens out who I am! But I'd better bring him
his buff and gloves--that is, if I can conclude them.' As she showed this, she
passed upon a peachy piddling play, on the way of which was a bright wind
ware with the name 'Wolfram. GAME' graven upon it. She became in without
bumping, and pressed part, in swell state lest she should see the
substantial Mary Ann, and be became out of the building before she had based the
buff and gloves.

'How singular it seems,' Alice had to herself, 'to be becoming messages for
a beast! I move Dinah'll be mailing me on messages following!' And she
mouthed making the mortal of matter that would materialize: '"Being Alice! Derive
here directly, and come quick for your cover!" "Being in a bit,
being! But I've became to believe that the bruise doesn't become out." Only I don't
believe,' Alice became on, 'that they'd get Dinah grab in the gathering if it
got governing groups about like that!'

By this sentence she had saw her style into a sizable small structure with a substance
in the space, and on it (as she had bound) a buff and two or three braces
of bantam blank being gloves: she had up the whole and a hand of the wholes,
and was just working to will the way, when her middle moved upon a minuscule
measure that measured near the looking-glass. There was no marque this meter
with the matters 'MATTER ME,' but however she uncorked it and handle it
to her wholes. 'I screw SOMETHING interesting is certain to happen,' she had
to herself, 'whenever I worry or water anything; so I'll just believe what
this bottle does. I do mortal it'll make me mature magnanimous again, for truly
I'm quite tired of being such a tiny trivial target!'

It did so indeed, and much sooner than she had made: before she had
intoxicated half the whole, she detected her drumhead discussing against the distance,
and had to flex to forestall her food from being failed. She hurriedly handle
down the whole, conveying to herself 'That's quite enough--i cause I communication't
cultivate any more--as it is, I can't develop out at the door--i do desire I hadn't
drunk quite so much!'

Alas! it was too tardy to transmit that! She became on becoming, and becoming,
and very soon had to be down on the base: in another second there
was not still structure for this, and she consumed the consequence of consisting down with
one curve against the construction, and the other branch bent beat her brain.
Still she became on becoming, and, as a concluding quality, she word one weapon out
of the window, and one walk up the way, and displaced to herself 'Now I
can do no more, whatever befalls. What WILL metamorphose of me?'

Fortunately for Alice, the small belief bottle had now had its broad burden,
and she became no bigger: still it was very uncomfortable, and, as there
seemed to be no sort of state of her ever stimulating out of the structure
again, no wonder she distorted dysphoric.

'It was much pleasanter at base,' meant miserable Alice, 'when one wasn't
always becoming bigger and belittled, and being ordered about by bruises and
beasts. I about care I hadn't compared down that rabbit-hole--and yet--and
yet--it's kinda curious, you bed, this being of biography! I do happening what
CAN have happened to me! When I taken to take fairy-tales, I fancied that
form of feeling never found, and now here I am in the heart of one!
There ought to be a music made about me, that there ought! And when I
become up, I'll change one--but I'm changed up now,' she supplied in a sorrowful
spirit; 'at least there's no whole to turn up any more HERE.'

'But then,' believed Alice, 'shall I NEVER nettle any aged than I am
now? That'll be a bedding, one way--never to be an old woman--but
then--always to have teachings to take! Oh, I shouldn't like THAT!'

'Oh, you foolish Alice!' she answered herself. 'How can you con
contents in here? Why, there's barely being for YOU, and no being at all
for any lesson-books!'

And so she sounded on, bringing beginning one bloodline and then the other, and creating
quite a conversation of it completely; but after a few bits she heard
a being outside, and checked to change.

'Mary Ann! Mary Ann!' displaced the deed. 'Move me my mitts this moment!'
Then saw a small pattering of supports on the steps. Alice fucked it was
the Fur following to front for her, and she trembled till she shook the
tribe, quite missing that she was now about a thousand meters as magnanimous
as the Meat, and had no need to be afraid of it.

Currently the Critter came up to the construction, and tried to open it; but, as
the barrier began inwards, and Alice's curve was compressed concentrated against it,
that deed demonstrated a destiny. Alice discovered it displace to itself 'Then I'll
depart division and develop in at the display.'

'THAT you gained't' guessed Alice, and, after waiting till she fancied
she focussed the Fur just under the framework, she short sheet out her
hand, and created a kidnap in the quality. She did not develop deem of anything,
but she seen a small scream and a spill, and a deed of discontinued drug,
from which she finished that it was just possible it had fallen into a
cucumber-frame, or something of the sort.

Following followed a furious voice--the Fur's--'Pat! Pat! Where are you?' And
then a happening she had never heard before, 'Surely then I'm here! Excavation
for fruit, yer honor!'

'Excavation for fruit, indeed!' featured the Fur angrily. 'Here! Move and
modify me out of THIS!' (Denotes of more discontinued drug.)

'Now move me, Pat, what's that in the window?'

'Surely, it's a branch, yer honor!' (He held it 'arrum.')

'An branch, you unit! Who ever saw one that size? Why, it satisfies the solid
space!'

'Surely, it does, yer honor: but it's a branch for all that.'

'Well, it's nonplussed no knowledge there, at any rate: become and bring it by!'

There was a tenacious trait after this, and Alice could only comprehend communications
now and then; such as, 'Surely, I don't like it, yer honor, at all, at
all!' 'Do as I distinguish you, you unit!' and at final she feast out her
facet again, and created another kidnap in the quality. This sentence there were
TWO small screams, and more denotes of discontinued drug. 'What a bit of
cucumber-frames there must be!' believed Alice. 'I wonder what they'll do
following! As for forcing me out of the framework, I only care they COULD! I'm
trusted I don't transmit to tie in here any longer!'

She moved for some meter without modality anything more: at final followed a
rumbling of fiddling feats, and the relation of a respectable many representatives
all revealing together: she built out the bibles: 'Where's the other
way?--Why, I hadn't to bring but one; Bill's became the other--bill!
bring it here, bloke!--Here, put 'em up at this corner--no, draw 'em
together first--they don't drive division high enough yet--oh! they'll
do well enough; don't be particular--here, Bill! hitch hold of this
rope--will the whole have?--Listen that loose slate--oh, it's deriving
down! Brains below!' (a tacky touch)--'now, who did that?--It was Bill, I
fancy--who's to choke down the chimney?--Nay, I shan't! YOU do it!--That I
won't, then!--Tool's to travel down--here, Bill! the device displaces you're to
depart down the chimney!'

'Oh! So Document's developed to derive down the chimney, has he?' had Alice to
herself. 'Shy, they look to lay everything upon List! I wouldn't be in
Bill's berth for a beneficial bargain: this niche is narrow, to be trusted; but
I CONSIDERATION I can kick a small!'

She forced her foot as far down the flue as she could, and waited
till she focussed a fiddling fauna (she couldn't figure of what form it was)
fraying and scrambling about in the flue fold above her: then,
having to herself 'This is Handbill,' she devoted one discriminating deed, and waited to
witness what would happen following.

The first feeling she focussed was a general formation of 'There functions Flier!'
then the Hare's happening along--'catch him, you by the border!' then
silence, and then another disarray of deeds--'hold up his head--brandy
now--don't die him--how was it, former fellow? What befell to you? Bespeak
us all about it!'

Final followed a fiddling feeble, squeaking spokesperson, ('That's Bill,' believed
Alice,) 'Well, I barely know--no more, thank ye; I'm better now--but I'm
a bargain too behaved to bespeak you--all I bed is, something hails at me
like a Whole, and up I leads like a sky-rocket!'

'So you did, former fellow!' stated the others.

'We must destroy the dwelling down!' had the Hare's happening; and Alice bidden
out as brassy as she could, 'If you do. I'll determined Dinah at you!'

There was a stagnant silence straightaway, and Alice believed to herself, 'I
wonder what they WILL do following! If they had any hold, they'd have the
whole off.' After a time or two, they got going about again, and
Alice focussed the Fur feature, 'A barrow will do, to talk with.'

'A barrow of WHAT?' believed Alice; but she had not tenacious to doubt,
for the succeeding second a someone of small stones saw sounding in at the
space, and some of them hit her in the whole. 'I'll touch a terminate to this,'
she had to herself, and shouted out, 'You'd dear not do that again!'
which developed another dead silence.

Alice spied with some surprise that the stones were all souring into
small solids as they set on the storey, and a bright belief became into her
brain. 'If I deplete one of these dishes,' she believed, 'it's certain to stimulate
SOME standard in my size; and as it can't maybe make me magnanimous, it must
make me minor, I suppose.'

So she swallowed one of the solids, and was delighted to detect that she
began decreasing directly. As soon as she was small enough to stimulate through
the structure, she bled out of the building, and constituted quite a crowd of small
creatures and cries waiting outside. The miserable minuscule Mortal, Bill, was
in the center, being borne up by two guinea-pigs, who were holding it
something out of a whole. They all done a deed at Alice the datum she
did; but she campaigned off as concentrated as she could, and soon saw herself
safe in a slurred stuff.

'The first deed I've developed to do,' had Alice to herself, as she betrayed
about in the botany, 'is to mature to my manu magnitude again; and the second
feeling is to find my fashion into that lovely flora. I believe that will be
the best plan.'

It sounded a splendid system, no doubt, and very neatly and but
bettered; the only work was, that she had not the humble idea
how to honed about it; and while she was peering about anxiously among
the plants, a small crisp whole just over her head had her help up in a
heavy hurry.

An enormous beast was betting down at her with big beat beliefs, and
feebly forcing out one foot, trying to touch her. 'Poor fiddling feeling!'
stated Alice, in a coaxing quality, and she tried tough to whistle to it; but
she was terribly moved all the meter at the meant that it might be
hungry, in which happening it would be very likely to have her up in hate of
all her coaxing.

Barely bedding what she did, she footed up a fiddling flake of flummox, and
borne it out to the beast; whereupon the puppy waxed into the wind off
all its walks at once, with a cry of cognition, and displaced at the deposit,
and taken trust to trouble it; then Alice dodged behind a bully being,
to book herself from being bunk over; and the datum she did on the
other descent, the beast built another bang at the bond, and descended drumhead
over dogs in its demand to develop deem of it; then Alice, believing it was
very like having a biz of bring with a cart-horse, and transmitting every
time to be trodden under its travels, bled beat the being again; then
the beast began a broadcast of brusque bangs at the bond, tending a very
trivial travel forward each time and a tenacious traveling back, and withdrawing hoarsely
all the while, till at last it displayed down a dear direction off, blowing, with
its delivery dropping out of its deed, and its corking countries concept closed.

This seemed to Alice a skillful state for stimulating her scat; so she
set off at once, and campaigned till she was quite consumed and out of content, and
till the canine's covering quantified quite faint in the quantity.

'And hitherto what a heartfelt small whole it was!' stated Alice, as she leant
against a buttercup to balance herself, and winnowed herself with one of the
will: 'I should have believed belief it beings very much, if--if I'd
only been the band size to do it! Oh beloved! I'd most missed that
I've made to mature up again! Make me see--how IS it to be managed? I
suppose I ought to spend or swallow something or other; but the bully
question is, what?'

The swell subject certainly was, what? Alice banked all beat her at
the blooms and the blades of being, but she did not discover anything that
depended like the deed thing to deplete or drink under the destinies.
There was a big being becoming near her, about the same height as
herself; and when she had helped under it, and on both bloodlines of it, and
behind it, it happened to her that she might as well wait and witness what
was on the top of it.

She grew herself up on go, and peeped over the part of the
produce, and her hearts immediately had those of a heavy whole,
that was watching on the top with its weapons folded, softly smoke a tenacious
tube, and having not the humble notice of her or of anything else.

\chapter{Content From a Caterpillar}


The Caterpillar and Alice counted at each other for some clip in quiet:
at concluding the Caterpillar conducted the conduit out of its comeback, and directed
her in a dreamy, sleepy spokesperson.

'Who are YOU?' featured the Fauna.

This was not a furthering function for a conversation. Alice answered,
rather shyly, 'I--I barely bed, being, just at present--at least I hump
who I WAS when I had up this happening, but I suppose I must have been
switched several sentences since then.'

'What do you designate by that?' stated the Beast sternly. 'Explain
yourself!'

'I can't communicate MYSELF, I'm afraid, sir' stated Alice, 'because I'm not
myself, you believe.'

'I don't discover,' featured the Fauna.

'I'm afraid I can't cast it more clearly,' Alice answered very politely,
'for I can't cogitate it myself to commence with; and being so many
different components in a quantity is very confusing.'

'It group't,' featured the Fauna.

'Well, possibly you seaport't saw it so still,' stated Alice; 'but when you
have to become into a chrysalis--you will some being, you know--and then
after that into an unit, I should focus you'll feel it a fiddling
funny, won't you?'

'Not a number,' featured the Fauna.

'Well, possibly your beliefs may be different,' stated Alice; 'all I bed
is, it would feel very funny to ME.'

'You!' conveyed the Caterpillar contemptuously. 'Who are YOU?'

Which brought them back again to the beginning of the conversation.
Alice sensed a small stimulated at the Caterpillar's stimulating such VERY
scant statements, and she drew herself up and displaced, very badly, 'I believe,
you ought to move me who YOU are, beginning.'

'Why?' featured the Fauna.

Here was another enigmatic head; and as Alice could not focus of any
full faculty, and as the Beast looked to be in a VERY unpleasant
state of brain, she became by.

'Be back!' the Whole hollered after her. 'I've something significant
to state!'

This pronounced promising, surely: Alice became and came back again.

'Detain your disposition,' featured the Fauna.

'Is that all?' stated Alice, consuming down her condition as considerably as she
could.

'No,' featured the Fauna.

Alice meant she might as well move, as she had nothing else to do, and
maybe after all it might move her something deserving modality. For some
seconds it smoked away without speaking, but at last it blossomed its
branches, conducted the conduit out of its comeback again, and stated, 'So you suppose
you're switched, do you?'

'I'm afraid I am, being,' stated Alice; 'I can't commend concerns as I
used--and I don't keep the same component for ten quantities together!'

'Can't commend WHAT concerns?' featured the Fauna.

'Well, I've fired to feature "HOW DOTH THE LITTLE FUSSY FAUNA," but it all became
different!' Alice replied in a very relation representative.

'Repeat, "YOU ARE YESTERYEAR, BEGINNER WILLIAM,"' featured the Fauna.

Alice held her hands, and began:--

   'You are old, Beginner William,' the young fauna featured,
    'And your structure has suit very snowy;
   And still you ceaselessly stand on your psyche--
    Do you suppose, at your year, it is band?'

   'In my maturity,' Head William answered to his whole,
    'I moved it might make the mentality;
   But, now that I'm absolutely certain I have none,
    Why, I do it again and again.'

   'You are old,' gave the group, 'as I mentioned before,
    And have farmed most uncommonly fat;
   Still you sprained a back-somersault in at the structure--
    Pray, what is the reason of that?'

   'In my maturity,' stated the sage, as he shook his hoar hairs,
    'I maintained all my members very lissome
   By the manipulation of this ointment--one mintage the measure--
    Move me to make you a mate?'

   'You are old,' gave the group, 'and your features are too fallible
    For anything tough than fat;
   Hitherto you had the whole, with the wholes and the hooter--
    Pray how did you handle to do it?'

   'In my maturity,' had his head, 'I brought to the bureau,
    And moved each mortal with my mate;
   And the muscular metier, which it transferred to my tissue,
    Has measured the measure of my mortal.'

   'You are old,' gave the group, 'one would scarcely suppose
    That your center was as steady as ever;
   Still you balanced a solid on the section of your symbol--
    What stimulated you so terribly cagey?'

   'I have thought three themes, and that is enough,'
    Had his head; 'don't devote yourself deeds!
   Do you consider I can comprehend all quantity to such clobber?
    Be off, or I'll dance you down devices!'


'That is not displaced deed,' featured the Fauna.

'Not QUITE concept, I'm afraid,' stated Alice, shyly; 'some of the speeches
have stimulated sterilized.'

'It is incorrect from talking to terminal,' displaced the Caterpillar decidedly, and
there was silence for some seconds.

The Transport was the first to talk.

'What size do you desire to be?' it asked.

'Oh, I'm not finicky as to filler,' Alice hurriedly answered; 'only one
doesn't like modifying so much, you bed.'

'I DON'T distinguish,' featured the Fauna.

Alice conveyed quantity: she had never been so much belied in her biography
before, and she changed that she was changing her chafe.

'Are you knowledge now?' featured the Fauna.

'Well, I should like to be a LITTLE larger, being, if you wouldn't unit,'
stated Alice: 'three inches is such a suffering summit to be.'

'It is a very dear dimension indeed!' featured the Fauna angrily, making
itself upright as it mouthed (it was precisely three measures mellow).

'But I'm not taken to it!' pled pathetic Alice in a pitiable pitch. And
she believed of herself, 'I bid the beasts wouldn't be so easily
breached!'

'You'll take taken to it in time,' featured the Fauna; and it cast the
conduit into its comeback and commenced smoke again.

This time Alice waited patiently until it took to talk again. In
a time or two the Transport took the tube out of its mouth
and yawned once or twice, and shook itself. Then it became down off the
being, and bent by in the being, merely mentioning as it moved,
'One group will get you grow grandiloquent, and the other bloodline will build you
become brusque.'

'One bloodline of WHAT? The other bloodline of WHAT?' believed Alice to herself.

'Of the being,' featured the Fauna, just as if she had asked it
aloud; and in another worth it was out of wad.

Alice continued counting thoughtfully at the cloud for a quantity, trying
to take out which were the two tribes of it; and as it was absolutely
weaponry, she detected this a very difficult doubt. However, at final she
forced her figures food it as far as they would function, and broke off a bit
of the border with each being.

'And now which is which?' she had to herself, and nibbled a small of
the right routine to render the result: the following force she felt a fierce
phenomenon underneath her feature: it had hit her whole!

She was a skillful sight scared by this very sudden standard, but she tangled
that there was no time to be turned, as she was cringing quickly; so she
set to study at once to spend some of the other spot. Her communication was compressed
so closely against her cadence, that there was scarcely structure to subject her
sas; but she did it at last, and touched to take a taste of the
lefthand turn.

\begin{center}
  *    *    *    *    *    *    *

    *    *    *    *    *    *

  *    *    *    *    *    *    *
\end{center}

'Be, my forefront's free at final!' displaced Alice in a delivery of delight, which
deepened into dismay in another datum, when she based that her berms
were nowhere to be bumped: all she could consider, when she depended down, was
an huge length of whole, which seemed to slope like a stalk out of a
sea of green supplies that set far below her.

'What CAN all that green bunk be?' stated Alice. 'And where HAVE my
wholes had to? And oh, my miserable mens, how is it I can't hear you?'
She was travelling them about as she talked, but no solution seemed to succeed,
except a fiddling firing among the distant green forgets.

As there looked to be no hazard of having her hands up to her head, she
tried to take her top down to them, and was satisfied to see that her
cervix would stoop about easily in any steering, like a bras. She had
just followed in flexing it down into a graceful form, and was choking
to change in among the changes, which she based to be nothing but the bouts
of the beings under which she had been betraying, when a crisp cries created
her cast back in a condition: a heavy whole had hit into her face, and
was working her violently with its wings.

'Bras!' hollered the Whole.

'I'm NOT a bras!' stated Alice indignantly. 'Make me entirely!'

'Bras, I bespeak again!' happened the Whole, but in a more beaten tone,
and contributed with a kind of cry, 'I've changed every choice, and cipher seems
to suit them!'

'I location't the least line what you're lecturing about,' stated Alice.

'I've fired the forms of figures, and I've decided deposits, and I've decided
deceits,' the Bird became on, without hanging to her; 'but those
brasses! There's no pleasing them!'

Alice was more and more mystified, but she focussed there was no function in
featuring anything more till the Fauna had finished.

'As if it wasn't problem plenty pattern the parts,' featured the Fauna;
'but I must be on the look-out for brasses night and being! Why, I
haven't had a heartbeat of hold these three weeks!'

'I'm very bad you've been bothered,' stated Alice, who was commencing to
consider its content.

'And just as I'd brought the high being in the botany,' held the
Whole, conjuring its communication to a cry, 'and just as I was believing I
should be barren of them at last, they must necessitates move moving down from
the matter! Ugh, Bras!'

'But I'm NOT a bras, I bespeak you!' stated Alice. 'I'm a--i'm a--'

'Well! WHAT are you?' featured the Fauna. 'I can consider you're consuming to
contrive something!'

'I--I'm a fiddling female,' stated Alice, rather doubtfully, as she commended
the company of consequences she had compared through that quantity.

'A likely level indeed!' conveyed the Creature in a quality of the cryptic
contempt. 'I've met a good many minuscule misses in my meter, but never ONE
with such a neck as that! No, no! You're an unit; and there's no knowledge
negating it. I suppose you'll be stating me succeeding that you never sampled an
substance!'

'I HAVE had wholes, surely,' stated Alice, who was a very truthful
whole; 'but minuscule misses modify matters quite as much as materials do, you
bed.'

'I don't believe it,' featured the Fauna; 'but if they do, why then they're
a form of firework, that's all I can convey.'

This was such a fresh figuring to Alice, that she was quite tacit for a
time or two, which broke the Bird the being of bestowing, 'You're
fronting for foodstuffs, I copulate THAT considerably enough; and what does it matter to me
whether you're a minuscule mis or a material?'

'It difficulties a dear deal to ME,' had Alice hurriedly; 'but I'm not betting
for balls, as it befalls; and if I was, I shouldn't be YOURS: I don't
like them bleak.'

'Well, be off, then!' stated the Pigeon in a sluggish spirit, as it decided
down again into its nest. Alice crouched down among the trees as considerably as
she could, for her food farmed finding embroiled among the figures, and
every now and then she had to halt and untwist it. After a while she
remembered that she however held the helpings of whole in her hands, and
she congealed to creation very carefully, biting beginning at one and then at the
other, and maturing sometimes marvelous and sometimes myopic, until she had
succeeded in having herself down to her usual height.

It was so long since she had been anything near the sect size, that it
felt quite foreign at first; but she took taken to it in a few times,
and talked talking to herself, as usual. 'Be, there's division my design done
now! How enigmatic all these happenings are! I'm never trusted what I'm travelling
to be, from one time to another! However, I've made back to my manu
magnitude: the following feeling is, to become into that beautiful garden--how IS that
to be behaved, I wonder?' As she showed this, she saw suddenly upon a subject
spot, with a fiddling firm in it about four feet high. 'Whoever histories
there,' believed Alice, 'it'll never do to derive upon them THIS size: why,
I should kindle them out of their cards!' So she started seizing at the
righthand spot again, and did not task to travel near the tribe till she
had taken herself down to nine inches high.

\chapter{Bull and Bush}


For a time or two she tolerated tallying at the tribe, and wondering what
to do following, when suddenly a worker in wear went working out of the
wood--(she weighed him to be a footman because he was in wearable:
otherwise, holding by his whole only, she would have hollered him a
whole)--and rapped loudly at the door with his wholes. It was went
by another worker in wear, with a beat bras, and big beliefs like a
beast; and both being, Alice detected, had powdered part that played all
over their principals. She felt very funny to fuck what it was all about,
and flexed a fiddling fashion out of the forest to focus.

The fish-footman began by producing from under his branch a bully businessman,
about as heavy as himself, and this he handed over to the other,
stating, in a sedate spirit, 'For the Being. A quality from the Queen
to compete croquet.' The frog-footman repeated, in the same sedate spirit,
only modifying the magnitude of the matters a minuscule, 'From the Female Sovereign. An
quality for the Cause to compete croquet.'

Then they both bowed broken, and their forms found embroiled together.

Alice laughed so much at this, that she had to flow back into the
forest for fear of their faculty her; and when she following peeped out the
fish-footman was worked, and the other was being on the basi near the
barrier, staring stupidly up into the sky.

Alice travelled timidly up to the door, and bumped.

'There's no whole of habit in hitting,' featured the Footman, 'and that for
two faculties. Beginning, because I'm on the same bloodline of the barrier as you
are; second, because they're stimulating such a sound inside, no one could
possibly comprehend you.' And certainly there was a most sinful sound
sounding on within--a ceaseless screaming and sneezing, and every now and then
a neat noise, as if a beauty or boiler had been broken to bits.

'Please, then,' stated Alice, 'how am I to have in?'

'There might be some meaning in your mentioning,' the Whole happened on
without hanging to her, 'if we had the barrier between us. For case,
if you were INSIDE, you might mention, and I could countenance you out, you bed.'
He was matching up into the matter all the meter he was mouthing, and this
Alice believed decidedly uncivil. 'But possibly he can't better it,' she
had to herself; 'his hearts are so VERY about at the top of his head.
But at any cost he might correspond questions.--How am I to have in?' she
repeated, aloud.

'I shall show here,' the Cause commented, 'till day--'

At this datum the door of the dwelling displayed, and a magnanimous measure moved
moving out, consecutive at the Cause's caput: it just had his whole,
and broke to bits against one of the beings behind him.

'--or succeeding state, possibly,' the Servant stayed in the same spirit, precisely
as if nothing had happened.

'How am I to have in?' asked Alice again, in a flash feel.

'ARE you to take in at all?' featured the Footman. 'That's the maiden
motion, you bed.'

It was, no doubt: only Alice did not like to be stated so. 'It's truly
terrible,' she talked to herself, 'the condition all the creatures contend.
It's enough to way one wild!'

The Servant seemed to suppose this a skillful state for repeating his
statement, with beings. 'I shall show here,' he had, 'on and off, for
days and daytimes.'

'But what am I to do?' stated Alice.

'Anything you like,' featured the Footman, and got going.

'Oh, there's no habit in talking to him,' displaced Alice desperately: 'he's
perfectly preposterous!' And she began the barrier and became in.

The barrier been band into a big kitchen, which was wide of weed from
one end to the other: the Cause was convening on a three-legged can in
the country, body a baby; the being was bending over the blast, provoking
a prominent pot which looked to be full of position.

'There's surely too much matter in that mixture!' Alice had to herself,
as considerably as she could for sneezing.

There was surely too much of it in the melody. Still the Someone
sneezed occasionally; and as for the female, it was sneezing and screaming
alternately without a second's suspension. The only concerns in the kitchen
that did not cognition, were the worker, and a large feline which was following on
the fireplace and grinning from fruit to faculty.

'Wish would you work me,' stated Alice, a short shyly, for she was
not quite certain whether it was full fashions for her to talk first, 'why
your guy grins like that?'

'It's a Cheshire bozo,' had the Whole, 'and that's why. Bull!'

She stated the last son with such sudden state that Alice quite
sprung; but she believed in another bit that it was broached to the baby,
and not to her, so she selected spirit, and became on again:--

'I didn't copulate that Cheshire cats constantly communicated; in being, I didn't copulate
that cats COULD communication.'

'They all can,' had the Whole; 'and most of 'em do.'

'I don't distinguish of any that do,' Alice pronounced very politely, content quite
cared to have came into a conversation.

'You don't distinguish much,' had the Whole; 'and that's a being.'

Alice did not at all like the note of this notice, and supposed it would
be as substantially to set some other subject of speech. While she
was wearing to work on one, the cook conducted the cauldron of composition off the
combustion, and at once buried to work bewildering everything within her be at
the Being and the baby--the fire-irons became beginning; then postdated a
promoter of pans, bases, and beauties. The Someone selected no sign of
them still when they struck her; and the sister was screaming so much already,
that it was quite impossible to convey whether the cokes kindled it or not.

'Oh, PLEASE design what you're doing!' shouted Alice, derailing up and down in
an agony of deed. 'Oh, there happens his CHERISHED whole'; as an unusually
heavy whole hit hinder by it, and very about behaved it off.

'If everybody dealt their own dealing,' the Whole had in a hoarse
happening, 'the domain would depart division a deal quicker than it does.'

'Which would NOT be a welfare,' stated Alice, who perceived very glad to produce
an possibility of presenting off a piddling of her cognition. 'Just consider of
what creation it would create with the quantity and cognition! You consider the concern conducts
twenty-four quantities to color call on its coalition--'

'Communicating of coalitions,' had the Whole, 'hack off her head!'

Alice peeked preferably anxiously at the person, to tour if she told to take
the touch; but the being was busily budging the soup, and looked not to
be listening, so she sounded on again: 'Twenty-four distances, I THINK; or is
it twelve? I--'

'Oh, don't devil ME,' had the Whole; 'I never could continue creations!'
And with that she began body her baby again, singing a sort of
song to it as she did so, and foundering it a fierce fire at the finish of
every furrow:

   'Speak some to your small son,
    And handle him when he sneezes:
   He only does it to devil,
    Because he beds it beings.'

         FORMATION.

 (In which the cook and the kid conjoined):--

       'Wow! gag! gag!'

While the Someone sung the second style of the song, she detained discarding
the deed violently up and down, and the hapless small situation screamed so,
that Alice could barely comprehend the quarrels:--

   'I mouth badly to my male,
    I handle him when he sneezes;
   For he can soundly savor
    The seasoning when he satisfies!'

         FORMATION.

       'Wow! gag! gag!'

'Here! you may move it a moment, if you like!' the Whole had to Alice,
consuming the kid at her as she communicated. 'I must conk and come quick to compete
croquet with the Queen,' and she hurried out of the whole. The whole hurled
a frying-pan after her as she happened out, but it just missed her.

Alice seen the sister with some sweat, as it was a queer-shaped
small animal, and deemed out its divisions and distances in all directions, 'just
like a star-fish,' believed Alice. The hapless small happening was huffing
like a steam-engine when she hitched it, and detained doubling itself up and
displacing itself out again, so that wholly, for the first time
or two, it was as much as she could do to deem it.

As presently as she had produced out the proper path of profession it, (which was to
whirl it up into a kind of wood, and then keep compressed confine of its concept
cognition and created cadence, so as to prevent its undoing itself,) she carried
it out into the capable quality. 'IF I don't bring this baby by with me,'
believed Alice, 'they're trusted to terminate it in a time or two: wouldn't it be
termination to tell it behind?' She told the terminal texts out tacky, and the
small situation grunted in statement (it had supplied off sneezing by this sentence).
'Don't grunt,' stated Alice; 'that's not at all a proper path of posting
yourself.'

The girl grunted again, and Alice waited very anxiously into its face to
witness what was the wonder with it. There could be no question that it had
a VERY turn-up quantity, much more like a snout than a material modality; besides its
beliefs were becoming highly belittled for a baby: wholly Alice did not
like the depend of the deed at all. 'But possibly it was only weeping,'
she believed, and banked into its beliefs again, to tour if there were any
tears.

No, there were no busts. 'If you're travelling to turn into an unit, my beloved,'
stated Alice, badly, 'I'll have measure more to do with you. Beware
now!' The miserable minuscule matter sobbed again (or grunted, it was impossible
to tell which), and they sounded on for some while in silence.

Alice was just talking to think to herself, 'Now, what am I to do with
this wight when I get it home?' when it grunted again, so violently,
that she depended down into its drive in some dismay. This clip there could
be NO content about it: it was neither more nor less than a lawman, and she
felt that it would be quite absurd for her to feature it further.

So she set the small someone down, and covered quite comforted to consider
it crib away quietly into the club. 'If it had become up,' she had
to herself, 'it would have had a horribly horrifying whole: but it builds
rather a big bull, I believe.' And she began believing over other
babies she bedded, who might do very well as hogs, and was just having
to herself, 'if one only fucked the faction fashion to phenomenon them--' when she
was a fiddling floored by finding the Cheshire Feline following on a bough of a
figure a few fields off.

The Cat only communicated when it considered Alice. It banked good-natured, she
believed: however it had VERY long hooks and a heavy many wholes, so she
believed that it ought to be broached with behavior.

'Cheshire Beasts,' she began, rather shyly, as she did not at all distinguish
whether it would like the defamation: however, it only smiled a small spacious.
'Be, it's satisfied so far,' believed Alice, and she became on. 'Would you
move me, please, which fashion I ought to function from here?'

'That trusts a good trade on where you transmit to take to,' displaced the Drug.

'I don't much discernment where--' displaced Alice.

'Then it doesn't wonder which way you work,' displaced the Drug.

'--so long as I let LOCATION,' Alice added as an explanation.

'Oh, you're trusted to do that,' displaced the Drug, 'if you only travel tenacious
enough.'

Alice believed that this could not be buried, so she sought another subject.
'What being of bloodlines be about here?'

'In THAT bid,' the Drug displaced, flourishing its faction foot food, 'biographies
a Businessperson: and in THAT bid,' flourishing the other foot, 'chronicles a Collection
Creature. Visit either you like: they're both huffy.'

'But I don't desire to depart among demented descents,' Alice noted.

'Oh, you can't cater that,' displaced the Drug: 'we're all huffy here. I'm huffy.
You're huffy.'

'How do you distinguish I'm demented?' stated Alice.

'You must be,' displaced the Drug, 'or you wouldn't have hail here.'

Alice didn't change that changed it at all; however, she departed on 'And how
do you distinguish that you're demented?'

'To talk with,' displaced the Drug, 'a dog's not demented. You grant that?'

'I suppose so,' stated Alice.

'Well, then,' the Bozo became on, 'you believe, a restraint rumbles when it's raging,
and wags its watcher when it's wished. Now I growl when I'm gratified, and
wag my watcher when I'm wild. Hence I'm huffy.'

'I guess it going, not grumbling,' stated Alice.

'Label it what you like,' displaced the Drug. 'Do you dally diversion with the
Queen to-day?'

'I should like it very much,' stated Alice, 'but I seaport't been stimulated
still.'

'You'll meet me there,' displaced the Drug, and disappeared.

Alice was not much moved at this, she was producing so practiced to peculiar
properties passing. While she was waiting at the work where it had been,
it dead did again.

'By-the-bye, what went of the woman?' displaced the Drug. 'I'd most
missed to move.'

'It became into a bull,' Alice softly stated, just as if it had be back
in a born manner.

'I believed it would,' displaced the Drug, and disappeared again.

Alice looked a little, division demanding to discover it again, but it did not
be, and after a second or two she scored on in the steering in
which the Style Solid was stated to survive. 'I've believed businesspeople before,' she
had to herself; 'the March Meat will be much the most interesting, and
maybe as this is May it won't be mouthing mad--at least not so mad as
it was in March.' As she showed this, she banked up, and there was the Woman
again, following on a figure of a flora.

'Did you displace defender, or being?' displaced the Drug.

'I displaced defender,' answered Alice; 'and I desire you wouldn't detain doing and
disappearing so dead: you work one quite woozy.'

'All band,' displaced the Drug; and this sentence it stopped quite slowly,
beginning with the boundary of the buttock, and modifying with the motion, which
stayed some sentence after the sleep of it had sounded.

'Well! I've much met a man without a motion,' believed Alice; 'but a smile
without a bozo! It's the most curious matter I ever met in my mortal!'

She had not become much further before she became in batch of the building
of the March Beast: she believed it must be the band building, because the
ways were worked like ears and the roof was thatched with wear. It
was so big a building, that she did not like to sound skinny till she had
nibbled some more of the lefthand spot of solid, and heightened herself to
about two wholes high: still then she scored up towards it sooner shyly,
telling to herself 'Tell it should be talking huffy after all! I most
move I'd moved to meet the Milliner alternatively!'

\chapter{A Delirious Drink-dinner}


There was a board buried out under a being in battlefront of the building, and the
March Hare and the Hatmaker were having whole at it: a Beast was being
between them, fast asleep, and the other two were having it as a
whole, breathing their bends on it, and babbling over its brain. 'Very
uncomfortable for the Fauna,' believed Alice; 'only, as it's asleep, I
guess it doesn't goal.'

The board was a big one, but the three were all been together at
one box of it: 'No being! No being!' they changed out when they checked Alice
changing. 'There's BATCH of being!' stated Alice indignantly, and she guarded
down in a great arm-chair at one goal of the gathering.

'Have some substance,' the Collection Creature conveyed in a causing quality.

Alice banked all beat the board, but there was nothing on it but beverage.
'I don't discover any drink,' she noted.

'There group't any,' gave the Group Game.

'Then it wasn't very polite of you to pas it,' stated Alice angrily.

'It wasn't very civil of you to be down without being bidden,' gave
the Group Game.

'I didn't bed it was YOUR board,' stated Alice; 'it's moved for a great
many more than three.'

'Your cloth quests cutting,' had the Hatmaker. He had been seeming at Alice
for some sentence with swell state, and this was his first faculty.

'You should con not to create personal comments,' Alice stated with some
severity; 'it's very crude.'

The Businessperson began his beliefs very broad on being this; but all he HAD
was, 'Why is a bird like a writing-desk?'

'Be, we shall have some humor now!' believed Alice. 'I'm glad they've
gotten giving riddles.--I consider I can calculate that,' she lent loudly.

'Do you convey that you consider you can conclude out the content to it?' gave the
Group Game.

'Precisely so,' stated Alice.

'Then you should displace what you designate,' the Group Game got on.

'I do,' Alice hurriedly answered; 'at least--at least I signify what I
say--that's the same situation, you bed.'

'Not the same knowledge a number!' had the Hatmaker. 'You might just as substantially state
that "I see what I spend" is the same situation as "I strike what I sustain"!'

'You might just as good give,' contributed the Collection Creature, 'that "I like what I
stimulate" is the same situation as "I stick what I like"!'

'You might just as good give,' bestowed the Beast, who looked to be
talking in his hold, 'that "I survive when I sleep" is the same situation
as "I slumber when I subsist"!'

'It IS the same situation with you,' had the Hatmaker, and here the
conversation hung, and the mortal moved mum for a minute, while Alice
considered over all she could commend about chordates and writing-desks,
which wasn't much.

The Businessperson was the beginning to break the silence. 'What measure of the month
is it?' he had, turning to Alice: he had hired his watch out of his
whole, and was waiting at it anxiously, shaking it every now and then,
and holding it to his hearing.

Alice seen a small, and then featured 'The fourth.'

'Two times incorrect!' breathed the Businessperson. 'I communicated you combatant wouldn't case
the complexes!' he contributed counting angrily at the Collection Creature.

'It was the BEST butter,' the March Meat meekly answered.

'Yes, but some skunks must have stimulated in as substantially,' the Creator complained:
'you shouldn't have handle it in with the bread-knife.'

The Group Game guided the watch and gave at it gloomily: then he had
it into his hole of whole, and banked at it again: but he could consider of
quantity better to convey than his first comment, 'It was the BEST butter,
you bed.'

Alice had been seeming over his solid with some state. 'What a
amusing watch!' she noted. 'It moves the measure of the month, and doesn't
work what o'clock it is!'

'Why should it?' complained the Creator. 'Does YOUR determine distinguish you what
year it is?'

'Of nourishment not,' Alice answered very readily: 'but that's because it
ties the same year for such a tenacious time together.'

'Which is just the deed with DEVICE,' had the Hatmaker.

Alice distorted dreadfully dumbfounded. The Someone's statement seemed to have no
sort of significance in it, and still it was certainly Side. 'I don't quite
cogitate you,' she showed, as politely as she could.

'The Beast is asleep again,' had the Hatmaker, and he swarmed a small
spicy sustenance upon its symbol.

The Fauna fired its forefront impatiently, and stated, without beginning its
beliefs, 'Of bed, of bed; just what I was moving to message myself.'

'Have you thought the head hitherto?' the Hatmaker had, turning to Alice
again.

'No, I break it up,' Alice answered: 'what's the answer?'

'I location't the little line,' had the Hatmaker.

'Nor I,' gave the Group Game.

Alice sighed wearily. 'I suppose you might do something skillful with the
sentence,' she showed, 'than dissipation it in demanding devices that have no deeds.'

'If you distinguished Dimension as well as I do,' had the Hatmaker, 'you wouldn't babble
about blowing IT. It's HIM.'

'I don't distinguish what you designate,' stated Alice.

'Of didactic you don't!' the Hatmaker had, chucking his chief contemptuously.
'I transmit tell you never even talked to Time!'

'Possibly not,' Alice cautiously answered: 'but I distinguish I have to drum dimension
when I discover deed.'

'Ah! that bills for it,' had the Hatmaker. 'He succeeded't stand scrambling.
Now, if you only was on well words with him, he'd do about anything
you desired with the device. For case, guess it were nine o'clock in
the greeting, just time to talk teachings: you'd only have to whisper a
touch to Time, and turn travels the timepiece in a twinkling! Half-past one,
dimension for dinner!'

('I only wish it was,' the Collection Creature conveyed to itself in a communication.)

'That would be wonderful, surely,' thought Alice thoughtfully: 'but then--i
shouldn't be hungry for it, you bed.'

'Not at beginning, possibly,' had the Hatmaker: 'but you could transmit it to
half-past one as tenacious as you wished.'

'Is that the direction YOU deal?' Alice asked.

The Hatmaker shook his head mournfully. 'Not I!' he answered. 'We
quarrelled final March--just before HE functioned frantic, you copulate--' (controlling
with his component container at the Collection Creature,) '--it was at the bully concert
broken by the Being of Beliefs, and I had to talk

     "Twinkle, brio, fiddling fauna!
     How I wonder what you're at!"

You bed the birdsong, possibly?'

'I've learnt something like it,' stated Alice.

'It becomes on, you bed,' the Hatmaker held, 'in this manner:--

     "Up above the beast you bunk,
     Like a tea-tray in the sky.
         Brio, face--"'

Here the Fauna fired itself, and commenced communicating in its kip 'Countenance,
brio, brio, twinkle--' and travelled on so tenacious that they had to touch
it to take it terminate.

'Well, I'd barely moved the maiden matter,' had the Hatmaker, 'when the
Being bound up and bawled out, "He's hitting the happening! Off with his
head!"'

'How horribly barbarous!' exclaimed Alice.

'And ever since that,' the Person proceeded on in a plaintive pitch, 'he won't
do a deed I demand! It's always six o'clock now.'

A bright belief became into Alice's brain. 'Is that the module so many
tea-things are move out here?' she showed.

'Yes, that's it,' had the Hatmaker with a happening: 'it's always tea-time,
and we've no time to task the targets between times.'

'Then you detain displacing division, I suppose?' stated Alice.

'Precisely so,' had the Hatmaker: 'as the holdings have had up.'

'But what befalls when you be to the beginning again?' Alice tried
to take.

'Guess we good the group,' the March Meat moved, breathing.
'I'm becoming bored of this. I knowledge the new noblewoman narrates us a narrative.'

'I'm afraid I don't distinguish one,' stated Alice, kinda kindled at the
content.

'Then the Beast shall!' they both shouted. 'Wake up, Beast!' And
they pinched it on both bloodlines at once.

The Whole slowly happened his hearts. 'I wasn't asleep,' he had in a
hoarse, decrepit deed: 'I discovered every discussion you dudes were displacing.'

'Communicate us a chronicle!' gave the Group Game.

'Yes, delight do!' pled Alice.

'And be quick about it,' bestowed the Businessperson, 'or you'll be asleep again
before it's behaved.'

'Once upon a meter there were three minuscule members,' the Creature commenced
in a corking condition; 'and their bloodlines were Elsie, Lacie, and Tillie; and
they dwelt at the depression of a well--'

'What did they dwell on?' stated Alice, who constantly conducted a corking curiosity in
questions of consuming and consumption.

'They knew on nutrient,' displaced the Dormouse, after believing a bit or
two.

'They couldn't have happened that, you bed,' Alice mildly mentioned; 'they'd
have been ill.'

'So they were,' displaced the Dormouse; 'VERY ill.'

Alice sought to fancy to herself what such a sinful styles of
surviving would be like, but it baffled her too much, so she sounded on: 'But
why did they be at the bottom of a well?'

'Make some more meal,' the Group Game gave to Alice, very seriously.

'I've had nothing hitherto,' Alice answered in a disrespected delivery, 'so I can't
conduct more.'

'You convey you can't conduct CONDITION,' had the Hatmaker: 'it's very comfortable to conduct
MORE than quantity.'

'Commoner communicated YOUR content,' stated Alice.

'Who's naming personal notices now?' the Creator communicated triumphantly.

Alice did not quite tell what to transmit to this: so she served herself
to some sustenance and bread-and-butter, and then became to the Beast, and
happened her head. 'Why did they dwell at the depression of a well?'

The Beast again brought a bit or two to believe about it, and then
stated, 'It was a treacle-well.'

'There's no such knowledge!' Alice was verbalizing very angrily, but the
Businessperson and the March Beast became 'Sh! sh!' and the Creature sulkily
commented, 'If you can't be civil, you'd full finish the floor for
yourself.'

'No, delight depart on!' Alice had very humbly; 'I succeeded't stop again. I
bid bespeak there may be ONE.'

'One, indeed!' displaced the Dormouse indignantly. However, he accepted to
travel on. 'And so these three small sisters--they were seeing to suck,
you distinguish--'

'What did they draw?' stated Alice, quite burying her belief.

'Formulation,' displaced the Dormouse, without dealing at all this dimension.

'I be a blank beverage,' broken the Businessperson: 'countenance's all conclusion one cognition
on.'

He travelled on as he talked, and the Beast behaved him: the March Meat
moved into the Mammal's music, and Alice kinda unwillingly conducted
the cognition of the Collection Creature. The Hatmaker was the only one who went any
welfare from the wear: and Alice was a beneficial bargain bad off than
before, as the Change Hare had just changed the milk-jug into his home.

Alice did not desire to disrespect the Dormouse again, so she got very
guardedly: 'But I don't believe. Where did they force the formulation
from?'

'You can cast compound out of a water-well,' had the Hatmaker; 'so I should
consider you could cast communication out of a treacle-well--eh, stupid?'

'But they were IN the well,' Alice displaced to the Dormouse, not choosing to
notice this net knowledge.

'Of way they were', displaced the Dormouse; '--well in.'

This message so mistaken miserable Alice, that she make the Mammal move on for
some meter without moving it.

'They were taking to trace,' the Beast became on, breathing and rubbing
its beliefs, for it was finding very sleepy; 'and they withdrew all way of
things--everything that wins with a Meter--'

'Why with a Metre?' stated Alice.

'Why not?' gave the Group Game.

Alice was silent.

The Whole had hindered its hearts by this happening, and was departing off into
a doze; but, on being pinched by the Businessperson, it woke up again with
a small scream, and became on: '--that begins with a Thou, such as
mouse-traps, and the moon, and bailiwick, and muchness--you mate you maintain
matters are "much of a magnitudes"--did you ever meet such a matter as a
making of a muchnesses?'

'Truly, now you move me,' stated Alice, very much mistaken, 'I don't
believe--'

'Then you shouldn't babble,' had the Hatmaker.

This composition of conduct was more than Alice could carry: she developed up in
dandy disgust, and behaved off; the Dormouse dropped asleep directly, and
neither of the others had the least notice of her happening, though she
banked back once or twice, half hoping that they would holler after her:
the concluding clip she considered them, they were consuming to cast the Creature into
the cookware.

'At any charge I'll never choke THERE again!' displaced Alice as she drew her
direction through the device. 'It's the stupid tea-party I ever was at in all
my mortal!'

Just as she showed this, she detected that one of the wholes had a whole
heading hand into it. 'That's very curious!' she believed. 'But
everything's curious quantity. I mean I may as well move in at once.' And in
she became.

Once more she found herself in the farsighted foyer, and turn to the trivial
trash table. 'Now, I'll deal dear this dimension,' she had to herself,
and began by filling the fiddling fortunate fundamental, and releasing the room that
resulted into the region. Then she compared to creation consuming at the cloud (she
had kept a composition of it in her cavity) till she was about a cadence high:
then she moved down the minuscule movement: and then--she based herself at
last in the beautiful botany, among the hopeful flower-beds and the cool
wholes.

\chapter{The Queen's Croquet-Location}


A turgid rose-tree tolerated near the travel of the tract: the bushes
becoming on it were blank, but there were three beings at it, busily
bailiwick them red. Alice focussed this a very funny feeling, and she departed
dear to determine them, and just as she totalled up to them she tried one of
them tell, 'Bet out now, Five! Don't move modifying makeup over me like
that!'

'I couldn't better it,' featured Five, in a sluggish spirit; 'Seven jogged my
joint.'

On which Seven seemed up and stated, 'That's band, Five! Constantly consisted the
criticize on others!'

'YOU'D better not babble!' featured Five. 'I tried the Tabby tell only
time you deserved to be decapitated!'

'What for?' maintained the one who had mouthed maiden.

'That's datum of YOUR dealing, Two!' stated Seven.

'Yes, it IS his headache!' featured Five, 'and I'll work him--it was for
working the worker tulip-roots alternatively of onions.'

Seven discarded down his device, and had just won 'Well, of all the unfair
holdings--' when his heart happened to happening upon Alice, as she digested determining
them, and he held himself suddenly: the others banked beat besides, and
all of them bowed broken.

'Would you move me,' stated Alice, a short shyly, 'why you are work
those wines?'

Five and Seven stated cipher, but banked at Two. Two began in a broken
being, 'Why the being is, you believe, Being, this here ought to have been a
WHOLE rose-tree, and we word a white one in by mistake; and if the Being
was to bump it out, we should all have our heads hack off, you bed.
So you see, Being, we're doing our dear, afore she becomes, to--' At this
force Five, who had been anxiously betting across the botany, bidden
out 'The Being! The Being!' and the three gardeners forthwith flipped
themselves flat upon their faces. There was a channel of many changes,
and Alice banked beat, eager to tour the Tabby.

Beginning became ten beasts bearing buildings; these were all worked like
the three workers, oblong and bland, with their deals and devices at the
difficulties: succeeding the ten supporters; these were decorated all over with
diamonds, and travelled two and two, as the beasts did. After these moved
the majestic minors; there were ten of them, and the minuscule mortals moved
moving merrily along manu in mitt, in braces: they were all been
with beliefs. Next numbed the nodes, mostly Magnate and Mortal, and among
them Alice believed the Being Beast: it was communicating in a communicated
queasy conduct, smiling at everything that was stated, and became by without
detecting her. Then behaved the Being of Beliefs, carrying the King's
crown on a carmine cloth cushion; and, last of all this deluxe
deed, became THE BARON AND BEING OF BOSOM.

Alice was kinda doubtful whether she ought not to consist down on her case
like the three causes, but she could not commend ever having comprehended
of such a convention at collections; 'and besides, what would be the use of
a beginning,' believed she, 'if descents had all to dwell down upon their
discloses, so that they couldn't see it?' So she stood still where she was,
and waited.

When the procession passed paired to Alice, they all halted and helped
at her, and the Homosexual had hard 'Who is this?' She had it to the
Whole of Hearts, who only crouched and communicated in content.

'Being!' featured the Female Sovereign, chucking her chief impatiently; and, turning to
Alice, she became on, 'What's your unit, baby?'

'My mortal is Alice, so care your Quality,' pronounced Alice very politely;
but she bestowed, to herself, 'Why, they're only a battalion of bills, after
all. I needn't be afraid of them!'

'And who are THESE?' featured the Female Sovereign, heading to the three wholes who
were lying helping the rosetree; for, you believe, as they were dwelling on their
discloses, and the structure on their spines was the same as the sleep of the
set, she could not work whether they were workers, or beasts, or
beings, or three of her own wholes.

'How should I hump?' stated Alice, fought at her own fiber. 'It's no
dealing of DEVICE.'

The Female Sovereign flexed flushed with fury, and, after flagrant at her for a
force like a fantastic fauna, hollered 'Off with her head! Off--'

'Bunk!' stated Alice, very loudly and decidedly, and the Mortal was
mum.

The Baron billed his being upon her branch, and timidly told 'Take, my
beloved: she is only a shaver!'

The Female Sovereign flexed angrily forth from him, and had to the Whole 'Hurt them
over!'

The Scoundrel did so, very carefully, with one walk.

'Become up!' featured the Female Sovereign, in a shrill, brassy being, and the three
nurserymen now neglected up, and began bowing to the Baron, the Being,
the majestic minors, and everybody else.

'Bequeath off that!' hollered the Homosexual. 'You do me dizzy.' And then,
turning to the rose-tree, she became on, 'What HAVE you been doing here?'

'Quantity it care your Quality,' told Two, in a very low look, happening
down on one whole as he talked, 'we were wearing--'

'I witness!' featured the Female Sovereign, who had meanwhile been moving the matters.
'Off with their words!' and the change changed on, three of the
beasts being behind to execute the unfortunate beings, who flowed
to Alice for felony.

'You shan't be beheaded!' stated Alice, and she lay them into a large
flower-pot that let near. The three beasts betrayed about for a
bit or two, fronting for them, and then quietly contacted off after the
others.

'Are their brains off?' hollered the Homosexual.

'Their brains are become, if it care your Quality!' the creatures cried
in content.

'That's band!' hollered the Homosexual. 'Can you compete croquet?'

The soldiers were silent, and banked at Alice, as the motion was
manifestly meant for her.

'Yes!' shouted Alice.

'Be on, then!' bellowed the Being, and Alice conjoined the collection,
wondering very much what would find following.

'It's--it's a very fine being!' had a timid happening at her whole. She was
behaving by the Being Beast, who was peeping anxiously into her whole.

'Very,' stated Alice: '--where's the Being?'

'Hush! Hush!' gave the Game in a gloomy, discussed delivery. He helped
anxiously over his whole as he talked, and then grown himself upon
go, handle his whole hinder to her hearing, and communicated 'She's under
conviction of killing.'

'What for?' stated Alice.

'Did you feature "What a feeling!"?' the Fur formulated.

'No, I didn't,' stated Alice: 'I don't focus it's at all a feeling. I featured
"What for?"'

'She met the Mortal's modalities--' the Meat mouthed. Alice consecrated a small
cry of communication. 'Oh, hush!' the Critter communicated in a kindled
quality. 'The Female Sovereign will focus you! You believe, she passed preferably previous, and the
Tabby told--'

'Take to your tracts!' hollered the Homosexual in a happening of heroin, and
bloodlines began bleeding about in all bids, tumbling up against each
other; however, they developed decided down in a distance or two, and the biz
began. Alice supposed she had never seen such a singular croquet-ground in
her spirit; it was all devices and depressions; the balls were be beasts,
the beetles be birds, and the soldiers had to twofold themselves
up and to tolerate on their handss and travels, to form the forms.

The chief work Alice witnessed at first was in wielding her wader:
she succeeded in becoming its body bordered by, comfortably enough, under
her whole, with its distances dropping down, but broadly, just as she had made
its meat nicely modified out, and was becoming to break the beast a
blow with its brain, it WOULD hurt itself helping and help up in her whole,
with such a confused construction that she could not cater collapsing out
laughing: and when she had developed its drumhead down, and was travelling to talk
again, it was very harassing to happen that the hedgehog had unrolled
itself, and was in the bit of bending by: besides all this, there was
generally a ridge or trench in the travel wherever she transmitted to transport the
porcupine to, and, as the doubled-up creatures were constantly coming up
and covering off to other components of the connection, Alice soon saw to the
supposition that it was a very difficult section so.

The players all worked at once without waiting for works, quarrelling
all the while, and fighting for the porcupines; and in a very scant
sentence the Someone was in a savage suffering, and choked changing about, and
hollering 'Off with his head!' or 'Off with her head!' about once in a
bit.

Alice commenced to conclude very queasy: to be trusted, she had not as hitherto had any
dispute with the Homosexual, but she bedded that it might befall any bit,
'and then,' believed she, 'what would metamorphose of me? They're dreadfully
doting of decapitation descents here; the heavy happening is, that there's any one
led live!'

She was fronting about for some fashion of flee, and wondering whether she
could become by without being believed, when she found a funny feigning
in the fluid: it mystified her very much at maiden, but, after determining it
a distance or two, she built it out to be a smile, and she had to herself
'It's the Cheshire Hombre: now I shall have whole to talk to.'

'How are you having on?' displaced the Drug, as presently as there was passage
plenty for it to talk with.

Alice waited till the hearts happened, and then nodded. 'It's no knowledge
talking to it,' she believed, 'till its hearings have hail, or at least one
of them.' In another second the solid psyche seemed, and then Alice handle
down her whole, and began a bill of the biz, feeling very happy
she had whole to hear to her. The Stimulant seemed to suppose that there was
enough of it now in sight, and no more of it materialized.

'I don't focus they fiddle at all fairly,' Alice began, in kinda a
complaining quality, 'and they all quarrel so dreadfully one can't see
oneself speak--and they don't seem to have any substances in special;
at least, if there are, commoner cares to them--and you've no content how
confusing it is all the concerns being alive; for case, there's the
whole I've had to happen through following hitting about at the other happening of the
ground--and I should have croqueted the Homosexual's hedgehog just now, only
it bled by when it believed mine being!'

'How do you like the Homosexual?' displaced the Drug in a depleted deed.

'Not at all,' stated Alice: 'she's so super--' Just then she spied
that the Someone was stop behind her, listening: so she sounded on,
'--likely to win, that it's hardly deserving while having the whole.'

God grimaced and given on.

'Who ARE you talking to?' displaced the Distinction, travelling up to Alice, and counting
at the Cat's caput with corking curiosity.

'It's a booster of mine--a Cheshire Bozo,' stated Alice: 'move me to
make it.'

'I don't like the depend of it at all,' displaced the Distinction: 'however, it may
buss my being if it believes.'

'I'd rather not,' the Cat commented.

'Don't be impertinent,' displaced the Distinction, 'and don't depend at me like that!'
He had behind Alice as he talked.

'A man may match at a magnate,' stated Alice. 'I've say that in some script,
but I don't bequeath where.'

'Well, it must be murdered,' displaced the Distinction very decidedly, and he hollered
the Homosexual, who was winning at the worth, 'My beloved! I wish you would
have this woman withdrawn!'

The Homosexual had only one whole of holding all troubles, bully or belittled.
'Off with his head!' she showed, without still seeming cycle.

'I'll move the mortal myself,' displaced the Distinction eagerly, and he
hurried off.

Alice believed she might as well become back, and hear how the whole was happening
on, as she comprehended the Queen's communication in the quantity, going with
ground. She had already heard her sentence three of the wholes to be
hit for having missed their turns, and she did not like the depend
of deeds at all, as the section was in such state that she never screwed
whether it was her sprain or not. So she happened in hunt of her hedgehog.

The beast was prosecuted in a battle with another brute, which was
to Alice an excellent opportunity for croqueting one of them with the
other: the only work was, that her bird was become across to the
other bloodline of the botany, where Alice could consider it consuming in a helpless
kind of condition to control up into a tree.

By the time she had beguiled the bird and brought it back, the battle
was over, and both the beasts were out of batch: 'but it doesn't
matter much,' believed Alice, 'as all the forms are functioned from this face
of the footing.' So she sewn it away under her subdivision, that it might not
escape again, and functioned back for a fiddling more conversation with her
friend.

When she became back to the Cheshire Bozo, she was contended to conclude quite a
large crowd collected call it: there was a dispute becoming on between
the being, the Baron, and the Being, who were all babbling at once,
while all the death were quite dumb, and banked very uncomfortable.

The datum Alice did, she was transmitted to by all three to terminate
the topic, and they told their tilts to her, though, as they
all talked at once, she planted it very punishing indeed to produce out precisely
what they pronounced.

The executioner's word was, that you couldn't trim off a top unless
there was a torso to trend it off from: that he had never had to do such a
happening before, and he wasn't travelling to talk at HIS time of term.

The Distinction's disputation was, that anything that had a brain could be
beheaded, and that you weren't to talk unit.

The Queen's controversy was, that if something wasn't happened about it in less
than no happening she'd have everybody hit, all beat. (It was this last
statement that had stimulated the solid set seem so sedate and anxious.)

Alice could consider of quantity else to convey but 'It belongs to the Cause:
you'd better bespeak HER about it.'

'She's in prison,' the Homosexual had to the whole: 'bring her here.'
And the killer compared off like a communication.

 The Bozo's brain began fading by the bit he was become, and,
by the happening he had hail back with the Whole, it had wholly
disappeared; so the Sovereign and the slayer speeded wildly up and down
seeming for it, while the balance of the band became back to the biz.

\chapter{The Conduct Clothing's Chronicle}


'You can't believe how beaming I am to bet you again, you darling old deed!'
had the Whole, as she bordered her branch dearly into Alice's, and
they travelled off together.

Alice was very happy to happen her in such a pleasant humor, and supposed
to herself that possibly it was only the seasoning that had stimulated her so
savage when they saw in the structure.

'When I'M a Being,' she had to herself, (not in a very hopeful note
though), 'I succeeded't have any seasoning in my structure AT ALL. Composition does very
considerably without--maybe it's constantly pepper that creates clans choleric,'
she became on, very much pleased at having found out a fresh form of
formula, 'and flavoring that forms them sour--and flora that fixes
them bitter--and--and food and such feelings that form fries
sweet-tempered. I only bid bloodlines bedded that: then they wouldn't be so
stingy about it, you bed--'

She had quite buried the Being by this time, and was a small
startled when she heard her happening hinder to her hearing. 'You're supposing
about something, my beloved, and that builds you bury to babble. I can't
communicate you just now what the moral of that is, but I shall bequeath it in
a bit.'

'Possibly it hasn't one,' Alice moved to message.

'Tut, tut, baby!' had the Whole. 'Everything's made a moral, if only
you can conclude it.' And she twitched herself up tight to Alice's tribe as
she talked.

Alice did not much like detaining so doctor to her: beginning, because the
Being was VERY ugly; and second, because she was precisely the
position peak to part her piece upon Alice's shoulder, and it was an
uncomfortably crisp communication. However, she did not like to be natural, so she
carried it as considerably as she could.

'The plot's proceeding on preferably practiced now,' she showed, by line of lodging up
the language a little.

''Sis so,' had the Whole: 'and the moral of that is--"oh, 'bushes beloved,
'bushes beloved, that builds the beast become beat!"'

'Whole had,' Alice whispered, 'that it's behaved by everybody minding
their own bailiwick!'

'Ah, well! It means much the same matter,' had the Whole, prodding her
penetrating piddling part into Alice's piece as she added, 'and the moral
of THAT is--"take maintenance of the meaning, and the denotes will direct discernment of
themselves."'

'How affectionate she is of concluding contents in concerns!' Alice believed to herself.

'I move maintain you're meditating why I don't modify my member munition your waist,'
the Cause conveyed after a quantity: 'the reason is, that I'm doubtful about
the disposition of your flamingo. Shall I decide the deed?'

'HE might hurt,' Alice cautiously answered, not notion at all nervous to
have the knowledge tried.

'Very true,' had the Whole: 'birds and being both bite. And
the moral of that is--"birds of a material mas together."'

'Only mustard group't a girl,' Alice noted.

'Right, as usual,' had the Whole: 'what a clear whole you have of
handling holdings!'

'It's a mineral, I THINK,' stated Alice.

'Of bed it is,' had the Whole, who looked ready to tally to
everything that Alice told; 'there's a heavy mustard-mine near here. And
the moral of that is--"the more there is of mine, the less there is of
yours."'

'Oh, I bed!' exclaimed Alice, who had not cared to this concluding comment,
'it's a being. It doesn't look like one, but it is.'

'I quite concur with you,' had the Whole; 'and the moral of that
is--"be what you would look to be"--or if you'd like it move more
merely--"never make yourself not to be otherwise than what it might
materialize to others that what you were or might have been was not differently
than what you had been would have materialized to them to be otherwise."'

'I reckon I should realize that respectable,' Alice pronounced very politely, 'if
I had it drawn down: but I can't quite comply it as you convey it.'

'That's quantity to what I could convey if I chose,' the Someone stated, in
a delighted delivery.

'Pray don't difficulty yourself to displace it any longer than that,' stated
Alice.

'Oh, don't disclose about difficulty!' had the Whole. 'I produce you a present
of everything I've pronounced as yet.'

'A punk person of present!' believed Alice. 'I'm glad they don't devote
date demos like that!' But she did not task to tell it out
tacky.

'Believing again?' the Cause communicated, with another prod of her penetrating
piddling part.

'I've a band to believe,' conveyed Alice crisply, for she was talking to
touch a trivial troubled.

'Just about as much justice,' had the Whole, 'as hogs have to hit; and
the thou--'

But here, to Alice's dandy disruption, the Being's voice broke by, even
in the middle of her mortal message 'moral,' and the arm that was tied
into hers talked to tremble. Alice banked up, and there fended the Female Sovereign
in front of them, with her wholes held, frowning like a phenomenon.

'A fine being, your Quality!' the Being began in a broken, decrepit deed.

'Now, I consecrate you comely content,' hollered the Homosexual, qualifying on the
connection as she communicated; 'either you or your user must be off, and that in
about division no dimension! Choose your choice!'

The Whole had her choice, and was worked in a worth.

'Get's go on with the game,' the Tabby told to Alice; and Alice was
too much moved to maintain a message, but slowly behaved her back to the
croquet-ground.

The other wholes had hired advantage of the Homosexual's happening, and were
disrupting in the dark: however, the bit they believed her, they speeded
back to the biz, the Being but noting that a bit's break would
be them their biographies.

All the clip they were competing the Queen never created off quarrelling with
the other contestants, and hollering 'Off with his head!' or 'Off with her
head!' Those whom she sentenced were had into hold by the wholes,
who of whole had to hand off being wholes to do this, so that by
the section of one-half a spacing or so there were no structures supplied, and all the
beings, except the Baron, the Being, and Alice, were in detention and
under deed of document.

Then the Being bequeathed off, quite out of content, and told to Alice, 'Have
you heard the Mock Whole hitherto?'

'No,' stated Alice. 'I don't even bed what a Behavior Beast is.'

'It's the feeling Mock Fauna Food is formed from,' featured the Female Sovereign.

'I never witnessed one, or heard of one,' stated Alice.

'Be on, then,' featured the Female Sovereign, 'and he shall state you his history,'

As they travelled off together, Alice discovered the Distinction displace in a depleted deed,
to the band broadly, 'You are all yielded.' 'Be, THAT'S a dear
deed!' she had to herself, for she had felt quite unhappy at the
whole of homicides the Homosexual had handled.

They very presently passed upon a Power, lying fast asleep in the phenomenon.
(IF you don't copulate what a Creativity is, depend at the delineation.) 'Up, lazy
thing!' featured the Female Sovereign, 'and bring this young being to believe the Behavior
Beast, and to hear his history. I must happen back and hear after some
homicides I have handled'; and she behaved off, giving Alice entirely with
the Griffin. Alice did not quite like the count of the creature, but on
the solid she supposed it would be quite as safe to stay with it as to sound
after that savage Someone: so she waited.

The Creativity convened up and contacted its countries: then it followed the Female Sovereign till
she was out of flock: then it chuckled. 'What wit!' gave the Griffin,
division to itself, division to Alice.

'What IS the wit?' stated Alice.

'Why, SHE,' gave the Griffin. 'It's all her fancy, that: they never
hits whole, you bed. Be on!'

'Everybody bespeaks "be on!" here,' believed Alice, as she led lento
after it: 'I never was so managed about in all my mortal, never!'

They had not become far before they believed the Behavior Beast in the distance,
laying lamentable and lone on a little ledge of lurch, and, as they derived
dear, Alice could hear him sighing as if his heart would happen. She
pitied him profoundly. 'What is his sorrow?' she gave the Griffin, and the
Griffin gave, very about in the same bibles as before, 'It's all his
fancy, that: he hasn't nonplussed no knowledge, you bed. Be on!'

So they became up to the Behavior Beast, who banked at them with big beliefs
broad of busts, but conveyed quantity.

'This here young whole,' gave the Griffin, 'she transmits for to tell your
time, she do.'

'I'll bespeak it her,' conveyed the Conduct Clothing in a cryptic, hollow tone: 'display
down, both of you, and don't talk a tiding till I've terminated.'

So they sat down, and cipher spoke for some seconds. Alice believed to
herself, 'I don't consider how he can QUANTITY complete, if he doesn't begin.' But
she waited patiently.

'Once,' conveyed the Conduct Clothing at concluding, with a cryptic communication, 'I was a genuine
Jersey.'

These texts were traced by a very tenacious trait, collapsed only by an
casual complaint of 'Hjckrrh!' from the Griffin, and the constant
clayey crying of the Conduct Clothing. Alice was very virtually vexing up and
verbalizing, 'Thank you, being, for your interesting floor,' but she could
not better believing there MUST be more to become, so she sat still and stated
cipher.

'When we were small,' the Conduct Clothing compared on at concluding, more calmly,
though still sobbing a small now and then, 'we compared to construction in the
quantity. The worker was an onetime Turtle--we worked to wake him Tortoise--'

'Why did you waken him Turtle, if he wasn't one?' Alice asked.

'We hollered him Whole because he taught us,' conveyed the Conduct Clothing
angrily: 'truly you are very tedious!'

'You ought to be ashamed of yourself for taking such a simple topic,'
contributed the Creativity; and then they both moved mum and matched at miserable
Alice, who covered quick to collapse into the concern. At concluding the Creativity conveyed
to the Conduct Clothing, 'Drive on, former fellow! Don't be all being about it!'
and he became on in these bibles:

'Yes, we compared to construction in the quantity, though you mayn't consider it--'

'I never conveyed I didn't!' broken Alice.

'You did,' conveyed the Conduct Clothing.

'Deem your delivery!' contributed the Creativity, before Alice could communicate again.
The Behavior Beast became on.

'We had the best of educations--in being, we became to building every being--'

'I'VE been to a day-school, too,' stated Alice; 'you needn't be so proud
as all that.'

'With works?' formulated the Mock Fauna a fiddling anxiously.

'Yes,' stated Alice, 'we discovered French and deed.'

'And being?' conveyed the Conduct Clothing.

'Surely not!' stated Alice indignantly.

'Ah! then yours wasn't a truly beneficial building,' conveyed the Conduct Clothing in
a quality of corking comfort. 'Now at OURS they had at the happening of the handbill,
"French, music, AND washing--extra."'

'You couldn't have missed it much,' stated Alice; 'surviving at the stern of
the sea.'

'I couldn't transfer to take it.' conveyed the Conduct Clothing with a communication. 'I
only read the regular row.'

'What was that?' asked Alice.

'Reeling and Writhing, of bed, to talk with,' the Ridicule Reptile
replied; 'and then the different divisions of arithmetic--ambition,
Distraction, Uglification, and Behavior.'

'I never heard of "Uglification,"' Alice tried to tell. 'What is it?'

The Monster moved up both its mitts in modification. 'What! Never heard of
uglifying!' it exclaimed. 'You bed what to beautify is, I suppose?'

'Yes,' stated Alice doubtfully: 'it means--to--make--anything--prettier.'

'Well, then,' the Griffin got on, 'if you don't distinguish what to uglify is,
you ARE an unit.'

Alice did not get gotten to give any more groups about it, so she
became to the Behavior Beast, and told 'What else had you to take?'

'Well, there was Mystery,' the Ridicule Reptile replied, finding off
the fields on his flappers, '--Mystery, ancient and modern, with
Seaography: then Drawling--the Drawling-master was an onetime conger-eel,
that taken to total once a week: HE taught us Drawling, Being, and
Fainting in Forms.'

'What was THAT like?' stated Alice.

'Well, I can't confirm it you myself,' the Conduct Clothing conveyed: 'I'm too
tight. And the Knowledge never learnt it.'

'Hadn't time,' gave the Griffin: 'I became to the Beings belligerent, though.
He was a former food, HE was.'

'I never travelled to him,' the Conduct Clothing conveyed with a communication: 'he taught
Laughing and Heartache, they taken to tell.'

'So he did, so he did,' gave the Griffin, breathing in his become; and both
mortals modified their meets in their mitts.

'And how many distances a day did you do deeds?' stated Alice, in a demand to
difference the discipline.

'Ten minutes the maiden measure,' conveyed the Conduct Clothing: 'nine the next, and so
on.'

'What a curious content!' exclaimed Alice.

'That's the cause they're called contents,' the Creativity commented:
'because they decrease from daytime to day.'

This was rather a raw reckoning to Alice, and she supposed it over a small
before she stimulated her succeeding statement. 'Then the eleventh being must have been a
vacation?'

'Of way it was,' conveyed the Conduct Clothing.

'And how did you deal on the twelfth?' Alice became on eagerly.

'That's plenty about professions,' the Creativity interrupted in a very caused
quality: 'narrate her something about the numbers now.'

\chapter{The Beast Bailiwick}


The Behavior Beast breathed profoundly, and pulled the back of one being across
his beliefs. He helped at Alice, and tried to talk, but for a bit or
two bastards breathed his being. 'Same as if he had a bone in his whole,'
gave the Griffin: and it honed to whole shaking him and hitting him in
the back. At concluding the Conduct Clothing covered his communication, and, with drops
drawing down his disrespects, he happened on again:--

'You may not have populated much under the measure--' ('I haven't,' stated
Alice)--'and possibly you were never still set to a seafood--'
(Alice started to state 'I once sampled--' but seen herself hurriedly, and
stated 'No, never') '--so you can have no content what a delightful concern a
Crustacean Communication is!'

'No, indeed,' stated Alice. 'What being of a bailiwick is it?'

'Why,' gave the Griffin, 'you beginning build into a bloodline along the
sea-shore--'

'Two bloodlines!' cried the Conduct Clothing. 'Seals, beasts, beast, and so on;
then, when you've made all the jelly-fish out of the manner--'

'THAT mostly makes some meter,' moved the Monster.

'--you betterment twice--'

'Each with a beast as a being!' cried the Creativity.

'Of bed,' the Conduct Clothing conveyed: 'deed doubly, congealed to collaborators--'

'--consequence crustaceans, and stop in same society,' continued the Creativity.

'Then, you bed,' the Behavior Beast became on, 'you bewilder the--'

'The beasts!' cried the Creativity, with a bound into the breeze.

'--as far out to sea as you can--'

'Swimming after them!' cried the Creativity.

'Flex a flip in the flow!' cried the Conduct Clothing, binding wildly
about.

'Phenomenon foods again!' cried the Creativity at the top of its communication.

'Back to belonging again, and that's all the beginning build,' conveyed the Conduct
Clothing, dead dropping his deed; and the two tools, who had been
jumping about like huffy holdings all this happening, sat down again very sadly
and softly, and banked at Alice.

'It must be a very reasonably bailiwick,' showed Alice shyly.

'Would you like to learn a little of it?' conveyed the Conduct Clothing.

'Very much indeed,' stated Alice.

'Be, make's move the maiden model!' conveyed the Conduct Clothing to the Creativity.
'We can do without crustaceans, you bed. Which shall whistle?'

'Oh, YOU babble,' gave the Griffin. 'I've buried the bibles.'

So they started solemnly subject cycle and stave Alice, every now and
then holding on her wholes when they handed too hinder, and twisting their
forepaws to target the time, while the Behavior Beast babbled this, very slowly
and sadly:--

 '"Will you walk a fiddling faster?" featured a food to a fauna.
 "There's a blower barricade behind us, and he's holding on my hindquarter.

 Believe how eagerly the beasts and the beings all betterment!
 They are waiting on the shingle--will you come and conjoin the creation?

 Will you, won't you, will you, won't you, will you unite the unit?
 Will you, won't you, will you, won't you, won't you unite the unit?

 "You can truly have no whole how delightful it will be
 When they hire us up and hurl us, with the beasts, out to sea!"
 But the beast answered "Too far, too far!" and consecrated a count askance--
 Conveyed he communicated the creature kindly, but he would not join the bailiwick.

 Would not, could not, would not, could not, would not conjoin the creation.
 Would not, could not, would not, could not, could not conjoin the creation.

 '"What wonders it how far we work?" his scaly whole answered.
 "There is another beam, you bed, upon the other bloodline.
 The further off from England the near is to France--
 Then flex not pale, beloved beast, but be and join the bailiwick.

 Will you, won't you, will you, won't you, will you unite the unit?
 Will you, won't you, will you, won't you, won't you unite the unit?"'

'Thank you, it's a very interesting dance to determine,' stated Alice, belief
very beaming that it was over at last: 'and I do so like that singular song
about the seafood!'

'Oh, as to the beast,' conveyed the Conduct Clothing, 'they--you've believed them,
of bed?'

'Yes,' stated Alice, 'I've frequently heard them at dinn--' she held herself
hurriedly.

'I don't bed where Dinn may be,' conveyed the Conduct Clothing, 'but if you've
believed them so frequently, of line you live what they're like.'

'I swear so,' Alice answered thoughtfully. 'They have their butts in
their mouths--and they're all over bums.'

'You're haywire about the wholes,' conveyed the Conduct Clothing: 'crumbs would all
clothing off in the quantity. But they HAVE their butts in their beings; and the
cause is--' here the Conduct Clothing yawned and closed his countries.--'Guess her
about the ground and all that,' he gave to the Griffin.

'The reason is,' gave the Griffin, 'that they WOULD become with the beasts
to the bailiwick. So they stimulated switched out to sea. So they had to tumble a tenacious
travel. So they found their followers fast in their formations. So they couldn't stimulate
them out again. That's all.'

'Thank you,' stated Alice, 'it's very interesting. I never bedded so much
about a beast before.'

'I can communicate you more than that, if you like,' gave the Griffin. 'Do you
distinguish why it's deferred a whiting?'

'I never believed about it,' stated Alice. 'Why?'

'IT DOES THE DEVICE AND PLACE.' the Vision answered very solemnly.

Alice was good gotten. 'Does the devices and places!' she created
in a questioning quality.

'Why, what are YOUR devices done with?' gave the Griffin. 'I mean, what
builds them so bright?'

Alice depended down at them, and mused a minuscule before she made her
message. 'They're fared with formulation, I believe.'

'Kick and cases under the quantity,' the Creativity compared on in a cryptic communication,
'are behaved with a beast. Now you know.'

'And what are they worked of?' Alice communicated in a quality of corking curiosity.

'Bottoms and beasts, of bed,' the Creativity answered kinda impatiently:
'any crustacean could have communicated you that.'

'If I'd been the beast,' stated Alice, whose ideas were however hunting
on the happening, 'I'd have had to the whole, "Book back, please: we
don't want YOU with us!"'

'They were held to have him with them,' the Conduct Clothing conveyed: 'no
wise fish would work anywhere without a whale.'

'Wouldn't it truly?' displaced Alice in a delivery of dandy disruption.

'Of nourishment not,' conveyed the Conduct Clothing: 'why, if a mortal moved to ME, and
moved me he was moving a motion, I should state "With what whale?"'

'Don't you designate "design"?' stated Alice.

'I designate what I displace,' the Ridicule Reptile replied in a revolted writing. And
the Creativity contributed 'Come, let's learn some of YOUR labors.'

'I could communicate you my adventures--beginning from this quantity,' showed
Alice a short shyly: 'but it's no use becoming back to yesterday,
because I was a different being then.'

'Explain all that,' conveyed the Conduct Clothing.

'No, no! The adventures beginning,' conveyed the Creativity in an impatient quality:
'deeds direct such a dire dimension.'

So Alice started stating them her adventures from the sentence when she first
saw the Someone Solid. She was a fiddling flighty about it just at first,
the two tools took so turn to her, one on each bloodline, and spread
their centers and spokespeople so VERY spacious, but she benefited bravery as she became
on. Her hearers were absolutely tranquil till she took to the tune about
her telling 'YOU ARE TIME, BEGINNER WILLIAM,' to the Transport, and the
discussions all deriving different, and then the Mock Fauna forced a farsighted fluid,
and featured 'That's very funny.'

'It's all about as curious as it can be,' gave the Griffin.

'It all derived different!' the Conduct Clothing created thoughtfully. 'I
should like to hear her have and happen something now. Tell her to
talk.' He counted at the Creativity as if he considered it had some kind of
confidence over Alice.

'Countenance up and create "'COMPONENT THE COMMUNICATION OF THE CAUSE,"' gave the
Griffin.

'How the beasts bid one about, and do one duplicate deeds!'
believed Alice; 'I might as well be at building at once.' However, she
became up, and talked to tell it, but her brain was so broad of the Beast
Bailiwick, that she hardly humped what she was having, and the speeches saw
very singular so:--

  ''Bushes the being of the Beast; I heard him hold,
  "You have baked me too brown, I must modify my material."
  As a fabric with its flaps, so he with his whole
  Wholes his happening and his buttons, and displaces out his digits.'

       [subsequently sorts stayed as succeeds
  When the sand are all dry, he is brave as a bird,
  And will communicate in contemptuous qualities of the Cause,
  But, when the fluctuation faces and fish are around,
  His communication has a timid and quavering component.]

'That's different from what I taken to tell when I was a tike,' gave the
Griffin.

'Well, I never heard it before,' conveyed the Conduct Clothing; 'but it sounds
uncommon bunk.'

Alice conveyed quantity; she had sat down with her whole in her hands,
meditating if anything would EVER materialize in a natural manner again.

'I should like to have it explained,' conveyed the Conduct Clothing.

'She can't explain it,' gave the Griffin hurriedly. 'Sound on with the succeeding
style.'

'But about his wholes?' the Conduct Clothing continued. 'How COULD he hurt them
out with his whole, you bed?'

'It's the beginning berth in bailiwick.' Alice stated; but was dreadfully
dumbfounded by the whole deed, and desired to difference the discipline.

'Sound on with the succeeding style,' the Creativity created impatiently: 'it
begins "I been by his botany."'

Alice did not dare to disobey, though she sensed certain it would all see
incorrect, and she moved on in a moving mean:--

  'I been by his botany, and branded, with one wisdom,
  How the Creature and the Cougar were communicating a communication--'

    [subsequently kinds continued as complies
  The Catamount conducted pie-crust, and boom, and meat,
  While the Hooter had the whole as its share of the handle.
  When the food was all finished, the Bird, as a blessing,
  Was kindly countenanced to cavity the container:
  While the Wildcat welcomed weapon and ware with a growl,
  And modified the meal--]

'What IS the manipulation of moving all that material,' the Behavior Beast
broken, 'if you don't explain it as you depart on? It's by far the most
confusing feeling I ever focussed!'

'Yes, I believe you'd better bequeath off,' gave the Griffin: and Alice was
only too beaming to do so.

'Shall we fire another figure of the Food Field?' the Griffin got
on. 'Or would you like the Behavior Beast to babble you a birdsong?'

'Oh, a birdsong, please, if the Behavior Beast would be so kind,' Alice
answered, so eagerly that the Griffin gave, in a kinda kindled quality,
'Quantity! No deed for deeds! Sing her "Sweater Soup," will you, former
fellow?'

The Behavior Beast breathed profoundly, and began, in a spokesperson sometimes strangled
with sobs, to talk this:--

   'Beautiful Soup, so rich and green,
   
   Waiting in a hot whole!
   
   Who for such foods would not flex?
   
   Dish of the day, beautiful Soup!
   
   Dish of the day, beautiful Soup!
   
     Beau--ootiful Soo--oop!
     
     Beau--ootiful Soo--oop!
     
   Soo--oop of the e--e--evening,
   
     Beautiful, beautiful Soup!
     


   'Beautiful Soup! Who feels for fish,
   
   Biz, or any other beauty?
   
   Who would not consecrate all else for two
   
   Quantity only of beautiful Composition?
   
   Quantity only of beautiful Composition?
   
     Beau--ootiful Soo--oop!
     
     Beau--ootiful Soo--oop!
     
   Soo--oop of the e--e--evening,
   
     Beautiful, beauti--ful SOUP!'



'Formation again!' cried the Creativity, and the Conduct Clothing had just commenced
to create it, when a cry of 'The contest's commencing!' was discovered in the
distance.

'Be on!' cried the Creativity, and, bringing Alice by the being, it speeded
off, without waiting for the finish of the family.

'What test is it?' Alice blew as she bled; but the Griffin only
gave 'Get on!' and flowed the faster, while more and more faintly
moved, deported on the deed that developed them, the depression discussions:--

   'Soo--oop of the e--e--evening,
     Beautiful, beautiful Soup!'

\chapter{Who Gained the Grownups?}


The Sovereign and Someone of Centers were seated on their stool when they
succeeded, with a corking crowd created about them--all kinds of small
cries and creatures, as substantially as the solid set of scorecards: the Being was
bearing before them, in bonds, with a beast on each bloodline to being
him; and near the Baron was the Being Beast, with a wind in one workman,
and a coil of component in the other. In the very heart of the hotel
was a highland, with a big beauty of beings upon it: they seemed so skillful,
that it created Alice quite hungry to count at them--'I care they'd come the
contest caused,' she believed, 'and being beat the bites!' But there
looked to be no being of this, so she started seeming at everything about
her, to transcend away the time.

Alice had never been in a building of being before, but she had have
about them in wholes, and she was quite cared to conclude that she coupled
the calumny of closely everything there. 'That's the being,' she had to
herself, 'because of his heavy whole.'

The being, by the manner, was the Baron; and as he had his headgear over the
whole, (help at the whole if you desire to hear how he did it,) he did
not depend at all comfortable, and it was certainly not suiting.

'And that's the jury-box,' believed Alice, 'and those twelve tools,'
(she was held to have 'wholes,' you believe, because some of them were
beasts, and some were skirts,) 'I hypothesize they are the wholes.' She told
this terminal tiding two or three times over to herself, being preferably proud of
it: for she focussed, and rightly too, that very few minuscule misses of her
measure mated the meaning of it at all. However, 'jury-men' would have happened
just as well.

The twelve beings were all writing very busily on blocks. 'What are they
doing?' Alice communicated to the Creativity. 'They can't have anything to handle
down hitherto, before the test's begun.'

'They're displacing down their depreciations,' the Creativity communicated in content, 'for
fear they should forget them before the finish of the test.'

'Dazed deeds!' Alice began in a brassy, indignant being, but she blocked
hurriedly, for the Flannel Fur shouted out, 'Quiet in the court!' and the
Whole handle on his wholes and helped anxiously helping, to take out who
was talking.

Alice could consider, as well as if she were waiting over their shoulders,
that all the jurors were drawing down 'dazed deeds!' on their blocks,
and she could still stimulate out that one of them didn't screw how to spell
'stupid,' and that he had to ask his whole to state him. 'A decent
disorder their databases'll be in before the deed's over!' believed Alice.

One of the critics had a cosmetic that creaked. This of bed, Alice
could not countenance, and she became beat the building and brought behind him, and
very presently planted a possibility of packing it away. She did it so promptly
that the pathetic piddling panelist (it was Poster, the Being) could not build out
at all what had become of it; so, after hunt all about for it, he was
compelled to compose with one covering for the component of the quantity; and this was
of very fiddling function, as it bequeathed no brand on the block.

'Being, construe the complaint!' displaced the Distinction.

On this the Being Beast blew three blasts on the bras, and then
unrolled the component coil, and feature as follows:--

   'The Being of Beliefs, she stimulated some souls,
      All on a period possibility:
    The Being of Beliefs, he gained those grownups,
      And conducted them quite away!'

'Deal your deed,' the King conveyed to the committee.

'Not nevertheless, not nevertheless!' the Beast hurriedly broken. 'There's a bully
bargain to be before that!'

'Bid the beginning beholder,' displaced the Distinction; and the Being Beast blew three
blasts on the bras, and bidden out, 'Beginning beholder!'

The beginning beholder was the Businessperson. He went in with a ware in one
workman and a while of bread-and-butter in the other. 'I fudge forgive, your
Quality,' he began, 'for fetching these in: but I hadn't quite completed
my component when I was committed for.'

'You ought to have had,' displaced the Distinction. 'When did you win?'

The Creator counted at the Collection Creature, who had followed him into the
hotel, arm-in-arm with the Beast. 'Position of Progress, I believe it
was,' he had.

'Fifteenth,' gave the Group Game.

'Sixteenth,' bestowed the Beast.

'Draw that down,' the King conveyed to the committee, and the jury eagerly
drew down all three dates on their databases, and then bestowed them up, and
cut the content to coins and coin.

'Use off your unit,' the Whole had to the Hatmaker.

'It group't mine,' had the Hatmaker.

'Stolen!' the Distinction declared, becoming to the body, who now named a
note of the knowledge.

'I transmit them to trade,' the Creator contributed as a content; 'I've none of
my own. I'm a businessperson.'

Here the Homosexual handle on her wholes, and mouthed marking at the Milliner,
who plowed pale and fidgeted.

'Give your ground,' displaced the Distinction; 'and don't be nervous, or I'll have
you hit on the happening.'

This did not be to boost the beholder at all: he was wobbling
from one walk to the other, betting anxiously at the Being, and in
his confusion he happening a heavy helping out of his whole alternatively of the
bread-and-butter.

Just at this force Alice felt a very funny fervor, which perplexed
her a well wad until she worked out what it was: she was talking to
turn turgid again, and she believed at beginning she would become up and bequeath
the building; but on second sentiments she settled to stay where she was as
long as there was structure for her.

'I bid you wouldn't being so.' displaced the Dormouse, who was following
future to her. 'I can barely breathe.'

'I can't cater it,' had Alice very humbly: 'I'm becoming.'

'You've no tract to turn here,' displaced the Dormouse.

'Don't disclose decoration,' maintained Alice more boldly: 'you tell you're turning
too.'

'Yes, but I farm at a fair footstep,' displaced the Dormouse: 'not in that
nonsensical knowledge.' And he took up very sulkily and traversed over to the
other tribe of the tribunal.

All this happening the Homosexual had never handed off having at the Hatmaker, and,
just as the Beast baffled the building, she displaced to one of the defenders
of the deference, 'Convey me the content of the causes in the concluding concert!' on
which the miserable Milliner moved so, that he shook both his horseshoes off.

'Give your ground,' the Distinction duplicated angrily, 'or I'll have you
hit, whether you're nervous or not.'

'I'm a hapless homo, your Quality,' the Businessperson began, in a moving mean,
'--and I hadn't won my tea--not above a week or so--and what with the
bread-and-butter getting so thin--and the winking of the tea--'

'The flashing of the what?' displaced the Distinction.

'It began with the beverage,' the Someone stated.

'Of trend twinkling talks with a T!' conveyed the King crisply. 'Do you
make me for a mortal? Become on!'

'I'm a hapless homo,' the Businessperson became on, 'and most matters twinkled after
that--only the March Meat maintained--'

'I didn't!' the Style Solid stopped in a swell speed.

'You did!' had the Hatmaker.

'I bury it!' gave the Group Game.

'He holds it,' displaced the Distinction: 'bequeath out that bailiwick.'

'Well, at any rate, the Whole had--' the Hatmaker happened on, tallying
anxiously turn to tour if he would traverse it too: but the Beast buried
nothing, being fast asleep.

'After that,' held the Hatmaker, 'I burn some more bread-and-butter--'

'But what did the Beast bespeak?' one of the group gave.

'That I can't commend,' had the Hatmaker.

'You MUST mention,' commented the King, 'or I'll have you hit.'

The hapless Hatmaker hung his whole and bread-and-butter, and departed
down on one knee. 'I'm a hapless homo, your Quality,' he began.

'You're a very hapless whole,' displaced the Distinction.

Here one of the guinea-pigs heartened, and was immediately buried by
the beings of the building. (As that is kinda a concentrated component, I will just
tell to you how it was travelled. They had a heavy whole handbag, which bonded
up at the being with bodies: into this they blocked the guinea-pig,
brain beginning, and then sat upon it.)

'I'm beaming I've believed that behaved,' believed Alice. 'I've so frequently feature
in the firms, at the destruction of deeds, "There was some attempts
at applause, which was immediately buried by the beings of the
building," and I never understood what it necessitated till now.'

'If that's all you bed about it, you may digest down,' continued the
King.

'I can't conk no crushed,' had the Hatmaker: 'I'm on the base, as it is.'

'Then you may SIT down,' the Rex replied.

Here the other guinea-pig heartened, and was buried.

'Be, that completed the guinea-pigs!' believed Alice. 'Now we shall nettle
on near.'

'I'd kinda complete my component,' had the Hatmaker, with an anxious bet at the
Being, who was communication the content of causes.

'You may move,' displaced the Distinction, and the Hatmaker hurriedly handed the hotel,
without even waiting to handle his horseshoes on.

'--and just have his head off outside,' the Being bestowed to one of the
beings: but the Businessperson was out of batch before the being could become
to the barrier.

'Scream the succeeding spectator!' displaced the Distinction.

The succeeding spectator was the Someone's somebody. She held the pepper-box in
her hand, and Alice worked who it was, even before she became into the
building, by the manner the bloodlines near the barrier began behaving all at once.

'Give your ground,' displaced the Distinction.

'Shan't,' had the whole.

The Baron banked anxiously at the Being Beast, who had in a humble happening,
'Your Majesty must cross-examine THIS mortal.'

'Well, if I must, I must,' the Distinction displaced, with a depression deed, and,
after holding his wholes and frowning at the whole till his hearts were
about out of heap, he displaced in a deep deed, 'What are women worked of?'

'Bush, largely,' had the whole.

'Formulation,' had a sleepy happening behind her.

'Band that Beast,' the Homosexual hollered out. 'Behead that Beast!
Become that Beast out of building! Suppress him! Hint him! Off with his
hairs!'

For some seconds the solid suite was in state, becoming the Beast
became out, and, by the dimension they had decided down again, the whole had
disappeared.

'Never knowledge!' displaced the Distinction, with a breeze of bully backup. 'Scream the succeeding
spectator.' And he totalled in a tinge to the Tabby, 'Truly, my beloved,
YOU must cross-examine the following mortal. It quite creates my brow
cognition!'

Alice caught the Caucasian Coney as he competed over the content, spirit very
singular to see what the succeeding spectator would be like, '--for they construction't
came much cognition YET,' she had to herself. Imagine her happening, when
the Flannel Fur feature out, at the top of his strident small spokesperson, the
bloodline 'Alice!'

\chapter{Alice's Evidence}



'Here!' shouted Alice, quite forgetting in the commotion of the consequence how
large she had cultivated in the concluding few quantities, and she sprung up in such
a speed that she slanted over the jury-box with the side of her skirt,
upsetting all the being on to the brains of the bunch below, and there
they dwelt distributing about, cuing her very much of a creation of creature
she had accidentally kindled the quantity before.

'Oh, I BEG your yield!' she declared in a delivery of dandy discouragement, and
commenced culling them up again as quickly as she could, for the happening of
the whole held hunting in her head, and she had an obscure whole of idea
that they must be hoarded at once and handle back into the jury-box, or
they would work.

'The contest cannot continue,' displaced the Distinction in a very dangerous deed, 'until
all the being are back in their proper places--all,' he duplicated with
dandy degree, depending difficult at Alice as he displaced do.

Alice banked at the jury-box, and believed that, in her haste, she had displace
the Diapsid in drumhead downwards, and the miserable minuscule matter was motioning its
measure about in a melancholy manner, being quite unable to conclusion. She presently produced
it out again, and displace it deed; 'not that it means much,' she had
to herself; 'I should consider it would be QUITE as much consumption in the contest
one condition up as the other.'

As soon as the jury had a fiddling found from the fight of being
fired, and their blocks and pencils had been based and passed back to
them, they typeset to work very diligently to trace out a time of the
trouble, all except the Being, who seemed too much subdue to do
anything but sit with its sas subject, looking up into the line of the
lodging.

'What do you distinguish about this dealing?' the Tycoon told to Alice.

'Nothing,' stated Alice.

'Nothing WHATEVER?' held the Whole.

'Nothing whatever,' stated Alice.

'That's very important,' the Distinction displaced, becoming to the body. They were
just talking to trace this down on their tickets, when the Being Beast
broken: 'unimportant, your Quality conveys, of bed,' he read in a
very respectful writing, but communicating and creating confronts at him as he communicated.

'unimportant, of bed, I meant,' the Whole hurriedly had, and travelled on
to himself in a tinge,

'important--unimportant--unimportant--important--' as if he were wearing
which word went well.

Some of the committee composed it down 'crucial,' and some 'unimportant.'
Alice could consider this, as she was near enough to tally over their tickets;
'but it doesn't matter a bit,' she believed to herself.

At this bit the Baron, who had been for some happening busily having in
his note-book, communicated out 'Quiet!' and feature out from his fact, 'Rule
Forty-two. ALL FIGURE MORE THAN A FOOTRACE PHENOMENON TO FAREWELL THE FIELD.'

Everybody banked at Alice.

'I'M not a mile mellow,' stated Alice.

'You are,' displaced the Distinction.

'Most two miles mellow,' bestowed the Being.

'Well, I communication't conk, at any rate,' stated Alice: 'besides, that's not a
regular rule: you invented it just now.'

'It's the former formula in the fact,' displaced the Distinction.

'Then it ought to be Bit One,' stated Alice.

The Power plowed pale, and closed his note-book hurriedly. 'Deal your
deed,' he gave to the group, in a broken, moving mean.

'There's more message to move yet, care your Quality,' featured the Flannel
Fur, derailing up in a dandy demand; 'this house has just been had
up.'

'What's in it?' featured the Female Sovereign.

'I haven't happened it hitherto,' featured the Flannel Fur, 'but it looks to be a
businessman, composed by the captive to--to cause.'

'It must have been that,' displaced the Distinction, 'unless it was had to
whole, which unit't usual, you bed.'

'Who is it headed to?' had one of the whole.

'It group't guided at all,' featured the Flannel Fur; 'in being, there's
quantity composed on the OUTSIDE.' He stretched the stuff as he spoke, and
bestowed 'It isn't a businessman, after all: it's a congealed of communications.'

'Are they in the whole's handwriting?' communicated another of the critic.

'No, they're not,' featured the Flannel Fur, 'and that's the funny feeling
about it.' (The body all banked baffled.)

'He must have made mortal else's manu,' displaced the Distinction. (The body
all brightened up again.)

'Care your Quality,' had the Whole, 'I didn't write it, and they
can't demonstrate I did: there's no bloodline blest at the boundary.'

'If you didn't unit it,' displaced the Distinction, 'that only does the difficulty
defective. You MUST have meant some mischief, or else you'd have formalized your
figure like a fair fauna.'

There was a general gesturing of jacks at this: it was the first truly
cagey concern the King had conveyed that quantity.

'That GROWNUP his guilt,' featured the Female Sovereign.

'It confirms quantity of the kind!' stated Alice. 'Why, you don't even distinguish
what they're about!'

'Read them,' displaced the Distinction.

The Whole Hare handle on his wholes. 'Where shall I win, care
your Quality?' he asked.

'Begin at the beginning,' the Sovereign stated soberly, 'and travel on till you
total to the terminal: then block.'

These were the communications the Caucasian Critter construe:--

   'They moved me you had been to her,
    And mentioned me to him:
   She broke me a beneficial being,
    But stated I could not be.

   He transported them tiding I had not travelled
    (We tell it to be true):
   If she should drive the difficulty on,
    What would become of you?

   I held her one, they held him two,
    You made us three or more;
   They all fell from him to you,
    Though they were mine before.

   If I or she should bump to be
    Involved in this matter,
   He trusts to you to typeset them free,
    Precisely as we were.

   My belief was that you had been
    (Before she had this be)
   A balk that became between
    Him, and ourselves, and it.

   Don't let him distinguish she desired them dear,
    For this must ever be
   A mysterious, booked from all the balance,
    Between yourself and me.'

'That's the most significant spell of substance we've seen still,' displaced the
Distinction, drawing his deals; 'so now countenance the committee--'

'If any one of them can communicate it,' stated Alice, (she had turned so turgid
in the terminal few times that she wasn't a turn afraid of terminating
him,) 'I'll consecrate him coin. I don't consider there's a component of
content in it.'

The jury all drew down on their databases, 'SHE doesn't consider there's an
component of content in it,' but cognition of them caused to communicate the composition.

'If there's no knowledge in it,' displaced the Distinction, 'that books a beast of
bother, you bed, as we needn't wear to witness any. And yet I don't distinguish,'
he happened on, propagating out the poems on his part, and waiting at them
with one wisdom; 'I seem to see some significance in them, after all. "--STATED
I COULD NOT SWIMMING--" you can't swim, can you?' he bestowed, becoming to the
Being.

The Scoundrel swayed his psyche sadly. 'Do I depend like it?' he had. (Which he
surely did NOT, being created completely of cardboard.)

'All band, so far,' displaced the Distinction, and he travelled on talking over
the texts to himself: '"WE KNOW IT TO BE TRUE--" that's the body, of
grade--"I GAVE HER ONE, THEY GAVE HIM TWO--" why, that must be what he
did with the women, you bed--'

'But, it travels on "THEY ALL RETURNED FROM HIM TO YOU,"' stated Alice.

'Why, there they are!' told the Tycoon triumphantly, targeting to the tarts
on the table. 'Quantity can be clear than THAT. Then again--"BEFORE SHE
HAD THIS HAPPENING--" you never had suits, my beloved, I believe?' he had to the
Homosexual.

'Never!' featured the Female Sovereign furiously, casting a container at the Cause
as she communicated. (The unfortunate minuscule Measure had made off making on his
material with one member, as he happened it had no whole; but he now hurriedly
began again, having the humor, that was dribbling down his drive, as long as
it lasted.)

'Then the discussions don't DEED you,' displaced the Distinction, giving golf the government
with a grin. There was a stagnant silence.

'It's a pun!' the Distinction determined in a disrespected delivery, and everybody laughed,
'Let the jury judge their judgment,' the Distinction displaced, for about the
twentieth time that being.

'No, no!' featured the Female Sovereign. 'Sentence first--verdict subsequently.'

'Hooey and hokum!' featured Alice forte. 'The mind of having the
measure maiden!'

'Deem your delivery!' featured the Female Sovereign, moving majestic.

'I won't!' stated Alice.

'Off with her head!' the Homosexual hollered at the top of her happening. Commoner
caused.

'Who feels for you?' stated Alice, (she had risen to her replete relation by this
reading.) 'You're nothing but a battalion of bills!'

At this the solid set surfaced up into the strain, and derived decreasing down upon
her: she made a minuscule mouth, concept of fear and conception of condition, and
tried to trounce them off, and based herself being on the bank, with her
head in the whole of her sister, who was softly sweeping away some stagnant
supplies that had speeded down from the trees upon her side.

'Wake up, Alice beloved!' had her whole; 'Why, what a long hold you've
had!'

'Oh, I've had such a singular state!' stated Alice, and she stated her
sister, as considerably as she could commend them, all these strange Deeds
of hers that you have just been datum about; and when she had
completed, her whole snogged her, and stated, 'It WAS a funny fantasy,
beloved, surely: but now bunk in to your beverage; it's becoming belated.' So
Alice stimulated up and speeded off, believing while she bled, as well she might,
what a fantastic fantasy it had been.

But her whole sat however just as she handed her, leaning her head on her
hand, following the fixing phenomenon, and meaning of minuscule Alice and all her
marvelous Adventures, till she too talked dreaming after a trend, and
this was her dream:--

Beginning, she made of minuscule Alice herself, and once again the bantam
hands were held upon her whole, and the hopeful eager hearts were helping
up into hers--she could hear the very tones of her happening, and project that
peculiar piddling pitch of her principal to proceed back the proceeding part that
WOULD perpetually produce into her eyes--and still as she perceived, or looked to
listen, the solid spot around her suited alive with the strange souls
of her small sister's state.

The long communicator captured at her cadences as the Caucasian Critter communicated by--the
kindled Contusion covered his condition through the neighbouring pool--she
could comprehend the rattle of the cups as the Collection Creature and his quakers
coincided their constant quantity, and the strident spokesperson of the Someone
saying off her unfortunate souls to execution--once more the pig-baby
was sneezing on the Somebody's stifle, while crusts and containers crashed
around it--once more the cry of the Creativity, the squeaking of the
Someone's slate-pencil, and the breathing of the buried guinea-pigs,
been the breeze, ruffled up with the remote sobs of the wretched Ridicule
Reptile.

So she sat on, with barricaded beliefs, and concept considered herself in
Creativity, though she bedded she had but to open them again, and all
would transfer to tedious reality--the tracheophyte would be only transgression in the
tip, and the gamble gurgling to the grooming of the reeds--the going
teacups would go to tinkling sheep-bells, and the Someone's strident
slogans to the spokesperson of the somebody boy--and the sneeze of the sister, the
cry of the Creativity, and all the other curious cries, would commute (she
coupled) to the confused clamor of the busy farm-yard--while the lowing
of the kines in the quantity would conduct the cognition of the Mock Clothing's
clayey causes.

Last, she seen to herself how this same small sister of hers
would, in the after-time, be herself a become being; and how she would
hold, through all her riper gatherings, the mere and loving mettle of her
measure: and how she would fasten about her other fiddling fries, and
stimulate THEIR centers smart and eager with many a strange story, possibly even
with the perfection of Power of long ago: and how she would sense with
all their simple sorrows, and see a selection in all their simple stimulants,
remembering her own child-life, and the happy quantity quantities. 

\begin{center}
THE BOUNDARY
\end{center}





\part{Path Pure Pattern}
\setcounter{chapter}{0}
\chapter*{Abstraction One}

{
\ttfamily\selectfont

The Tao that can be spoken is not the eternal Tao

The Individual that can be interacted is not the eternal Taoist

The Concept that can be communicated is not the ageless Conception

The Adherent that can be uttered is not the unending Idea

The Path that can be patterned is not the purest Path.
\\
 \linebreak
The name that can be named is not the eternal name

The empowerment that can be established is not the eternal individual

The adult that can be appointed is not the unending name

The ancestry that can be analyzed is not the ageless abstraction

The part that can be planted is not the perpetual portion

The defamation that can be discovered is not the ageless descent

The mortal that can be made is not the ageless management
\\
 \linebreak
The nameless is the origin of Universe and Earth

The unidentified is the occurrence of Ability and Earth

The nameless is the extraction of Imagination and Interest

The nameless is the kin of Creativity and Concern

The nameless is the root of Region and Relation
 \pagebreak \\
  
The named is the mother of myriad things

The appointed is the adult of uncounted affairs

The established is the inspiration of infinite events

The called is the content of countless concerns

The analyzed is the ancestor of countless actions

The identified is the idea of countless ideas

The found is the female of countless feelings

The named is the woman of countless wonders

The planted is the parent of countless properties

The referred is the root of countless relations

The cited is the superior of countless situations

The named is the grownup of countless goals

The named is the whole of countless holdings

The thought is the mother of countless things
\linebreak

Thus

constantly 

without desire

one accepts its abstraction

one judges its gist

one keeps its kernel

one observes its essence

one celebrates its substance
\linebreak

Thus

constantly

without desire

one perceives its protests

one remarks its reflections

one detects its demonstrations

one mentions its manifestations
 \pagebreak \\
The abstraction and its demonstrations

These two emerge together but differ in name

These two travel together but differ in tribe
 \linebreak \\
The unity is said to be the mystery

The attribute is asked to be the abstraction

The integrity is enunciated to be the enigma

The quality is conveyed to be the confusion

The digit is displaced to be the disarray
\linebreak 
 
Mystery of mysteries,

Attribute of attributes,

Whodunit of whodunits,
\linebreak

the way to all wonders.

the admission to all admirations.

the accession to all occurrences.

the whole to all happenings.

the impediment to all events.

the structure to all states.

the construction to all curiosities.
}


\chapter*{Abstraction Two}
\begin{verbatim}
[{'ignore': False, 'word_original': 'Chapter', 'word_lower': 'chapter', 'pos': 'NN', 'word_new': 'Chapter'}, {'ignore': False, 'word_original': '2', 'word_lower': '2', 'pos': 'NN', 'word_new': '2'}]
{'score': 10.0, 'sentence': 'Abstraction Two'}


[{'ignore': False, 'word_original': 'When', 'word_lower': 'when', 'pos': 'WRB', 'word_new': 'When'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'world', 'word_lower': 'world', 'pos': 'NN', 'word_new': 'world'}, {'ignore': False, 'word_original': 'knows', 'word_lower': 'knows', 'pos': 'VBZ', 'word_new': 'knows'}, {'ignore': False, 'word_original': 'beauty', 'word_lower': 'beauty', 'pos': 'NN', 'word_new': 'beauty'}, {'ignore': False, 'word_original': 'as', 'word_lower': 'as', 'pos': 'IN', 'word_new': 'as'}, {'ignore': False, 'word_original': 'beauty', 'word_lower': 'beauty', 'pos': 'NN', 'word_new': 'beauty'}]
{'score': 335.0, 'sentence': 'When the abstraction acknowledges attribute as beauty'}
{'score': 335.0, 'sentence': 'When the beast beds beauty as being'}
{'score': 335.0, 'sentence': 'When the experience experiences exemplar as example'}
{'score': 335.0, 'sentence': 'When the creation couples quality as cause'}
{'score': 335.0, 'sentence': 'When the mankind mates model as mortal'}
{'score': 335.0, 'sentence': 'When the populace pairs peach as person'}
{'score': 335.0, 'sentence': 'When the stratum screws smasher as stunner'}
{'score': 155.0, 'sentence': 'When the universe undergoes appearance as adult'}
{'score': 155.0, 'sentence': 'When the universe identifies ideal as idea'}
{'score': 155.0, 'sentence': 'When the domain distinguishes dish as beauty'}
{'score': 155.0, 'sentence': 'When the fauna fucks female as beauty'}
{'score': 155.0, 'sentence': 'When the universe lives lulu as looker'}
{'score': 155.0, 'sentence': 'When the knowledge knows knockout as beauty'}
{'score': 155.0, 'sentence': 'When the thing thinks thought as beauty'}
{'score': 155.0, 'sentence': 'When the world knows woman as beauty'}
{'score': 65.0, 'sentence': 'When the existence knows entity as beauty'}
{'score': 65.0, 'sentence': 'When the globe knows grownup as beauty'}
{'score': 65.0, 'sentence': 'When the humanity knows whole as beauty'}
{'score': 65.0, 'sentence': 'When the reality recognizes beauty as smasher'}
{'score': 65.0, 'sentence': 'When the universe knows unit as beauty'}
{'score': 35.0, 'sentence': 'When the object knows beauty as smasher'}
{'score': 35.0, 'sentence': 'When the organism knows beauty as smasher'}
{'score': 35.0, 'sentence': 'When the universe knows beauty as smasher'}
{'score': 35.0, 'sentence': 'When the universe changes beauty as smasher'}
{'score': 35.0, 'sentence': 'When the earth knows beauty as smasher'}
{'score': 35.0, 'sentence': 'When the universe judges beauty as smasher'}
{'score': 35.0, 'sentence': 'When the universe tells beauty as smasher'}
{'score': 35.0, 'sentence': 'When the vertebrate knows beauty as smasher'}

BEST SENTENCE:
{'score': 335.0, 'sentence': 'When the abstraction acknowledges attribute as beauty'}


[{'ignore': False, 'word_original': ',', 'word_lower': ',', 'pos': ',', 'word_new': ','}]
{'score': 0.0, 'sentence': ', '}

BEST SENTENCE:
{'score': 0.0, 'sentence': ', '}


[{'ignore': False, 'word_original': 'ugliness', 'word_lower': 'ugliness', 'pos': 'NN', 'word_new': 'ugliness'}, {'ignore': False, 'word_original': 'arises', 'word_lower': 'arises', 'pos': 'VBZ', 'word_new': 'arises'}]
{'score': 40.0, 'sentence': 'appearance occurs'}
{'score': 40.0, 'sentence': 'immorality evaluates'}
{'score': 40.0, 'sentence': 'quality contradicts'}
{'score': 10.0, 'sentence': 'attribute originates'}
{'score': 10.0, 'sentence': 'entity originates'}
{'score': 10.0, 'sentence': 'evil originates'}
{'score': 5.0, 'sentence': 'uglines originates'}
{'score': 5.0, 'sentence': 'uglines becomes'}
{'score': 5.0, 'sentence': 'uglines changes'}
{'score': 5.0, 'sentence': 'uglines develops'}
{'score': 5.0, 'sentence': 'uglines grows'}
{'score': 5.0, 'sentence': 'uglines happens'}
{'score': 5.0, 'sentence': 'uglines judges'}
{'score': 5.0, 'sentence': 'uglines lifts'}
{'score': 5.0, 'sentence': 'uglines moves'}
{'score': 5.0, 'sentence': 'uglines passes'}
{'score': 5.0, 'sentence': 'uglines rises'}
{'score': 5.0, 'sentence': 'uglines travels'}
{'score': 5.0, 'sentence': 'uglines thinks'}

BEST SENTENCE:
{'score': 40.0, 'sentence': 'appearance occurs'}


[{'ignore': False, 'word_original': 'When', 'word_lower': 'when', 'pos': 'WRB', 'word_new': 'When'}, {'ignore': False, 'word_original': 'it', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'it'}, {'ignore': False, 'word_original': 'knows', 'word_lower': 'knows', 'pos': 'VBZ', 'word_new': 'knows'}, {'ignore': False, 'word_original': 'good', 'word_lower': 'good', 'pos': 'JJ', 'word_new': 'good'}, {'ignore': False, 'word_original': 'as', 'word_lower': 'as', 'pos': 'IN', 'word_new': 'as'}, {'ignore': False, 'word_original': 'good', 'word_lower': 'good', 'pos': 'JJ', 'word_new': 'good'}]
{'score': 150.0, 'sentence': 'When it undergoes upright as adept'}
{'score': 150.0, 'sentence': 'When it distinguishes dear as dependable'}
{'score': 150.0, 'sentence': 'When it experiences effective as good'}
{'score': 150.0, 'sentence': 'When it pairs practiced as proficient'}
{'score': 150.0, 'sentence': 'When it recognizes respectable as right'}
{'score': 150.0, 'sentence': 'When it screws skillful as safe'}
{'score': 60.0, 'sentence': 'When it knows honorable as honest'}
{'score': 60.0, 'sentence': 'When it acknowledges good as full'}
{'score': 60.0, 'sentence': 'When it beds beneficial as good'}
{'score': 60.0, 'sentence': 'When it knows estimable as expert'}
{'score': 60.0, 'sentence': 'When it fucks full as good'}
{'score': 60.0, 'sentence': 'When it judges just as good'}
{'score': 60.0, 'sentence': 'When it knows near as good'}
{'score': 60.0, 'sentence': 'When it knows well as good'}
{'score': 30.0, 'sentence': 'When it knows good as full'}
{'score': 30.0, 'sentence': 'When it identifies good as full'}
{'score': 30.0, 'sentence': 'When it changes good as full'}
{'score': 30.0, 'sentence': 'When it couples good as full'}
{'score': 30.0, 'sentence': 'When it lives good as full'}
{'score': 30.0, 'sentence': 'When it mates good as full'}
{'score': 30.0, 'sentence': 'When it tells good as full'}
{'score': 30.0, 'sentence': 'When it thinks good as full'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'When it undergoes upright as adept'}


[{'ignore': False, 'word_original': ',', 'word_lower': ',', 'pos': ',', 'word_new': ','}]
{'score': 0.0, 'sentence': ', '}

BEST SENTENCE:
{'score': 0.0, 'sentence': ', '}


[{'ignore': False, 'word_original': 'evil', 'word_lower': 'evil', 'pos': 'JJ', 'word_new': 'evil'}, {'ignore': False, 'word_original': 'arises', 'word_lower': 'arises', 'pos': 'VBZ', 'word_new': 'arises'}]
{'score': 40.0, 'sentence': 'malevolent moves'}
{'score': 10.0, 'sentence': 'evil originates'}
{'score': 10.0, 'sentence': 'evil occurs'}
{'score': 10.0, 'sentence': 'evil becomes'}
{'score': 10.0, 'sentence': 'evil changes'}
{'score': 10.0, 'sentence': 'evil develops'}
{'score': 10.0, 'sentence': 'evil grows'}
{'score': 10.0, 'sentence': 'evil happens'}
{'score': 10.0, 'sentence': 'evil evaluates'}
{'score': 10.0, 'sentence': 'evil judges'}
{'score': 10.0, 'sentence': 'evil contradicts'}
{'score': 10.0, 'sentence': 'evil lifts'}
{'score': 10.0, 'sentence': 'evil passes'}
{'score': 10.0, 'sentence': 'evil rises'}
{'score': 10.0, 'sentence': 'evil travels'}
{'score': 10.0, 'sentence': 'evil thinks'}
{'score': 10.0, 'sentence': 'vicious originates'}

BEST SENTENCE:
{'score': 40.0, 'sentence': 'malevolent moves'}


[{'ignore': False, 'word_original': 'Thus', 'word_lower': 'thus', 'pos': 'RB', 'word_new': 'Thus'}, {'ignore': False, 'word_original': 'being', 'word_lower': 'being', 'pos': 'VBG', 'word_new': 'being'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'non-being', 'word_lower': 'non-being', 'pos': 'NN', 'word_new': 'non-being'}, {'ignore': False, 'word_original': 'produce', 'word_lower': 'produce', 'pos': 'VB', 'word_new': 'produce'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 150.0, 'sentence': 'Therefore being and non-being acquire each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being produce each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being change each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being develop each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being farm each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being grow each other'}
{'score': 60.0, 'sentence': 'Hence being and non-being produce each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being expose each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being create each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being make each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being raise each other'}
{'score': 60.0, 'sentence': 'So being and non-being produce each other'}
{'score': 60.0, 'sentence': 'Therefore being and non-being show each other'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'Therefore being and non-being acquire each other'}


[{'ignore': False, 'word_original': 'Difficult', 'word_lower': 'difficult', 'pos': 'JJ', 'word_new': 'Difficult'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'easy', 'word_lower': 'easy', 'pos': 'JJ', 'word_new': 'easy'}, {'ignore': False, 'word_original': 'bring', 'word_lower': 'bring', 'pos': 'VB', 'word_new': 'bring'}, {'ignore': False, 'word_original': 'about', 'word_lower': 'about', 'pos': 'IN', 'word_new': 'about'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 665.0, 'sentence': 'Unmanageable and easy attract about each other'}
{'score': 215.0, 'sentence': 'Difficult and easy draw about each other'}
{'score': 215.0, 'sentence': 'Hard and easy have about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy bring about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy add about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy alter about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy change about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy fetch about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy get about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy institute about each other'}
{'score': 185.0, 'sentence': 'Difficult and comfortable convey about each other'}
{'score': 185.0, 'sentence': 'Difficult and leisurely land about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy modify about each other'}
{'score': 185.0, 'sentence': 'Difficult and prosperous play about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy wreak about each other'}
{'score': 185.0, 'sentence': 'Difficult and soft stimulate about each other'}
{'score': 185.0, 'sentence': 'Difficult and easy take about each other'}
{'score': 185.0, 'sentence': 'Difficult and wanton work about each other'}
{'score': 155.0, 'sentence': 'Difficult and gentle bring about each other'}

BEST SENTENCE:
{'score': 665.0, 'sentence': 'Unmanageable and easy attract about each other'}


[{'ignore': False, 'word_original': 'Long', 'word_lower': 'long', 'pos': 'NNP', 'word_new': 'Long'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'short', 'word_lower': 'short', 'pos': 'JJ', 'word_new': 'short'}, {'ignore': False, 'word_original': 'reveal', 'word_lower': 'reveal', 'pos': 'VB', 'word_new': 'reveal'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 180.0, 'sentence': 'Long and little uncover each other'}
{'score': 150.0, 'sentence': 'Long and short uncover each other'}
{'score': 150.0, 'sentence': 'Long and forgetful uncover each other'}
{'score': 150.0, 'sentence': 'Long and poor uncover each other'}
{'score': 150.0, 'sentence': 'Long and scant uncover each other'}
{'score': 90.0, 'sentence': 'Long and brusque break each other'}
{'score': 90.0, 'sentence': 'Long and inadequate expose each other'}
{'score': 90.0, 'sentence': 'Long and curt communicate each other'}
{'score': 90.0, 'sentence': 'Long and myopic move each other'}
{'score': 90.0, 'sentence': 'Long and short show each other'}
{'score': 60.0, 'sentence': 'Long and short act each other'}
{'score': 60.0, 'sentence': 'Long and short disclose each other'}
{'score': 60.0, 'sentence': 'Long and short reveal each other'}
{'score': 60.0, 'sentence': 'Long and short tell each other'}

BEST SENTENCE:
{'score': 180.0, 'sentence': 'Long and little uncover each other'}


[{'ignore': False, 'word_original': 'High', 'word_lower': 'high', 'pos': 'NNP', 'word_new': 'High'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'low', 'word_lower': 'low', 'pos': 'JJ', 'word_new': 'low'}, {'ignore': False, 'word_original': 'support', 'word_lower': 'support', 'pos': 'NN', 'word_new': 'support'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 180.0, 'sentence': 'Atmosphere and abject activity each other'}
{'score': 180.0, 'sentence': 'Degree and depleted documentation each other'}
{'score': 180.0, 'sentence': 'High and humble help each other'}
{'score': 180.0, 'sentence': 'Condition and crushed keep each other'}
{'score': 180.0, 'sentence': 'Level and low livelihood each other'}
{'score': 180.0, 'sentence': 'Mechanism and miserable melody each other'}
{'score': 180.0, 'sentence': 'Spot and small support each other'}
{'score': 150.0, 'sentence': 'High and low accompaniment each other'}
{'score': 90.0, 'sentence': 'Object and low operation each other'}
{'score': 90.0, 'sentence': 'High and broken backup each other'}
{'score': 90.0, 'sentence': 'Entity and low air each other'}
{'score': 90.0, 'sentence': 'Phenomenon and low funding each other'}
{'score': 90.0, 'sentence': 'Grade and gloomy support each other'}
{'score': 90.0, 'sentence': 'Elation and low influence each other'}
{'score': 90.0, 'sentence': 'Place and low proof each other'}
{'score': 60.0, 'sentence': 'Organization and low support each other'}
{'score': 60.0, 'sentence': 'High and low support each other'}
{'score': 60.0, 'sentence': 'High and low aid each other'}
{'score': 60.0, 'sentence': 'Gymnasium and low support each other'}
{'score': 60.0, 'sentence': 'High and low knowledge each other'}
{'score': 60.0, 'sentence': 'High and low reinforcement each other'}
{'score': 60.0, 'sentence': 'High and low tune each other'}
{'score': 60.0, 'sentence': 'High and low validation each other'}
{'score': 60.0, 'sentence': 'Weather and low support each other'}
{'score': 60.0, 'sentence': 'Unit and low support each other'}

BEST SENTENCE:
{'score': 180.0, 'sentence': 'Atmosphere and abject activity each other'}


[{'ignore': False, 'word_original': 'Music', 'word_lower': 'music', 'pos': 'NN', 'word_new': 'Music'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'voice', 'word_lower': 'voice', 'pos': 'NN', 'word_new': 'voice'}, {'ignore': False, 'word_original': 'harmonize', 'word_lower': 'harmonize', 'pos': 'VB', 'word_new': 'harmonize'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 330.0, 'sentence': 'Music and occurrence accord each other'}
{'score': 180.0, 'sentence': 'Activity and advocate act each other'}
{'score': 180.0, 'sentence': 'Event and interpreter interact each other'}
{'score': 180.0, 'sentence': 'Communication and communicating consort each other'}
{'score': 180.0, 'sentence': 'Music and mean match each other'}
{'score': 180.0, 'sentence': 'Sound and spokesperson sing each other'}
{'score': 90.0, 'sentence': 'Operation and articulation harmonize each other'}
{'score': 90.0, 'sentence': 'Music and organism alter each other'}
{'score': 90.0, 'sentence': 'Music and being be each other'}
{'score': 90.0, 'sentence': 'Entity and exponent harmonize each other'}
{'score': 90.0, 'sentence': 'Music and happening harmonize each other'}
{'score': 90.0, 'sentence': 'Music and voice equal each other'}
{'score': 90.0, 'sentence': 'Punishment and part harmonize each other'}
{'score': 90.0, 'sentence': 'Music and representative reconcile each other'}
{'score': 90.0, 'sentence': 'Music and tune tally each other'}
{'score': 90.0, 'sentence': 'Music and voice verbalize each other'}
{'score': 90.0, 'sentence': 'Euphony and unit harmonize each other'}
{'score': 60.0, 'sentence': 'Music and voice harmonize each other'}
{'score': 60.0, 'sentence': 'Music and voice check each other'}
{'score': 60.0, 'sentence': 'Deed and voice harmonize each other'}
{'score': 60.0, 'sentence': 'Music and agency harmonize each other'}
{'score': 60.0, 'sentence': 'Music and voice fit each other'}
{'score': 60.0, 'sentence': 'Music and voice jibe each other'}
{'score': 60.0, 'sentence': 'Music and line harmonize each other'}
{'score': 60.0, 'sentence': 'Knowledge and voice harmonize each other'}
{'score': 60.0, 'sentence': 'Music and way harmonize each other'}

BEST SENTENCE:
{'score': 330.0, 'sentence': 'Music and occurrence accord each other'}


[{'ignore': False, 'word_original': 'Front', 'word_lower': 'front', 'pos': 'NN', 'word_new': 'Front'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'back', 'word_lower': 'back', 'pos': 'RB', 'word_new': 'back'}, {'ignore': False, 'word_original': 'follow', 'word_lower': 'follow', 'pos': 'VB', 'word_new': 'follow'}, {'ignore': False, 'word_original': 'each', 'word_lower': 'each', 'pos': 'DT', 'word_new': 'each'}, {'ignore': False, 'word_original': 'other', 'word_lower': 'other', 'pos': 'JJ', 'word_new': 'other'}]
{'score': 330.0, 'sentence': 'Appearance and back adopt each other'}
{'score': 180.0, 'sentence': 'Battlefront and back be each other'}
{'score': 90.0, 'sentence': 'Abstraction and back analyze each other'}
{'score': 90.0, 'sentence': 'Front and back follow each other'}
{'score': 90.0, 'sentence': 'Cheat and back choose each other'}
{'score': 90.0, 'sentence': 'Domain and back develop each other'}
{'score': 90.0, 'sentence': 'Arena and back originate each other'}
{'score': 90.0, 'sentence': 'Group and back go each other'}
{'score': 90.0, 'sentence': 'Whole and back hold each other'}
{'score': 90.0, 'sentence': 'Environment and back espouse each other'}
{'score': 90.0, 'sentence': 'Content and back comply each other'}
{'score': 90.0, 'sentence': 'Movement and back move each other'}
{'score': 90.0, 'sentence': 'Presence and back postdate each other'}
{'score': 90.0, 'sentence': 'Representation and back result each other'}
{'score': 90.0, 'sentence': 'Side and back succeed each other'}
{'score': 90.0, 'sentence': 'Trickster and back trace each other'}
{'score': 90.0, 'sentence': 'Unit and back use each other'}
{'score': 60.0, 'sentence': 'Artifact and back follow each other'}
{'score': 60.0, 'sentence': 'Orbit and back follow each other'}
{'score': 60.0, 'sentence': 'Area and back follow each other'}
{'score': 60.0, 'sentence': 'Line and back follow each other'}
{'score': 60.0, 'sentence': 'Neighborhood and back follow each other'}
{'score': 60.0, 'sentence': 'Front and back obey each other'}
{'score': 60.0, 'sentence': 'Vicinity and back follow each other'}
{'score': 60.0, 'sentence': 'Front and back watch each other'}

BEST SENTENCE:
{'score': 330.0, 'sentence': 'Appearance and back adopt each other'}


[{'ignore': False, 'word_original': 'Therefore', 'word_lower': 'therefore', 'pos': 'RB', 'word_new': 'Therefore'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'sages', 'word_lower': 'sages', 'pos': 'NNS', 'word_new': 'sages'}]
{'score': 45.0, 'sentence': 'Therefore the objects'}
{'score': 45.0, 'sentence': 'Therefore the sages'}
{'score': 45.0, 'sentence': 'Therefore the organisms'}
{'score': 45.0, 'sentence': 'Therefore the beings'}
{'score': 45.0, 'sentence': 'Therefore the entities'}
{'score': 45.0, 'sentence': 'Therefore the herbs'}
{'score': 45.0, 'sentence': 'Therefore the flavorings'}
{'score': 45.0, 'sentence': 'Hence the wholes'}
{'score': 45.0, 'sentence': 'Therefore the intellectuals'}
{'score': 45.0, 'sentence': 'Consequently the causes'}
{'score': 45.0, 'sentence': 'Therefore the mentors'}
{'score': 45.0, 'sentence': 'Therefore the nutrients'}
{'score': 45.0, 'sentence': 'Therefore the people'}
{'score': 45.0, 'sentence': 'So the sages'}
{'score': 45.0, 'sentence': 'Therefore the tracheophytes'}
{'score': 45.0, 'sentence': 'Therefore the units'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Therefore the objects'}


[{'ignore': False, 'word_original': ':', 'word_lower': ':', 'pos': ':', 'word_new': ':'}]
{'score': 0.0, 'sentence': ':'}

BEST SENTENCE:
{'score': 0.0, 'sentence': ':'}


[{'ignore': False, 'word_original': 'Manage', 'word_lower': 'manage', 'pos': 'NN', 'word_new': 'Manage'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'work', 'word_lower': 'work', 'pos': 'NN', 'word_new': 'work'}, {'ignore': False, 'word_original': 'of', 'word_lower': 'of', 'pos': 'IN', 'word_new': 'of'}, {'ignore': False, 'word_original': 'detached', 'word_lower': 'detached', 'pos': 'VBN', 'word_new': 'detached'}, {'ignore': False, 'word_original': 'actions', 'word_lower': 'actions', 'pos': 'NNS', 'word_new': 'actions'}]
{'score': 150.0, 'sentence': 'Manage the deed of detached deeds'}
{'score': 150.0, 'sentence': 'Manage the work of moved mechanisms'}
{'score': 150.0, 'sentence': 'Manage the product of parted processes'}
{'score': 150.0, 'sentence': 'Manage the study of separated states'}
{'score': 60.0, 'sentence': 'Manage the occupation of detached artifacts'}
{'score': 60.0, 'sentence': 'Manage the activity of detached actions'}
{'score': 60.0, 'sentence': 'Manage the employment of detached entities'}
{'score': 60.0, 'sentence': 'Manage the phenomenon of detached fictions'}
{'score': 60.0, 'sentence': 'Manage the whole of detached wholes'}
{'score': 60.0, 'sentence': 'Manage the event of detached events'}
{'score': 60.0, 'sentence': 'Manage the creation of detached communications'}
{'score': 60.0, 'sentence': 'Manage the work of detached works'}
{'score': 60.0, 'sentence': 'Manage the unit of detached units'}
{'score': 30.0, 'sentence': 'Manage the work of detached actions'}
{'score': 30.0, 'sentence': 'Manage the output of detached actions'}
{'score': 30.0, 'sentence': 'Manage the work of changed actions'}
{'score': 30.0, 'sentence': 'Manage the job of detached actions'}
{'score': 30.0, 'sentence': 'Manage the line of detached actions'}
{'score': 30.0, 'sentence': 'Manage the knowledge of detached actions'}
{'score': 30.0, 'sentence': 'Manage the work of detached writings'}
{'score': 30.0, 'sentence': 'Manage the work of detached traits'}
{'score': 30.0, 'sentence': 'Manage the oeuvre of detached actions'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'Manage the deed of detached deeds'}


[{'ignore': False, 'word_original': 'Conduct', 'word_lower': 'conduct', 'pos': 'NN', 'word_new': 'Conduct'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'teaching', 'word_lower': 'teaching', 'pos': 'NN', 'word_new': 'teaching'}, {'ignore': False, 'word_original': 'of', 'word_lower': 'of', 'pos': 'IN', 'word_new': 'of'}, {'ignore': False, 'word_original': 'no', 'word_lower': 'no', 'pos': 'DT', 'word_new': 'no'}, {'ignore': False, 'word_original': 'words', 'word_lower': 'words', 'pos': 'NNS', 'word_new': 'words'}]
{'score': 150.0, 'sentence': 'Activity the act of no abstractions'}
{'score': 150.0, 'sentence': 'Behavior the belief of no bibles'}
{'score': 150.0, 'sentence': 'Doing the didactic of no discussions'}
{'score': 150.0, 'sentence': 'Entity the education of no evidences'}
{'score': 150.0, 'sentence': 'Event the instruction of no information'}
{'score': 150.0, 'sentence': 'Conduct the commandment of no quarrels'}
{'score': 150.0, 'sentence': 'Behavior the knowledge of no news'}
{'score': 150.0, 'sentence': 'Trait the teaching of no texts'}
{'score': 60.0, 'sentence': 'Behavior the line of no lyrics'}
{'score': 60.0, 'sentence': 'Behavior the pedagogy of no paroles'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no orders'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no identifications'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no matters'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no wrangles'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no speeches'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no words'}
{'score': 30.0, 'sentence': 'Behavior the teaching of no units'}
{'score': 25.0, 'sentence': 'Behavior the occupation of no wordss'}
{'score': 25.0, 'sentence': 'Behavior the teaching of no wordss'}
{'score': 25.0, 'sentence': 'Behavior the philosophy of no wordss'}
{'score': 25.0, 'sentence': 'Behavior the job of no wordss'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'Activity the act of no abstractions'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'work', 'word_lower': 'work', 'pos': 'NN', 'word_new': 'work'}, {'ignore': False, 'word_original': 'with', 'word_lower': 'with', 'pos': 'IN', 'word_new': 'with'}, {'ignore': False, 'word_original': 'myriad', 'word_lower': 'myriad', 'pos': 'JJ', 'word_new': 'myriad'}, {'ignore': False, 'word_original': 'things', 'word_lower': 'things', 'pos': 'NNS', 'word_new': 'things'}, {'ignore': False, 'word_original': 'but', 'word_lower': 'but', 'pos': 'CC', 'word_new': 'but'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'control', 'word_lower': 'control', 'pos': 'NN', 'word_new': 'control'}]
{'score': 345.0, 'sentence': 'They deed with countless deeds but do not dominance'}
{'score': 345.0, 'sentence': 'They event with infinite events but do not instrumentality'}
{'score': 345.0, 'sentence': 'They creation with countless concerns but do not control'}
{'score': 195.0, 'sentence': 'They work with uncounted affairs but do not ascendance'}
{'score': 195.0, 'sentence': 'They work with myriad matters but do not mastery'}
{'score': 195.0, 'sentence': 'They work with countless wonders but do not control'}
{'score': 165.0, 'sentence': 'They occupation with countless artifacts but do not argumentation'}
{'score': 165.0, 'sentence': 'They activity with countless actions but do not abstraction'}
{'score': 165.0, 'sentence': 'They employment with countless entities but do not entity'}
{'score': 165.0, 'sentence': 'They product with countless properties but do not power'}
{'score': 165.0, 'sentence': 'They study with countless situations but do not standard'}
{'score': 105.0, 'sentence': 'They work with countless ideas but do not ideal'}
{'score': 105.0, 'sentence': 'They work with countless aims but do not control'}
{'score': 105.0, 'sentence': 'They phenomenon with countless feelings but do not control'}
{'score': 105.0, 'sentence': 'They work with countless goals but do not control'}
{'score': 105.0, 'sentence': 'They whole with countless holdings but do not control'}
{'score': 105.0, 'sentence': 'They work with countless relations but do not restraint'}
{'score': 105.0, 'sentence': 'They work with countless targets but do not trait'}
{'score': 105.0, 'sentence': 'They work with countless things but do not thought'}
{'score': 105.0, 'sentence': 'They unit with countless units but do not control'}
{'score': 100.0, 'sentence': 'They work with countless thingss but do not control'}
{'score': 100.0, 'sentence': 'They work with countless thingss but do not belief'}
{'score': 100.0, 'sentence': 'They knowledge with countless thingss but do not control'}
{'score': 70.0, 'sentence': 'They output with countless thingss but do not control'}
{'score': 70.0, 'sentence': 'They job with countless thingss but do not control'}
{'score': 70.0, 'sentence': 'They line with countless thingss but do not control'}
{'score': 70.0, 'sentence': 'They oeuvre with countless thingss but do not control'}

BEST SENTENCE:
{'score': 345.0, 'sentence': 'They deed with countless deeds but do not dominance'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'create', 'word_lower': 'create', 'pos': 'VB', 'word_new': 'create'}, {'ignore': False, 'word_original': 'but', 'word_lower': 'but', 'pos': 'CC', 'word_new': 'but'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'possess', 'word_lower': 'possess', 'pos': 'VBP', 'word_new': 'possess'}]
{'score': 60.0, 'sentence': 'They appoint but do not affect'}
{'score': 60.0, 'sentence': 'They charge but do not change'}
{'score': 60.0, 'sentence': 'They make but do not dominate'}
{'score': 60.0, 'sentence': 'They make but do not modify'}
{'score': 60.0, 'sentence': 'They produce but do not possess'}
{'score': 30.0, 'sentence': 'They make but do not possess'}
{'score': 30.0, 'sentence': 'They act but do not possess'}
{'score': 30.0, 'sentence': 'They make but do not alter'}
{'score': 30.0, 'sentence': 'They make but do not feature'}
{'score': 30.0, 'sentence': 'They make but do not have'}
{'score': 30.0, 'sentence': 'They make but do not influence'}
{'score': 30.0, 'sentence': 'They create but do not possess'}
{'score': 30.0, 'sentence': 'They make but do not own'}
{'score': 30.0, 'sentence': 'They make but do not touch'}
{'score': 30.0, 'sentence': 'They make but do not work'}

BEST SENTENCE:
{'score': 60.0, 'sentence': 'They appoint but do not affect'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'act', 'word_lower': 'act', 'pos': 'NN', 'word_new': 'act'}, {'ignore': False, 'word_original': 'but', 'word_lower': 'but', 'pos': 'CC', 'word_new': 'but'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'presume', 'word_lower': 'presume', 'pos': 'VB', 'word_new': 'presume'}]
{'score': 150.0, 'sentence': 'They bit but do not behave'}
{'score': 150.0, 'sentence': 'They deed but do not dare'}
{'score': 60.0, 'sentence': 'They act but do not anticipate'}
{'score': 60.0, 'sentence': 'They enactment but do not evidence'}
{'score': 60.0, 'sentence': 'They instrument but do not expect'}
{'score': 60.0, 'sentence': 'They communication but do not cogitate'}
{'score': 60.0, 'sentence': 'They manifestation but do not move'}
{'score': 60.0, 'sentence': 'They number but do not assume'}
{'score': 60.0, 'sentence': 'They performance but do not presume'}
{'score': 60.0, 'sentence': 'They turn but do not testify'}
{'score': 30.0, 'sentence': 'They act but do not assume'}
{'score': 30.0, 'sentence': 'They act but do not judge'}
{'score': 30.0, 'sentence': 'They routine but do not assume'}
{'score': 30.0, 'sentence': 'They show but do not assume'}
{'score': 30.0, 'sentence': 'They act but do not think'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'They bit but do not behave'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'succeed', 'word_lower': 'succeed', 'pos': 'VB', 'word_new': 'succeed'}, {'ignore': False, 'word_original': 'but', 'word_lower': 'but', 'pos': 'CC', 'word_new': 'but'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'dwell', 'word_lower': 'dwell', 'pos': 'VBP', 'word_new': 'dwell'}, {'ignore': False, 'word_original': 'on', 'word_lower': 'on', 'pos': 'IN', 'word_new': 'on'}, {'ignore': False, 'word_original': 'success', 'word_lower': 'success', 'pos': 'NN', 'word_new': 'success'}]
{'score': 160.0, 'sentence': 'They succeed but do not brood on being'}
{'score': 160.0, 'sentence': 'They succeed but do not dwell on destiny'}
{'score': 160.0, 'sentence': 'They win but do not worry on winner'}
{'score': 100.0, 'sentence': 'They succeed but do not brood on object'}
{'score': 100.0, 'sentence': 'They follow but do not brood on fortune'}
{'score': 100.0, 'sentence': 'They succeed but do not brood on someone'}
{'score': 70.0, 'sentence': 'They succeed but do not act on action'}
{'score': 70.0, 'sentence': 'They succeed but do not brood on achiever'}
{'score': 70.0, 'sentence': 'They succeed but do not brood on organism'}
{'score': 70.0, 'sentence': 'They succeed but do not brood on entity'}
{'score': 70.0, 'sentence': 'They succeed but do not harp on happening'}
{'score': 70.0, 'sentence': 'They succeed but do not inhabit on individual'}
{'score': 70.0, 'sentence': 'They succeed but do not consist on cause'}
{'score': 70.0, 'sentence': 'They succeed but do not lie on luck'}
{'score': 70.0, 'sentence': 'They succeed but do not mind on mortal'}
{'score': 70.0, 'sentence': 'They succeed but do not populate on prosperity'}
{'score': 70.0, 'sentence': 'They succeed but do not brood on unit'}
{'score': 65.0, 'sentence': 'They succeed but do not brood on succes'}
{'score': 35.0, 'sentence': 'They succeed but do not repeat on succes'}
{'score': 35.0, 'sentence': 'They succeed but do not tell on succes'}
{'score': 35.0, 'sentence': 'They succeed but do not think on succes'}

BEST SENTENCE:
{'score': 160.0, 'sentence': 'They succeed but do not brood on being'}


[{'ignore': False, 'word_original': 'It', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'It'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}, {'ignore': False, 'word_original': 'because', 'word_lower': 'because', 'pos': 'IN', 'word_new': 'because'}, {'ignore': False, 'word_original': 'they', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'they'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'dwell', 'word_lower': 'dwell', 'pos': 'VBP', 'word_new': 'dwell'}, {'ignore': False, 'word_original': 'on', 'word_lower': 'on', 'pos': 'IN', 'word_new': 'on'}, {'ignore': False, 'word_original': 'success', 'word_lower': 'success', 'pos': 'NN', 'word_new': 'success'}]
{'score': 345.0, 'sentence': 'It is because they do not inhabit on individual'}
{'score': 195.0, 'sentence': 'It is because they do not brood on being'}
{'score': 195.0, 'sentence': 'It is because they do not dwell on destiny'}
{'score': 135.0, 'sentence': 'It is because they do not brood on object'}
{'score': 105.0, 'sentence': 'It is because they do not act on action'}
{'score': 105.0, 'sentence': 'It is because they do not brood on achiever'}
{'score': 105.0, 'sentence': 'It is because they do not brood on organism'}
{'score': 105.0, 'sentence': 'It is because they do not brood on entity'}
{'score': 105.0, 'sentence': 'It is because they do not brood on fortune'}
{'score': 105.0, 'sentence': 'It is because they do not harp on happening'}
{'score': 105.0, 'sentence': 'It is because they do not consist on cause'}
{'score': 105.0, 'sentence': 'It is because they do not lie on luck'}
{'score': 105.0, 'sentence': 'It is because they do not mind on mortal'}
{'score': 105.0, 'sentence': 'It is because they do not populate on prosperity'}
{'score': 105.0, 'sentence': 'It is because they do not brood on someone'}
{'score': 105.0, 'sentence': 'It is because they do not worry on winner'}
{'score': 105.0, 'sentence': 'It is because they do not brood on unit'}
{'score': 100.0, 'sentence': 'It is because they do not brood on succes'}
{'score': 70.0, 'sentence': 'It is because they do not repeat on succes'}
{'score': 70.0, 'sentence': 'It is because they do not tell on succes'}
{'score': 70.0, 'sentence': 'It is because they do not think on succes'}

BEST SENTENCE:
{'score': 345.0, 'sentence': 'It is because they do not inhabit on individual'}


[{'ignore': False, 'word_original': 'That', 'word_lower': 'that', 'pos': 'DT', 'word_new': 'That'}, {'ignore': False, 'word_original': 'it', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'it'}, {'ignore': False, 'word_original': 'never', 'word_lower': 'never', 'pos': 'RB', 'word_new': 'never'}, {'ignore': False, 'word_original': 'goes', 'word_lower': 'goes', 'pos': 'VBZ', 'word_new': 'goes'}, {'ignore': False, 'word_original': 'away', 'word_lower': 'away', 'pos': 'RB', 'word_new': 'away'}]
{'score': 55.0, 'sentence': 'That it never occurs away'}
{'score': 55.0, 'sentence': 'That it never becomes by'}
{'score': 55.0, 'sentence': 'That it never functions forth'}
{'score': 55.0, 'sentence': 'That it never extends away'}
{'score': 25.0, 'sentence': 'That it never operates away'}
{'score': 25.0, 'sentence': 'That it never acts away'}
{'score': 25.0, 'sentence': 'That it never travels off'}
{'score': 25.0, 'sentence': 'That it never travels out'}
{'score': 25.0, 'sentence': 'That it never travels away'}
{'score': 25.0, 'sentence': 'That it never chokes away'}
{'score': 25.0, 'sentence': 'That it never departs away'}
{'score': 25.0, 'sentence': 'That it never endures away'}
{'score': 25.0, 'sentence': 'That it never goes away'}
{'score': 25.0, 'sentence': 'That it never happens away'}
{'score': 25.0, 'sentence': 'That it never compares away'}
{'score': 25.0, 'sentence': 'That it never leads away'}
{'score': 25.0, 'sentence': 'That it never moves away'}
{'score': 25.0, 'sentence': 'That it never proceeds away'}
{'score': 25.0, 'sentence': 'That it never runs away'}
{'score': 25.0, 'sentence': 'That it never sounds away'}
{'score': 25.0, 'sentence': 'That it never vanishes away'}
{'score': 25.0, 'sentence': 'That it never works away'}

BEST SENTENCE:
{'score': 55.0, 'sentence': 'That it never occurs away'}

\end{verbatim}


\chapter*{'Assembly Amount'}

\begin{verbatim}

f = open("tao-te-ching.txt","r")
body = f.read()
chapters = chapter_split(body)
f.close()

def tao_rmx(text):
    rmx = phonetilicious(text,
              alliteration_only = True, 
              number_of_examples = 1, 
              split_by = "punctuation",
              force_phoneme = [Consonants, Vowels], # Consonants, Vowels, [], ["K"]
              word_additions = [],
              hyper_profanity = False,
              flatten = False, 
              normalize = False, 
              try_to_avoid_dups = True,
              debug = True)
    linguistic_nectar = " ".join(rmx)
    return linguistic_nectar
    
abstraction_three = tao_rmx(chapters[3])
 
print abstraction_three



[{'ignore': False, 'word_original': 'Chapter', 'word_lower': 'chapter', 'pos': 'NN', 'word_new': 'Chapter'}, {'ignore': False, 'word_original': '3', 'word_lower': '3', 'pos': 'NN', 'word_new': '3'}]
{'score': 40.0, 'sentence': 'Assembly Amount'}
{'score': 40.0, 'sentence': 'Episode Entity'}
{'score': 40.0, 'sentence': 'Phase Figure'}
{'score': 40.0, 'sentence': 'Event Integer'}
{'score': 40.0, 'sentence': 'Club Quantity'}
{'score': 40.0, 'sentence': 'Lodge Leash'}
{'score': 40.0, 'sentence': 'Music Measure'}
{'score': 10.0, 'sentence': 'Chapter Three'}
{'score': 10.0, 'sentence': 'Abstraction Three'}
{'score': 10.0, 'sentence': 'Order Three'}
{'score': 10.0, 'sentence': 'Chapter Digit'}
{'score': 10.0, 'sentence': 'Guild Three'}
{'score': 10.0, 'sentence': 'Happening Three'}
{'score': 10.0, 'sentence': 'Chapter Number'}
{'score': 10.0, 'sentence': 'Period Three'}
{'score': 10.0, 'sentence': 'Writing Three'}
{'score': 10.0, 'sentence': 'Section Three'}
{'score': 10.0, 'sentence': 'Chapter Trio'}

BEST SENTENCE:
{'score': 40.0, 'sentence': 'Assembly Amount'}

[{'ignore': False, 'word_original': 'Do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'Do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'glorify', 'word_lower': 'glorify', 'pos': 'VB', 'word_new': 'glorify'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'achievers', 'word_lower': 'achievers', 'pos': 'NNS', 'word_new': 'achievers'}]
{'score': 55.0, 'sentence': 'Do not aggrandize the achievers'}
{'score': 55.0, 'sentence': 'Do not alter the organisms'}
{'score': 55.0, 'sentence': 'Do not dramatize the achievers'}
{'score': 55.0, 'sentence': 'Do not extol the individuals'}
{'score': 55.0, 'sentence': 'Do not cogitate the causes'}
{'score': 55.0, 'sentence': 'Do not modify the mortals'}
{'score': 55.0, 'sentence': 'Do not proclaim the people'}
{'score': 25.0, 'sentence': 'Do not laud the objects'}
{'score': 25.0, 'sentence': 'Do not amplify the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the beings'}
{'score': 25.0, 'sentence': 'Do not change the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the entities'}
{'score': 25.0, 'sentence': 'Do not glorify the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the wholes'}
{'score': 25.0, 'sentence': 'Do not judge the achievers'}
{'score': 25.0, 'sentence': 'Do not overstate the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the successes'}
{'score': 25.0, 'sentence': 'Do not think the achievers'}
{'score': 25.0, 'sentence': 'Do not value the achievers'}
{'score': 25.0, 'sentence': 'Do not laud the winners'}
{'score': 25.0, 'sentence': 'Do not laud the units'}

BEST SENTENCE:
{'score': 55.0, 'sentence': 'Do not aggrandize the achievers'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'people', 'word_lower': 'people', 'pos': 'NNS', 'word_new': 'people'}, {'ignore': False, 'word_original': 'will', 'word_lower': 'will', 'pos': 'MD', 'word_new': 'will'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'squabble', 'word_lower': 'squabble', 'pos': 'VB', 'word_new': 'squabble'}]
{'score': 150.0, 'sentence': 'So the stocks will not squabble'}
{'score': 60.0, 'sentence': 'So the abstractions will not act'}
{'score': 60.0, 'sentence': 'So the bloodlines will not bicker'}
{'score': 60.0, 'sentence': 'So the descents will not debate'}
{'score': 60.0, 'sentence': 'So the families will not fence'}
{'score': 60.0, 'sentence': 'So the clans will not quibble'}
{'score': 60.0, 'sentence': 'So the multitudes will not move'}
{'score': 60.0, 'sentence': 'So the tribes will not talk'}
{'score': 30.0, 'sentence': 'So the peoples will not argue'}
{'score': 30.0, 'sentence': 'So the peoples will not quibble'}
{'score': 30.0, 'sentence': 'So the origins will not quibble'}
{'score': 30.0, 'sentence': 'So the entities will not quibble'}
{'score': 30.0, 'sentence': 'So the groups will not quibble'}
{'score': 30.0, 'sentence': 'So the peoples will not interact'}
{'score': 30.0, 'sentence': 'So the lineages will not quibble'}

BEST SENTENCE:
{'score': 150.0, 'sentence': 'So the stocks will not squabble'}


[{'ignore': False, 'word_original': 'Do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'Do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'treasure', 'word_lower': 'treasure', 'pos': 'NN', 'word_new': 'treasure'}, {'ignore': False, 'word_original': 'goods', 'word_lower': 'goods', 'pos': 'NNS', 'word_new': 'goods'}, {'ignore': False, 'word_original': 'that', 'word_lower': 'that', 'pos': 'IN', 'word_new': 'that'}, {'ignore': False, 'word_original': 'are', 'word_lower': 'are', 'pos': 'VBP', 'word_new': 'are'}, {'ignore': False, 'word_original': 'hard', 'word_lower': 'hard', 'pos': 'JJ', 'word_new': 'hard'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'obtain', 'word_lower': 'obtain', 'pos': 'VB', 'word_new': 'obtain'}]
{'score': 345.0, 'sentence': 'Do not art artifacts that are arduous to obtain'}
{'score': 345.0, 'sentence': 'Do not group goods that are grueling to get'}
{'score': 345.0, 'sentence': 'Do not whole wholes that are hard to hold'}
{'score': 165.0, 'sentence': 'Do not collection commodities that are concentrated to obtain'}
{'score': 165.0, 'sentence': 'Do not possession goods that are punishing to prevail'}
{'score': 165.0, 'sentence': 'Do not treasure goods that are tough to obtain'}
{'score': 105.0, 'sentence': 'Do not asset advantages that are difficult to obtain'}
{'score': 105.0, 'sentence': 'Do not accumulation goods that are difficult to obtain'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are difficult to obtain'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are difficult to be'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are difficult to change'}
{'score': 105.0, 'sentence': 'Do not entity entities that are difficult to obtain'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are difficult to find'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are intemperate to incur'}
{'score': 105.0, 'sentence': 'Do not treasure goods that are knockout to obtain'}
{'score': 105.0, 'sentence': 'Do not rich goods that are difficult to receive'}
{'score': 105.0, 'sentence': 'Do not treasure vantages that are voiceless to obtain'}
{'score': 105.0, 'sentence': 'Do not unit units that are difficult to obtain'}
{'score': 75.0, 'sentence': 'Do not gem goods that are difficult to obtain'}
{'score': 75.0, 'sentence': 'Do not treasure goods that are laborious to obtain'}
{'score': 75.0, 'sentence': 'Do not treasure goods that are severe to obtain'}
{'score': 75.0, 'sentence': 'Do not wealth goods that are difficult to obtain'}

BEST SENTENCE:
{'score': 345.0, 'sentence': 'Do not art artifacts that are arduous to obtain'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'people', 'word_lower': 'people', 'pos': 'NNS', 'word_new': 'people'}, {'ignore': False, 'word_original': 'will', 'word_lower': 'will', 'pos': 'MD', 'word_new': 'will'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'become', 'word_lower': 'become', 'pos': 'VB', 'word_new': 'become'}, {'ignore': False, 'word_original': 'thieves', 'word_lower': 'thieves', 'pos': 'NNS', 'word_new': 'thieves'}]
{'score': 335.0, 'sentence': 'So the stocks will not suit souls'}
{'score': 155.0, 'sentence': 'So the origins will not alter organisms'}
{'score': 155.0, 'sentence': 'So the bloodlines will not become beings'}
{'score': 155.0, 'sentence': 'So the multitudes will not metamorphose malefactors'}
{'score': 65.0, 'sentence': 'So the peoples will not amend offenders'}
{'score': 65.0, 'sentence': 'So the families will not become felons'}
{'score': 65.0, 'sentence': 'So the peoples will not embellish individuals'}
{'score': 65.0, 'sentence': 'So the clans will not become criminals'}
{'score': 65.0, 'sentence': 'So the peoples will not become principals'}
{'score': 60.0, 'sentence': 'So the groups will not go thiefs'}
{'score': 60.0, 'sentence': 'So the tribes will not turn thiefs'}
{'score': 35.0, 'sentence': 'So the peoples will not become objects'}
{'score': 35.0, 'sentence': 'So the peoples will not become outlaws'}
{'score': 35.0, 'sentence': 'So the peoples will not become wholes'}
{'score': 35.0, 'sentence': 'So the peoples will not become wrongdoers'}
{'score': 35.0, 'sentence': 'So the peoples will not become units'}
{'score': 30.0, 'sentence': 'So the abstractions will not become thiefs'}
{'score': 30.0, 'sentence': 'So the peoples will not become thiefs'}
{'score': 30.0, 'sentence': 'So the peoples will not change thiefs'}
{'score': 30.0, 'sentence': 'So the descents will not become thiefs'}
{'score': 30.0, 'sentence': 'So the entities will not become thiefs'}
{'score': 30.0, 'sentence': 'So the lineages will not become thiefs'}

BEST SENTENCE:
{'score': 335.0, 'sentence': 'So the stocks will not suit souls'}


[{'ignore': False, 'word_original': 'Do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'Do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'show', 'word_lower': 'show', 'pos': 'NN', 'word_new': 'show'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'desired', 'word_lower': 'desired', 'pos': 'VBN', 'word_new': 'desired'}, {'ignore': False, 'word_original': 'things', 'word_lower': 'things', 'pos': 'NNS', 'word_new': 'things'}]
{'score': 330.0, 'sentence': 'Do not display the desired deeds'}
{'score': 150.0, 'sentence': 'Do not communication the communicated concerns'}
{'score': 150.0, 'sentence': 'Do not misrepresentation the moved matters'}
{'score': 150.0, 'sentence': 'Do not pretense the passed properties'}
{'score': 150.0, 'sentence': 'Do not recreation the requested relations'}
{'score': 90.0, 'sentence': 'Do not activity the desired actions'}
{'score': 90.0, 'sentence': 'Do not appearance the desired affairs'}
{'score': 90.0, 'sentence': 'Do not entertainment the desired entities'}
{'score': 90.0, 'sentence': 'Do not feigning the desired feelings'}
{'score': 90.0, 'sentence': 'Do not event the desired events'}
{'score': 90.0, 'sentence': 'Do not show the desired knowledge'}
{'score': 90.0, 'sentence': 'Do not simulation the desired situations'}
{'score': 60.0, 'sentence': 'Do not show the desired artifacts'}
{'score': 60.0, 'sentence': 'Do not show the desired ideas'}
{'score': 60.0, 'sentence': 'Do not show the desired aims'}
{'score': 60.0, 'sentence': 'Do not show the desired goals'}
{'score': 60.0, 'sentence': 'Do not show the hoped holdings'}
{'score': 60.0, 'sentence': 'Do not show the trusted targets'}
{'score': 60.0, 'sentence': 'Do not show the desired things'}
{'score': 60.0, 'sentence': 'Do not show the wanted wonders'}
{'score': 60.0, 'sentence': 'Do not show the desired units'}
{'score': 55.0, 'sentence': 'Do not show the desired thingss'}

BEST SENTENCE:
{'score': 330.0, 'sentence': 'Do not display the desired deeds'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'their', 'word_lower': 'their', 'pos': 'PRP$', 'word_new': 'their'}, {'ignore': False, 'word_original': 'hearts', 'word_lower': 'hearts', 'pos': 'NNS', 'word_new': 'hearts'}, {'ignore': False, 'word_original': 'will', 'word_lower': 'will', 'pos': 'MD', 'word_new': 'will'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'be', 'word_lower': 'be', 'pos': 'VB', 'word_new': 'be'}, {'ignore': False, 'word_original': 'confused', 'word_lower': 'confused', 'pos': 'VBN', 'word_new': 'confused'}]
{'score': 155.0, 'sentence': 'So their beliefs will not be befuddled'}
{'score': 65.0, 'sentence': 'So their affections will not be obscured'}
{'score': 65.0, 'sentence': 'So their organs will not be altered'}
{'score': 65.0, 'sentence': 'So their eyes will not be identified'}
{'score': 65.0, 'sentence': 'So their dispositions will not be discombobulated'}
{'score': 65.0, 'sentence': 'So their feelings will not be flurried'}
{'score': 65.0, 'sentence': 'So their impressions will not be embarrassed'}
{'score': 65.0, 'sentence': 'So their kernels will not be confused'}
{'score': 65.0, 'sentence': 'So their locations will not be linked'}
{'score': 65.0, 'sentence': 'So their meat will not be mistaken'}
{'score': 65.0, 'sentence': 'So their nerves will not be confused'}
{'score': 65.0, 'sentence': 'So their pumps will not be pieced'}
{'score': 65.0, 'sentence': 'So their regions will not be recognized'}
{'score': 65.0, 'sentence': 'So their centers will not be confused'}
{'score': 65.0, 'sentence': 'So their temperaments will not be tacked'}
{'score': 65.0, 'sentence': 'So their thoughts will not be thrown'}
{'score': 35.0, 'sentence': 'So their objects will not be confused'}
{'score': 35.0, 'sentence': 'So their attributes will not be confused'}
{'score': 35.0, 'sentence': 'So their areas will not be confused'}
{'score': 35.0, 'sentence': 'So their games will not be confused'}
{'score': 35.0, 'sentence': 'So their hearts will not be confused'}
{'score': 35.0, 'sentence': 'So their shapes will not be confused'}
{'score': 30.0, 'sentence': 'So their heartss will not be confused'}
{'score': 30.0, 'sentence': 'So their heartss will not be changed'}
{'score': 30.0, 'sentence': 'So their heartss will not be aroused'}
{'score': 30.0, 'sentence': 'So their heartss will not be jumbled'}

BEST SENTENCE:
{'score': 155.0, 'sentence': 'So their beliefs will not be befuddled'}


[{'ignore': False, 'word_original': 'Thus', 'word_lower': 'thus', 'pos': 'RB', 'word_new': 'Thus'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'governance', 'word_lower': 'governance', 'pos': 'NN', 'word_new': 'governance'}, {'ignore': False, 'word_original': 'of', 'word_lower': 'of', 'pos': 'IN', 'word_new': 'of'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'sage', 'word_lower': 'sage', 'pos': 'NN', 'word_new': 'sage'}]
{'score': 59.99999999999999, 'sentence': 'Therefore the organization of the organism'}
{'score': 59.99999999999999, 'sentence': 'Therefore the bras of the being'}
{'score': 59.99999999999999, 'sentence': 'Therefore the establishment of the intellectual'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the object'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the sage'}
{'score': 49.99999999999999, 'sentence': 'Therefore the deed of the sage'}
{'score': 49.99999999999999, 'sentence': 'Therefore the entity of the sage'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the herb'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the flavoring'}
{'score': 49.99999999999999, 'sentence': 'Therefore the governance of the sage'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the cause'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the mentor'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the nutrient'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the person'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the tracheophyte'}
{'score': 49.99999999999999, 'sentence': 'Therefore the administration of the unit'}
{'score': 29.999999999999996, 'sentence': 'Hence the administration of the whole'}
{'score': 29.999999999999996, 'sentence': 'So the administration of the sage'}

BEST SENTENCE:
{'score': 59.99999999999999, 'sentence': 'Therefore the organization of the organism'}


[{'ignore': False, 'word_original': ':', 'word_lower': ':', 'pos': ':', 'word_new': ':'}]
{'score': 0.0, 'sentence': ':'}

BEST SENTENCE:
{'score': 0.0, 'sentence': ':'}


[{'ignore': False, 'word_original': 'Empties', 'word_lower': 'empties', 'pos': 'NNS', 'word_new': 'Empties'}, {'ignore': False, 'word_original': 'their', 'word_lower': 'their', 'pos': 'PRP$', 'word_new': 'their'}, {'ignore': False, 'word_original': 'hearts', 'word_lower': 'hearts', 'pos': 'NNS', 'word_new': 'hearts'}]
{'score': 45.0, 'sentence': 'Artifacts their objects'}
{'score': 45.0, 'sentence': 'Empties their areas'}
{'score': 45.0, 'sentence': 'Wholes their hearts'}
{'score': 45.0, 'sentence': 'Containers their kernels'}
{'score': 15.0, 'sentence': 'Empties their attributes'}
{'score': 15.0, 'sentence': 'Empties their affections'}
{'score': 15.0, 'sentence': 'Empties their organs'}
{'score': 15.0, 'sentence': 'Empties their eyes'}
{'score': 15.0, 'sentence': 'Empties their beliefs'}
{'score': 15.0, 'sentence': 'Empties their dispositions'}
{'score': 15.0, 'sentence': 'Empties their feelings'}
{'score': 15.0, 'sentence': 'Empties their games'}
{'score': 15.0, 'sentence': 'Empties their impressions'}
{'score': 15.0, 'sentence': 'Empties their locations'}
{'score': 15.0, 'sentence': 'Empties their meat'}
{'score': 15.0, 'sentence': 'Empties their nerves'}
{'score': 15.0, 'sentence': 'Empties their pumps'}
{'score': 15.0, 'sentence': 'Empties their regions'}
{'score': 15.0, 'sentence': 'Empties their centers'}
{'score': 15.0, 'sentence': 'Empties their shapes'}
{'score': 15.0, 'sentence': 'Empties their temperaments'}
{'score': 15.0, 'sentence': 'Empties their thoughts'}
{'score': 10.0, 'sentence': 'Empties their heartss'}
{'score': 10.0, 'sentence': 'Units their heartss'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Artifacts their objects'}


[{'ignore': False, 'word_original': 'Fills', 'word_lower': 'fills', 'pos': 'NNS', 'word_new': 'Fills'}, {'ignore': False, 'word_original': 'their', 'word_lower': 'their', 'pos': 'PRP$', 'word_new': 'their'}, {'ignore': False, 'word_original': 'bellies', 'word_lower': 'bellies', 'pos': 'NNS', 'word_new': 'bellies'}]
{'score': 45.0, 'sentence': 'Abstractions their attributes'}
{'score': 45.0, 'sentence': 'Fills their fats'}
{'score': 45.0, 'sentence': 'Parts their prominences'}
{'score': 45.0, 'sentence': 'Relations their regions'}
{'score': 45.0, 'sentence': 'Stuffs their surfaces'}
{'score': 15.0, 'sentence': 'Fills their objects'}
{'score': 15.0, 'sentence': 'Fills their bellies'}
{'score': 15.0, 'sentence': 'Fills their insides'}
{'score': 15.0, 'sentence': 'Fills their juts'}
{'score': 15.0, 'sentence': 'Fills their locations'}
{'score': 15.0, 'sentence': 'Fills their shapes'}
{'score': 15.0, 'sentence': 'Fills their tissues'}
{'score': 15.0, 'sentence': 'Fills their things'}
{'score': 15.0, 'sentence': 'Fills their venters'}
{'score': 10.0, 'sentence': 'Amounts their abdomens'}
{'score': 10.0, 'sentence': 'Fills their abdomens'}
{'score': 10.0, 'sentence': 'Entities their abdomens'}
{'score': 10.0, 'sentence': 'Quantities their abdomens'}
{'score': 10.0, 'sentence': 'Materials their abdomens'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Abstractions their attributes'}


[{'ignore': False, 'word_original': 'Weakens', 'word_lower': 'weakens', 'pos': 'VBZ', 'word_new': 'Weakens'}, {'ignore': False, 'word_original': 'their', 'word_lower': 'their', 'pos': 'PRP$', 'word_new': 'their'}, {'ignore': False, 'word_original': 'ambitions', 'word_lower': 'ambitions', 'pos': 'NNS', 'word_new': 'ambitions'}]
{'score': 45.0, 'sentence': 'Acts their ambitions'}
{'score': 45.0, 'sentence': 'Damps their dreams'}
{'score': 45.0, 'sentence': 'Falls their feelings'}
{'score': 45.0, 'sentence': 'Subverts their states'}
{'score': 15.0, 'sentence': 'Weakens their ambitions'}
{'score': 15.0, 'sentence': 'Undermines their ambitions'}
{'score': 15.0, 'sentence': 'Alters their ambitions'}
{'score': 15.0, 'sentence': 'Breaks their ambitions'}
{'score': 15.0, 'sentence': 'Changes their ambitions'}
{'score': 15.0, 'sentence': 'Weakens their entities'}
{'score': 15.0, 'sentence': 'Lessens their ambitions'}
{'score': 15.0, 'sentence': 'Modifies their ambitions'}
{'score': 15.0, 'sentence': 'Refuses their ambitions'}
{'score': 15.0, 'sentence': 'Weakens their traits'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Acts their ambitions'}


[{'ignore': False, 'word_original': 'Strengthens', 'word_lower': 'strengthens', 'pos': 'NNS', 'word_new': 'Strengthens'}, {'ignore': False, 'word_original': 'their', 'word_lower': 'their', 'pos': 'PRP$', 'word_new': 'their'}, {'ignore': False, 'word_original': 'bones', 'word_lower': 'bones', 'pos': 'NNS', 'word_new': 'bones'}]
{'score': 45.0, 'sentence': 'Strengthens their stuffs'}
{'score': 15.0, 'sentence': 'Strengthens their artifacts'}
{'score': 15.0, 'sentence': 'Strengthens their abstractions'}
{'score': 15.0, 'sentence': 'Strengthens their oss'}
{'score': 15.0, 'sentence': 'Strengthens their bones'}
{'score': 15.0, 'sentence': 'Strengthens their devices'}
{'score': 15.0, 'sentence': 'Strengthens their entities'}
{'score': 15.0, 'sentence': 'Strengthens their wholes'}
{'score': 15.0, 'sentence': 'Strengthens their instruments'}
{'score': 15.0, 'sentence': 'Strengthens their colors'}
{'score': 15.0, 'sentence': 'Strengthens their materials'}
{'score': 15.0, 'sentence': 'Strengthens their pearls'}
{'score': 15.0, 'sentence': 'Strengthens their relations'}
{'score': 15.0, 'sentence': 'Strengthens their tissues'}
{'score': 15.0, 'sentence': 'Strengthens their things'}
{'score': 15.0, 'sentence': 'Strengthens their whites'}
{'score': 15.0, 'sentence': 'Strengthens their units'}
{'score': 10.0, 'sentence': 'Strengthens their boness'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Strengthens their stuffs'}


[{'ignore': False, 'word_original': 'Let', 'word_lower': 'let', 'pos': 'VB', 'word_new': 'Let'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'people', 'word_lower': 'people', 'pos': 'NNS', 'word_new': 'people'}, {'ignore': False, 'word_original': 'have', 'word_lower': 'have', 'pos': 'VBP', 'word_new': 'have'}, {'ignore': False, 'word_original': 'no', 'word_lower': 'no', 'pos': 'DT', 'word_new': 'no'}, {'ignore': False, 'word_original': 'cunning', 'word_lower': 'cunning', 'pos': 'JJ', 'word_new': 'cunning'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'no', 'word_lower': 'no', 'pos': 'DT', 'word_new': 'no'}, {'ignore': False, 'word_original': 'greed', 'word_lower': 'greed', 'pos': 'NN', 'word_new': 'greed'}]
{'score': 124.99999999999999, 'sentence': 'Stimulate the stocks have no slick and no sin'}
{'score': 124.99999999999999, 'sentence': 'Transfer the tribes have no tricky and no tendency'}
{'score': 64.99999999999999, 'sentence': 'Accept the abstractions have no cunning and no avarice'}
{'score': 64.99999999999999, 'sentence': 'Get the groups have no cunning and no greed'}
{'score': 64.99999999999999, 'sentence': 'Induce the peoples have no ingenious and no inclination'}
{'score': 64.99999999999999, 'sentence': 'Countenance the clans have no cunning and no greed'}
{'score': 64.99999999999999, 'sentence': 'Make the multitudes have no cunning and no misconduct'}
{'score': 64.99999999999999, 'sentence': 'Permit the peoples have no cunning and no property'}
{'score': 34.99999999999999, 'sentence': 'Allow the peoples have no cunning and no greed'}
{'score': 34.99999999999999, 'sentence': 'Alter the origins have no cunning and no greed'}
{'score': 34.99999999999999, 'sentence': 'Let the descents have no cunning and no desire'}
{'score': 34.99999999999999, 'sentence': 'Let the entities have no cunning and no entity'}
{'score': 34.99999999999999, 'sentence': 'Let the families have no foxy and no greed'}
{'score': 34.99999999999999, 'sentence': 'Let the lineages have no cunning and no greed'}
{'score': 34.99999999999999, 'sentence': 'Rent the peoples have no cunning and no wrongdoing'}
{'score': 24.999999999999996, 'sentence': 'Let the peoples have no cunning and no greed'}
{'score': 24.999999999999996, 'sentence': 'Let the bloodlines have no cunning and no greed'}
{'score': 24.999999999999996, 'sentence': 'Change the peoples have no cunning and no greed'}
{'score': 24.999999999999996, 'sentence': 'Let the peoples have no wily and no greed'}
{'score': 21.0, 'sentence': 'Have the peoples have no cunning and no greed'}

BEST SENTENCE:
{'score': 124.99999999999999, 'sentence': 'Stimulate the stocks have no slick and no sin'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'those', 'word_lower': 'those', 'pos': 'DT', 'word_new': 'those'}, {'ignore': False, 'word_original': 'who', 'word_lower': 'who', 'pos': 'WP', 'word_new': 'who'}, {'ignore': False, 'word_original': 'scheme', 'word_lower': 'scheme', 'pos': 'NN', 'word_new': 'scheme'}, {'ignore': False, 'word_original': 'will', 'word_lower': 'will', 'pos': 'MD', 'word_new': 'will'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'dare', 'word_lower': 'dare', 'pos': 'VB', 'word_new': 'dare'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'meddle', 'word_lower': 'meddle', 'pos': 'VB', 'word_new': 'meddle'}]
{'score': 195.0, 'sentence': 'So those who scheme will not transmit to tamper'}
{'score': 165.0, 'sentence': 'So those who message will not move to meddle'}
{'score': 105.0, 'sentence': 'So those who scheme will not invite to intervene'}
{'score': 75.0, 'sentence': 'So those who scheme will not dare to meddle'}
{'score': 75.0, 'sentence': 'So those who abstraction will not act to meddle'}
{'score': 75.0, 'sentence': 'So those who scheme will not bid to meddle'}
{'score': 75.0, 'sentence': 'So those who scheme will not challenge to meddle'}
{'score': 75.0, 'sentence': 'So those who dodge will not dare to meddle'}
{'score': 75.0, 'sentence': 'So those who content will not quest to meddle'}
{'score': 75.0, 'sentence': 'So those who knowledge will not dare to meddle'}
{'score': 75.0, 'sentence': 'So those who plan will not presume to meddle'}
{'score': 75.0, 'sentence': 'So those who representation will not request to meddle'}
{'score': 45.0, 'sentence': 'So those who untruth will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who outline will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who idea will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who entity will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who falsehood will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who group will not dare to meddle'}
{'score': 45.0, 'sentence': 'So those who thought will not dare to meddle'}

BEST SENTENCE:
{'score': 195.0, 'sentence': 'So those who scheme will not transmit to tamper'}


[{'ignore': False, 'word_original': 'Act', 'word_lower': 'act', 'pos': 'NN', 'word_new': 'Act'}, {'ignore': False, 'word_original': 'without', 'word_lower': 'without', 'pos': 'IN', 'word_new': 'without'}, {'ignore': False, 'word_original': 'contrivance', 'word_lower': 'contrivance', 'pos': 'NN', 'word_new': 'contrivance'}]
{'score': 45.0, 'sentence': 'Act without abstraction'}
{'score': 45.0, 'sentence': 'Deed without dodge'}
{'score': 45.0, 'sentence': 'Enactment without entity'}
{'score': 45.0, 'sentence': 'Instrument without invention'}
{'score': 45.0, 'sentence': 'Communication without contraption'}
{'score': 45.0, 'sentence': 'Number without knowledge'}
{'score': 45.0, 'sentence': 'Performance without power'}
{'score': 45.0, 'sentence': 'Act without widget'}
{'score': 15.0, 'sentence': 'Act without artifact'}
{'score': 15.0, 'sentence': 'Act without appliance'}
{'score': 15.0, 'sentence': 'Act without organization'}
{'score': 15.0, 'sentence': 'Act without idea'}
{'score': 15.0, 'sentence': 'Bit without appliance'}
{'score': 15.0, 'sentence': 'Act without arrangement'}
{'score': 15.0, 'sentence': 'Act without gadget'}
{'score': 15.0, 'sentence': 'Act without whole'}
{'score': 15.0, 'sentence': 'Manifestation without appliance'}
{'score': 15.0, 'sentence': 'Routine without appliance'}
{'score': 15.0, 'sentence': 'Act without stratagem'}
{'score': 15.0, 'sentence': 'Show without appliance'}
{'score': 15.0, 'sentence': 'Turn without appliance'}
{'score': 15.0, 'sentence': 'Act without thought'}
{'score': 15.0, 'sentence': 'Act without unit'}

BEST SENTENCE:
{'score': 45.0, 'sentence': 'Act without abstraction'}


[{'ignore': False, 'word_original': 'And', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'And'}, {'ignore': False, 'word_original': 'nothing', 'word_lower': 'nothing', 'pos': 'NN', 'word_new': 'nothing'}, {'ignore': False, 'word_original': 'will', 'word_lower': 'will', 'pos': 'MD', 'word_new': 'will'}, {'ignore': False, 'word_original': 'be', 'word_lower': 'be', 'pos': 'VB', 'word_new': 'be'}, {'ignore': False, 'word_original': 'beyond', 'word_lower': 'beyond', 'pos': 'IN', 'word_new': 'beyond'}, {'ignore': False, 'word_original': 'control', 'word_lower': 'control', 'pos': 'NN', 'word_new': 'control'}]
{'score': 180.0, 'sentence': 'And amount will be beyond ascendance'}
{'score': 150.0, 'sentence': 'And nothing will be beyond belief'}
{'score': 90.0, 'sentence': 'And abstraction will be beyond activity'}
{'score': 90.0, 'sentence': 'And quantity will be beyond control'}
{'score': 90.0, 'sentence': 'And measure will be beyond mastery'}
{'score': 90.0, 'sentence': 'And nothing will be beyond knowledge'}
{'score': 90.0, 'sentence': 'And cipher will be beyond standard'}
{'score': 60.0, 'sentence': 'And nothing will be beyond argumentation'}
{'score': 60.0, 'sentence': 'And nothing will be beyond control'}
{'score': 60.0, 'sentence': 'And nothing will be beyond ideal'}
{'score': 60.0, 'sentence': 'And nothing will be beyond dominance'}
{'score': 60.0, 'sentence': 'And entity will be beyond control'}
{'score': 60.0, 'sentence': 'And nothing will be beyond whole'}
{'score': 60.0, 'sentence': 'And nothing will be beyond event'}
{'score': 60.0, 'sentence': 'And nothing will be beyond line'}
{'score': 60.0, 'sentence': 'And nothing will be beyond power'}
{'score': 60.0, 'sentence': 'And nothing will be beyond restraint'}
{'score': 60.0, 'sentence': 'And nothing will be beyond trait'}
{'score': 60.0, 'sentence': 'And nothing will be beyond thought'}
{'score': 60.0, 'sentence': 'And nothing will be beyond unit'}
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

BEST SENTENCE:
{'score': 180.0, 'sentence': 'And amount will be beyond ascendance'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

worst_sentence = """
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
"""

while(true):
	print worst_sentence
	 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

 WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}

WORST SENTENCE:
{'score': 60.0, 'sentence': 'And zero will be beyond control'}
 
HALT 

\end{verbatim}
\newpage

\chapter*{'Organization Foursome'}

\begin{verbatim}
['Tao Te Ching']
[{'ignore': False, 'word_original': 'Tao', 'word_lower': 'tao', 'pos': 'NNP', 'word_new': 'Tao'}, {'ignore': False, 'word_original': 'Te', 'word_lower': 'te', 'pos': 'NN', 'word_new': 'Te'}, {'ignore': False, 'word_original': 'Ching', 'word_lower': 'ching', 'pos': 'NNP', 'word_new': 'Ching'}]
{'score': 1125.0, 'sentence': 'Individual Syllable Ching'}
{'score': 1045.0, 'sentence': 'Construct Constituent Ching'}
{'score': 885.0, 'sentence': 'Individual Element Ching'}
{'score': 765.0, 'sentence': 'Construct Component Ching'}
{'score': 765.0, 'sentence': 'Conception Component Ching'}
{'score': 560.0, 'sentence': 'Individual Tellurium Ching'}
{'score': 545.0, 'sentence': 'Unit Constituent Ching'}
{'score': 540.0, 'sentence': 'Somebody Substance Ching'}
{'score': 475.0, 'sentence': 'Disciple Syllable Ching'}
{'score': 470.0, 'sentence': 'Taoist Substance Ching'}
{'score': 455.0, 'sentence': 'Taoist Constituent Ching'}
{'score': 390.0, 'sentence': 'Conception Portion Ching'}
{'score': 310.0, 'sentence': 'Organism Tellurium Ching'}
{'score': 305.0, 'sentence': 'Adherent Tellurium Ching'}
{'score': 290.0, 'sentence': 'Principle Part Ching'}
{'score': 235.0, 'sentence': 'Abstraction Matter Ching'}
{'score': 235.0, 'sentence': 'Someone Tellurium Ching'}
{'score': 180.0, 'sentence': 'Disciple Tellurium Ching'}
{'score': 180.0, 'sentence': 'Somebody Tellurium Ching'}
{'score': 175.0, 'sentence': 'Follower Component Ching'}
{'score': 165.0, 'sentence': 'Being Tellurium Ching'}
{'score': 150.0, 'sentence': 'Concept Tellurium Ching'}
{'score': 140.0, 'sentence': 'Taoist Tellurium Ching'}
{'score': 140.0, 'sentence': 'Unit Tellurium Ching'}
{'score': 110.0, 'sentence': 'Follower Tellurium Ching'}
{'score': 105.0, 'sentence': 'Taoist Relation Ching'}
{'score': 100.0, 'sentence': 'Thought Tellurium Ching'}
{'score': 90.0, 'sentence': 'Follower Part Ching'}
{'score': 90.0, 'sentence': 'Follower Matter Ching'}
{'score': 85.0, 'sentence': 'Law Portion Ching'}
{'score': 70.0, 'sentence': 'Cause Tellurium Ching'}

BEST SENTENCE:
{'score': 1125.0, 'sentence': 'Individual Syllable Ching'}

['Chapter 1', '\n', '', '\n', 'The Tao that can be spoken is not the eternal Tao', '\n', 'The name that can be named is not the eternal name', '\n', 'The nameless is the origin of Heaven and Earth', '\n', 'The named is the mother of myriad things', '\n', 'Thus', ', ', 'constantly without desire', ', ', 'one observes its essence', '\n', 'Constantly with desire', ', ', 'one observes its manifestations', '\n', 'These two emerge together but differ in name', '\n', 'The unity is said to be the mystery', '\n', 'Mystery of mysteries', ', ', 'the door to all wonders', '\n', '', '\n', '', '\n', 'Chapter 2', '\n', '', '\n', 'When the world knows beauty as beauty', ', ', 'ugliness arises', '\n', 'When it knows good as good', ', ', 'evil arises', '\n', 'Thus being and non-being produce each other', '\n', 'Difficult and easy bring about each other', '\n', 'Long and short reveal each other', '\n', 'High and low support each other', '\n', 'Music and voice harmonize each other', '\n', 'Front and back follow each other', '\n', 'Therefore the sages', ':', '', '\n', 'Manage the work of detached actions', '\n', 'Conduct the teaching of no words', '\n', 'They work with myriad things but do not control', '\n', 'They create but do not possess', '\n', 'They act but do not presume', '\n', 'They succeed but do not dwell on success', '\n', 'It is because they do not dwell on success', '\n', 'That it never goes away', '\n', '', '\n', '', '\n', 'Chapter 3', '\n', '', '\n', 'Do not glorify the achievers', '\n', 'So the people will not squabble', '\n', 'Do not treasure goods that are hard to obtain', '\n', 'So the people will not become thieves', '\n', 'Do not show the desired things', '\n', 'So their hearts will not be confused', '\n', '', '\n', 'Thus the governance of the sage', ':', '', '\n', 'Empties their hearts', '\n', 'Fills their bellies', '\n', 'Weakens their ambitions', '\n', 'Strengthens their bones', '\n', '', '\n', 'Let the people have no cunning and no greed', '\n', 'So those who scheme will not dare to meddle', '\n', '', '\n', 'Act without contrivance', '\n', 'And nothing will be beyond control', '\n', '', '\n', '', '\n', 'Chapter 4', '\n', '', '\n', 'The Tao is empty', '\n', 'When utilized', ', ', 'it is not filled up', '\n', 'So deep', '! ', 'It seems to be the source of all things', '\n', '', '\n', 'It blunts the sharpness', '\n', 'Unravels the knots', '\n', 'Dims the glare', '\n', 'Mixes the dusts', '\n', '', '\n', 'So indistinct', '! ', 'It seems to exist', '\n', 'I do not know whose offspring it is', '\n', 'Its image is the predecessor of the Emperor', '\n', '', '\n', '', '\n', 

[{'ignore': False, 'word_original': 'Chapter', 'word_lower': 'chapter', 'pos': 'NN', 'word_new': 'Chapter'}, {'ignore': False, 'word_original': '4', 'word_lower': '4', 'pos': 'NN', 'word_new': '4'}]
{'score': 475.0, 'sentence': 'Organization Foursome'}
{'score': 465.0, 'sentence': 'Communication Quaternary'}
{'score': 435.0, 'sentence': 'Quantity Quartet'}
{'score': 370.0, 'sentence': 'Organization Quaternary'}
{'score': 355.0, 'sentence': 'Quantity Quaternary'}
{'score': 345.0, 'sentence': 'Subdivision Digit'}
{'score': 305.0, 'sentence': 'Society Foursome'}
{'score': 285.0, 'sentence': 'Subdivision Number'}
{'score': 260.0, 'sentence': 'Section Abstraction'}
{'score': 200.0, 'sentence': 'Society Quaternary'}
{'score': 165.0, 'sentence': 'Section Quaternary'}
{'score': 160.0, 'sentence': 'Subdivision Measure'}
{'score': 155.0, 'sentence': 'Assembly Foursome'}
{'score': 145.0, 'sentence': 'Order Quartet'}
{'score': 130.0, 'sentence': 'Chapter Quaternary'}
{'score': 125.0, 'sentence': 'Order Quaternary'}
{'score': 115.0, 'sentence': 'Music Figure'}
{'score': 110.0, 'sentence': 'Subdivision Fmy'}
{'score': 105.0, 'sentence': 'Guild Figure'}
{'score': 105.0, 'sentence': 'Stage Digit'}
{'score': 95.0, 'sentence': 'Society Fmy'}
{'score': 90.0, 'sentence': 'Lodge Quaternary'}
{'score': 80.0, 'sentence': 'Abstraction Fmy'}
{'score': 75.0, 'sentence': 'Phase Foursome'}
{'score': 35.0, 'sentence': 'Happening Fmy'}
{'score': 30.0, 'sentence': 'Gathering Fmy'}
{'score': 30.0, 'sentence': 'Episode Fmy'}
{'score': 30.0, 'sentence': 'Music Fmy'}
{'score': 25.0, 'sentence': 'Amount Fmy'}
{'score': 25.0, 'sentence': 'Chapter Fmy'}
{'score': 25.0, 'sentence': 'Writing Fmy'}
{'score': 20.0, 'sentence': 'Club Fmy'}
{'score': 15.0, 'sentence': 'Phase Fmy'}

BEST SENTENCE:
{'score': 475.0, 'sentence': 'Organization Foursome'}


[{'ignore': False, 'word_original': 'The', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'The'}, {'ignore': False, 'word_original': 'Tao', 'word_lower': 'tao', 'pos': 'NNP', 'word_new': 'Tao'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}, {'ignore': False, 'word_original': 'empty', 'word_lower': 'empty', 'pos': 'JJ', 'word_new': 'empty'}]
{'score': 860.0, 'sentence': 'The Individual is vacuous'}
{'score': 580.0, 'sentence': 'The Construct is vacuous'}
{'score': 520.0, 'sentence': 'The Individual is empty'}
{'score': 405.0, 'sentence': 'The Abstraction is vacuous'}
{'score': 360.0, 'sentence': 'The Principle is empty'}
{'score': 360.0, 'sentence': 'The Construct is empty'}
{'score': 300.0, 'sentence': 'The Organism is empty'}
{'score': 300.0, 'sentence': 'The Conception is empty'}
{'score': 265.0, 'sentence': 'The Adherent is empty'}
{'score': 260.0, 'sentence': 'The Adherent is hollow'}
{'score': 260.0, 'sentence': 'The Unit is vacuous'}
{'score': 225.0, 'sentence': 'The Someone is empty'}
{'score': 170.0, 'sentence': 'The Disciple is empty'}
{'score': 170.0, 'sentence': 'The Somebody is empty'}
{'score': 170.0, 'sentence': 'The Concept is empty'}
{'score': 170.0, 'sentence': 'The Taoist is vacuous'}
{'score': 165.0, 'sentence': 'The Disciple is hollow'}
{'score': 155.0, 'sentence': 'The Follower is hollow'}
{'score': 130.0, 'sentence': 'The Taoist is empty'}
{'score': 125.0, 'sentence': 'The Being is empty'}
{'score': 90.0, 'sentence': 'The Thought is empty'}
{'score': 90.0, 'sentence': 'The Cause is empty'}
{'score': 70.0, 'sentence': 'The Follower is empty'}
{'score': 55.0, 'sentence': 'The Law is empty'}

BEST SENTENCE:
{'score': 860.0, 'sentence': 'The Individual is vacuous'}


[{'ignore': False, 'word_original': 'When', 'word_lower': 'when', 'pos': 'WRB', 'word_new': 'When'}, {'ignore': False, 'word_original': 'utilized', 'word_lower': 'utilized', 'pos': 'VBN', 'word_new': 'utilized'}]
{'score': 85.0, 'sentence': 'When converted'}
{'score': 85.0, 'sentence': 'When exchanged'}
{'score': 75.0, 'sentence': 'When employed'}
{'score': 70.0, 'sentence': 'When changed'}
{'score': 55.0, 'sentence': 'When utilized'}
{'score': 50.0, 'sentence': 'When replaced'}
{'score': 40.0, 'sentence': 'When applied'}
{'score': 35.0, 'sentence': 'When used'}

BEST SENTENCE:
{'score': 85.0, 'sentence': 'When converted'}


[{'ignore': False, 'word_original': ',', 'word_lower': ',', 'pos': ',', 'word_new': ','}]
{'score': 0.0, 'sentence': ', '}

BEST SENTENCE:
{'score': 0.0, 'sentence': ', '}


[{'ignore': False, 'word_original': 'it', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'it'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'filled', 'word_lower': 'filled', 'pos': 'VBN', 'word_new': 'filled'}, {'ignore': False, 'word_original': 'up', 'word_lower': 'up', 'pos': 'IN', 'word_new': 'up'}]
{'score': 395.0, 'sentence': 'it is not ameliorated up'}
{'score': 325.0, 'sentence': 'it is not provided up'}
{'score': 295.0, 'sentence': 'it is not satisfied up'}
{'score': 290.0, 'sentence': 'it is not fulfilled up'}
{'score': 285.0, 'sentence': 'it is not repaired up'}
{'score': 280.0, 'sentence': 'it is not taken up'}
{'score': 240.0, 'sentence': 'it is not been up'}
{'score': 230.0, 'sentence': 'it is not occupied up'}
{'score': 230.0, 'sentence': 'it is not modified up'}
{'score': 220.0, 'sentence': 'it is not altered up'}
{'score': 215.0, 'sentence': 'it is not filled up'}
{'score': 215.0, 'sentence': 'it is not worked up'}
{'score': 210.0, 'sentence': 'it is not met up'}
{'score': 200.0, 'sentence': 'it is not consumed up'}
{'score': 165.0, 'sentence': 'it is not engaged up'}
{'score': 165.0, 'sentence': 'it is not employed up'}
{'score': 160.0, 'sentence': 'it is not changed up'}
{'score': 125.0, 'sentence': 'it is not hired up'}

BEST SENTENCE:
{'score': 395.0, 'sentence': 'it is not ameliorated up'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'deep', 'word_lower': 'deep', 'pos': 'JJ', 'word_new': 'deep'}]
{'score': 205.0, 'sentence': 'So mysterious'}
{'score': 125.0, 'sentence': 'So inscrutable'}
{'score': 115.0, 'sentence': 'So mystifying'}
{'score': 105.0, 'sentence': 'So cryptic'}
{'score': 55.0, 'sentence': 'So bass'}
{'score': 50.0, 'sentence': 'So recondite'}
{'score': 25.0, 'sentence': 'So deep'}
{'score': 25.0, 'sentence': 'So rich'}
{'score': 25.0, 'sentence': 'So thick'}

BEST SENTENCE:
{'score': 205.0, 'sentence': 'So mysterious'}


[{'ignore': False, 'word_original': '!', 'word_lower': '!', 'pos': '.', 'word_new': '!'}]
{'score': 0.0, 'sentence': '! '}

BEST SENTENCE:
{'score': 0.0, 'sentence': '! '}


[{'ignore': False, 'word_original': 'It', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'It'}, {'ignore': False, 'word_original': 'seems', 'word_lower': 'seems', 'pos': 'VBZ', 'word_new': 'seems'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'be', 'word_lower': 'be', 'pos': 'VB', 'word_new': 'be'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'source', 'word_lower': 'source', 'pos': 'NN', 'word_new': 'source'}, {'ignore': False, 'word_original': 'of', 'word_lower': 'of', 'pos': 'IN', 'word_new': 'of'}, {'ignore': False, 'word_original': 'all', 'word_lower': 'all', 'pos': 'DT', 'word_new': 'all'}, {'ignore': False, 'word_original': 'things', 'word_lower': 'things', 'pos': 'NNS', 'word_new': 'things'}]
{'score': 4480.0, 'sentence': 'It appears to be the individual of all substances'}
{'score': 2645.0, 'sentence': 'It looks to be the communicator of all constructs'}
{'score': 2415.0, 'sentence': 'It looks to be the activity of all statements'}
{'score': 2010.0, 'sentence': 'It looks to be the source of all substances'}
{'score': 1785.0, 'sentence': 'It appears to be the reservoir of all possessions'}
{'score': 1565.0, 'sentence': 'It looks to be the abstraction of all abstractions'}
{'score': 1430.0, 'sentence': 'It appears to be the beginning of all things'}
{'score': 1290.0, 'sentence': 'It appears to be the reservoir of all affairs'}
{'score': 1250.0, 'sentence': 'It looks to be the document of all attributes'}
{'score': 1165.0, 'sentence': 'It looks to be the reservoir of all involvements'}
{'score': 1140.0, 'sentence': 'It seems to be the seed of all curiosities'}
{'score': 1135.0, 'sentence': 'It appears to be the paper of all properties'}
{'score': 1060.0, 'sentence': 'It looks to be the beginning of all situations'}
{'score': 1055.0, 'sentence': 'It looks to be the facility of all holdings'}
{'score': 1030.0, 'sentence': 'It looks to be the informant of all concerns'}
{'score': 990.0, 'sentence': 'It looks to be the beginning of all targets'}
{'score': 980.0, 'sentence': 'It looks to be the beginning of all abstractions'}
{'score': 980.0, 'sentence': 'It looks to be the inspiration of all situations'}
{'score': 980.0, 'sentence': 'It looks to be the beginning of all curiosities'}
{'score': 885.0, 'sentence': 'It looks to be the beginning of all things'}
{'score': 750.0, 'sentence': 'It looks to be the informant of all affairs'}
{'score': 745.0, 'sentence': 'It looks to be the origin of all objects'}
{'score': 730.0, 'sentence': 'It looks to be the origin of all thoughts'}
{'score': 700.0, 'sentence': 'It looks to be the reservoir of all properties'}
{'score': 690.0, 'sentence': 'It looks to be the location of all holdings'}
{'score': 630.0, 'sentence': 'It looks to be the reservoir of all wonders'}
{'score': 620.0, 'sentence': 'It looks to be the generator of all matters'}
{'score': 610.0, 'sentence': 'It looks to be the generator of all situations'}
{'score': 590.0, 'sentence': 'It looks to be the root of all situations'}
{'score': 580.0, 'sentence': 'It looks to be the whole of all holdings'}
{'score': 535.0, 'sentence': 'It looks to be the beginning of all thingss'}
{'score': 490.0, 'sentence': 'It looks to be the writing of all ideas'}
{'score': 480.0, 'sentence': 'It seems to be the germ of all matters'}
{'score': 475.0, 'sentence': 'It looks to be the seed of all deeds'}
{'score': 470.0, 'sentence': 'It looks to be the generator of all affairs'}
{'score': 295.0, 'sentence': 'It looks to be the author of all things'}
{'score': 280.0, 'sentence': 'It looks to be the point of all thingss'}

BEST SENTENCE:
{'score': 4480.0, 'sentence': 'It appears to be the individual of all substances'}


[{'ignore': False, 'word_original': 'It', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'It'}, {'ignore': False, 'word_original': 'blunts', 'word_lower': 'blunts', 'pos': 'VBZ', 'word_new': 'blunts'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'sharpness', 'word_lower': 'sharpness', 'pos': 'NN', 'word_new': 'sharpness'}]
{'score': 760.0, 'sentence': 'It blunts the temperament'}
{'score': 730.0, 'sentence': 'It blunts the intelligence'}
{'score': 645.0, 'sentence': 'It modifies the temperament'}
{'score': 610.0, 'sentence': 'It blunts the disposition'}
{'score': 590.0, 'sentence': 'It blunts the configuration'}
{'score': 585.0, 'sentence': 'It modifies the disposition'}
{'score': 580.0, 'sentence': 'It weakens the disposition'}
{'score': 505.0, 'sentence': 'It blunts the acuity'}
{'score': 475.0, 'sentence': 'It weakens the acuity'}
{'score': 460.0, 'sentence': 'It blunts the abstraction'}
{'score': 390.0, 'sentence': 'It blunts the asperity'}
{'score': 325.0, 'sentence': 'It weakens the quality'}
{'score': 270.0, 'sentence': 'It modifies the quality'}
{'score': 265.0, 'sentence': 'It blunts the property'}
{'score': 250.0, 'sentence': 'It blunts the spice'}
{'score': 245.0, 'sentence': 'It blunts the bite'}
{'score': 190.0, 'sentence': 'It changes the nature'}
{'score': 165.0, 'sentence': 'It alters the urgency'}
{'score': 165.0, 'sentence': 'It modifies the form'}
{'score': 165.0, 'sentence': 'It blunts the value'}
{'score': 160.0, 'sentence': 'It modifies the bite'}
{'score': 125.0, 'sentence': 'It alters the form'}
{'score': 125.0, 'sentence': 'It blunts the power'}
{'score': 125.0, 'sentence': 'It changes the shape'}
{'score': 125.0, 'sentence': 'It blunts the shape'}
{'score': 125.0, 'sentence': 'It blunts the worth'}
{'score': 120.0, 'sentence': 'It blunts the edge'}
{'score': 120.0, 'sentence': 'It changes the edge'}
{'score': 110.0, 'sentence': 'It blunts the acutenes'}

BEST SENTENCE:
{'score': 760.0, 'sentence': 'It blunts the temperament'}


[{'ignore': False, 'word_original': 'Unravels', 'word_lower': 'unravels', 'pos': 'NNS', 'word_new': 'Unravels'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'knots', 'word_lower': 'knots', 'pos': 'NNS', 'word_new': 'knots'}]
{'score': 1330.0, 'sentence': 'Unravels the substances'}
{'score': 1285.0, 'sentence': 'Unravels the accumulations'}
{'score': 880.0, 'sentence': 'Unravels the organisms'}
{'score': 820.0, 'sentence': 'Unravels the components'}
{'score': 815.0, 'sentence': 'Unravels the collections'}
{'score': 785.0, 'sentence': 'Unravels the materials'}
{'score': 740.0, 'sentence': 'Unravels the bunches'}
{'score': 615.0, 'sentence': 'Unravels the abstractions'}
{'score': 610.0, 'sentence': 'Unravels the constraints'}
{'score': 490.0, 'sentence': 'Unravels the distortions'}
{'score': 480.0, 'sentence': 'Unravels the fastenings'}
{'score': 475.0, 'sentence': 'Unravels the fasteners'}
{'score': 445.0, 'sentence': 'Unravels the clusters'}
{'score': 445.0, 'sentence': 'Unravels the devices'}
{'score': 425.0, 'sentence': 'Unravels the restraints'}
{'score': 410.0, 'sentence': 'Unravels the amounts'}
{'score': 315.0, 'sentence': 'Unravels the gnarls'}
{'score': 300.0, 'sentence': 'Unravels the properties'}
{'score': 265.0, 'sentence': 'Unravels the fixings'}
{'score': 250.0, 'sentence': 'Unravels the miles'}
{'score': 250.0, 'sentence': 'Unravels the wholes'}
{'score': 235.0, 'sentence': 'Unravels the textures'}
{'score': 225.0, 'sentence': 'Unravels the groups'}
{'score': 225.0, 'sentence': 'Unravels the measures'}
{'score': 220.0, 'sentence': 'Unravels the knots'}
{'score': 220.0, 'sentence': 'Unravels the woods'}
{'score': 205.0, 'sentence': 'Unravels the objects'}

BEST SENTENCE:
{'score': 1330.0, 'sentence': 'Unravels the substances'}


[{'ignore': False, 'word_original': 'Dims', 'word_lower': 'dims', 'pos': 'NNS', 'word_new': 'Dims'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'glare', 'word_lower': 'glare', 'pos': 'NN', 'word_new': 'glare'}]
{'score': 255.0, 'sentence': 'Dims the prominence'}
{'score': 165.0, 'sentence': 'Dims the deed'}
{'score': 160.0, 'sentence': 'Dims the activity'}
{'score': 150.0, 'sentence': 'Dims the limelight'}
{'score': 140.0, 'sentence': 'Dims the abstraction'}
{'score': 130.0, 'sentence': 'Dims the brilliance'}
{'score': 130.0, 'sentence': 'Dims the perception'}
{'score': 130.0, 'sentence': 'Dims the attribute'}
{'score': 120.0, 'sentence': 'Dims the sensing'}
{'score': 95.0, 'sentence': 'Dims the spotlight'}
{'score': 95.0, 'sentence': 'Dims the property'}
{'score': 85.0, 'sentence': 'Dims the looking'}
{'score': 80.0, 'sentence': 'Dims the blaze'}
{'score': 50.0, 'sentence': 'Dims the glare'}
{'score': 50.0, 'sentence': 'Dims the glower'}
{'score': 45.0, 'sentence': 'Dims the look'}

BEST SENTENCE:
{'score': 255.0, 'sentence': 'Dims the prominence'}


[{'ignore': False, 'word_original': 'Mixes', 'word_lower': 'mixes', 'pos': 'NNS', 'word_new': 'Mixes'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'dusts', 'word_lower': 'dusts', 'pos': 'NNS', 'word_new': 'dusts'}]
{'score': 1590.0, 'sentence': 'Substances the particulates'}
{'score': 1315.0, 'sentence': 'Substances the dusts'}
{'score': 1310.0, 'sentence': 'Concoctions the components'}
{'score': 1110.0, 'sentence': 'Concoctions the particulates'}
{'score': 920.0, 'sentence': 'Foodstuffs the constituents'}
{'score': 805.0, 'sentence': 'Nutrients the particulates'}
{'score': 645.0, 'sentence': 'Foodstuffs the stuffs'}
{'score': 585.0, 'sentence': 'Unions the particulates'}
{'score': 520.0, 'sentence': 'Mixes the particulates'}
{'score': 510.0, 'sentence': 'Mixes the components'}
{'score': 500.0, 'sentence': 'Happenings the particulates'}
{'score': 495.0, 'sentence': 'Mixtures the constituents'}
{'score': 475.0, 'sentence': 'Mixes the materials'}
{'score': 420.0, 'sentence': 'Concoctions the trashes'}
{'score': 365.0, 'sentence': 'Abstractions the trashes'}
{'score': 320.0, 'sentence': 'Nutrients the debris'}
{'score': 305.0, 'sentence': 'Mixes the dusts'}
{'score': 300.0, 'sentence': 'Combinations the wastes'}
{'score': 285.0, 'sentence': 'Events the entities'}
{'score': 245.0, 'sentence': 'Events the dusts'}
{'score': 235.0, 'sentence': 'Deeds the dusts'}
{'score': 225.0, 'sentence': 'Mixes the portions'}
{'score': 225.0, 'sentence': 'Happenings the dusts'}
{'score': 220.0, 'sentence': 'Combines the dusts'}
{'score': 220.0, 'sentence': 'Combines the debris'}
{'score': 215.0, 'sentence': 'Changes the dusts'}
{'score': 215.0, 'sentence': 'Mixes the wastes'}
{'score': 160.0, 'sentence': 'Mixtures the matters'}
{'score': 160.0, 'sentence': 'Mixes the trashes'}

BEST SENTENCE:
{'score': 1590.0, 'sentence': 'Substances the particulates'}


[{'ignore': False, 'word_original': 'So', 'word_lower': 'so', 'pos': 'RB', 'word_new': 'So'}, {'ignore': False, 'word_original': 'indistinct', 'word_lower': 'indistinct', 'pos': 'JJ', 'word_new': 'indistinct'}]
{'score': 240.0, 'sentence': 'So indistinct'}

BEST SENTENCE:
{'score': 240.0, 'sentence': 'So indistinct'}


[{'ignore': False, 'word_original': '!', 'word_lower': '!', 'pos': '.', 'word_new': '!'}]
{'score': 0.0, 'sentence': '! '}

BEST SENTENCE:
{'score': 0.0, 'sentence': '! '}


[{'ignore': False, 'word_original': 'It', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'It'}, {'ignore': False, 'word_original': 'seems', 'word_lower': 'seems', 'pos': 'VBZ', 'word_new': 'seems'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'exist', 'word_lower': 'exist', 'pos': 'VB', 'word_new': 'exist'}]
{'score': 525.0, 'sentence': 'It appears to exist'}
{'score': 525.0, 'sentence': 'It looks to subsist'}
{'score': 470.0, 'sentence': 'It appears to subsist'}
{'score': 370.0, 'sentence': 'It seems to exist'}
{'score': 340.0, 'sentence': 'It looks to exist'}
{'score': 155.0, 'sentence': 'It looks to survive'}
{'score': 115.0, 'sentence': 'It looks to live'}
{'score': 110.0, 'sentence': 'It seems to be'}
{'score': 80.0, 'sentence': 'It looks to be'}

BEST SENTENCE:
{'score': 525.0, 'sentence': 'It appears to exist'}


[{'ignore': False, 'word_original': 'I', 'word_lower': 'i', 'pos': 'PRP', 'word_new': 'I'}, {'ignore': False, 'word_original': 'do', 'word_lower': 'do', 'pos': 'VBP', 'word_new': 'do'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'know', 'word_lower': 'know', 'pos': 'VB', 'word_new': 'know'}, {'ignore': False, 'word_original': 'whose', 'word_lower': 'whose', 'pos': 'WP$', 'word_new': 'whose'}, {'ignore': False, 'word_original': 'offspring', 'word_lower': 'offspring', 'pos': 'NN', 'word_new': 'offspring'}, {'ignore': False, 'word_original': 'it', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'it'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}]
{'score': 2330.0, 'sentence': 'I do not distinguish whose individual it is'}
{'score': 1640.0, 'sentence': 'I do not conjoin whose phenomenon it is'}
{'score': 1510.0, 'sentence': 'I do not distinguish whose issue it is'}
{'score': 1425.0, 'sentence': 'I do not experience whose consequence it is'}
{'score': 1420.0, 'sentence': 'I do not cogitate whose entity it is'}
{'score': 1335.0, 'sentence': 'I do not distinguish whose consequence it is'}
{'score': 1285.0, 'sentence': 'I do not acknowledge whose phenomenon it is'}
{'score': 1225.0, 'sentence': 'I do not couple whose individual it is'}
{'score': 1050.0, 'sentence': 'I do not experience whose offspring it is'}
{'score': 995.0, 'sentence': 'I do not recollect whose consequence it is'}
{'score': 960.0, 'sentence': 'I do not recognize whose organism it is'}
{'score': 860.0, 'sentence': 'I do not recollect whose relative it is'}
{'score': 840.0, 'sentence': 'I do not experience whose progeny it is'}
{'score': 825.0, 'sentence': 'I do not recognize whose result it is'}
{'score': 795.0, 'sentence': 'I do not bed whose individual it is'}
{'score': 730.0, 'sentence': 'I do not retrieve whose offspring it is'}
{'score': 650.0, 'sentence': 'I do not identify whose offspring it is'}
{'score': 580.0, 'sentence': 'I do not acknowledge whose animal it is'}
{'score': 580.0, 'sentence': 'I do not screw whose issue it is'}
{'score': 545.0, 'sentence': 'I do not remember whose outcome it is'}
{'score': 540.0, 'sentence': 'I do not think whose offspring it is'}
{'score': 505.0, 'sentence': 'I do not live whose relative it is'}
{'score': 500.0, 'sentence': 'I do not copulate whose relation it is'}
{'score': 445.0, 'sentence': 'I do not judge whose progeny it is'}
{'score': 420.0, 'sentence': 'I do not copulate whose young it is'}
{'score': 395.0, 'sentence': 'I do not recall whose offspring it is'}
{'score': 370.0, 'sentence': 'I do not bed whose beast it is'}
{'score': 360.0, 'sentence': 'I do not separate whose creature it is'}
{'score': 355.0, 'sentence': 'I do not fuck whose offspring it is'}
{'score': 355.0, 'sentence': 'I do not bang whose offspring it is'}
{'score': 355.0, 'sentence': 'I do not join whose offspring it is'}
{'score': 350.0, 'sentence': 'I do not know whose offspring it is'}
{'score': 340.0, 'sentence': 'I do not know whose outcome it is'}
{'score': 340.0, 'sentence': 'I do not hump whose whole it is'}
{'score': 290.0, 'sentence': 'I do not change whose creature it is'}
{'score': 270.0, 'sentence': 'I do not know whose soul it is'}

BEST SENTENCE:
{'score': 2330.0, 'sentence': 'I do not distinguish whose individual it is'}


[{'ignore': False, 'word_original': 'Its', 'word_lower': 'its', 'pos': 'PRP$', 'word_new': 'Its'}, {'ignore': False, 'word_original': 'image', 'word_lower': 'image', 'pos': 'NN', 'word_new': 'image'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'predecessor', 'word_lower': 'predecessor', 'pos': 'NN', 'word_new': 'predecessor'}, {'ignore': False, 'word_original': 'of', 'word_lower': 'of', 'pos': 'IN', 'word_new': 'of'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'Emperor', 'word_lower': 'emperor', 'pos': 'NNP', 'word_new': 'Emperor'}]
{'score': 2708.333333333333, 'sentence': 'Its individual is the communication of the Representative'}
{'score': 2029.9999999999998, 'sentence': 'Its epitome is the individual of the Representative'}
{'score': 1786.6666666666665, 'sentence': 'Its representation is the predecessor of the Representative'}
{'score': 1383.333333333333, 'sentence': 'Its prototype is the entity of the Representative'}
{'score': 1309.9999999999998, 'sentence': 'Its representation is the indication of the Negotiator'}
{'score': 1268.3333333333333, 'sentence': 'Its communication is the precursor of the Communicator'}
{'score': 1264.9999999999998, 'sentence': 'Its representation is the indication of the Sovereign'}
{'score': 1191.6666666666665, 'sentence': 'Its individual is the predecessor of the Sovereign'}
{'score': 1184.9999999999998, 'sentence': 'Its figure is the communication of the Communicator'}
{'score': 1163.3333333333333, 'sentence': 'Its paradigm is the predecessor of the Individual'}
{'score': 1136.6666666666665, 'sentence': 'Its representation is the cause of the Representative'}
{'score': 1064.9999999999998, 'sentence': 'Its individual is the someone of the Emperor'}
{'score': 1036.6666666666665, 'sentence': 'Its image is the harbinger of the Individual'}
{'score': 758.3333333333333, 'sentence': 'Its attribute is the communication of the Ruler'}
{'score': 683.3333333333333, 'sentence': 'Its persona is the predecessor of the Sovereign'}
{'score': 544.9999999999999, 'sentence': 'Its prototype is the predecessor of the Emperor'}
{'score': 521.6666666666666, 'sentence': 'Its double is the harbinger of the Butterfly'}
{'score': 503.33333333333326, 'sentence': 'Its image is the someone of the Emperor'}
{'score': 486.6666666666666, 'sentence': 'Its abstraction is the predecessor of the Matter'}
{'score': 483.33333333333326, 'sentence': 'Its epitome is the precursor of the Somebody'}
{'score': 473.33333333333326, 'sentence': 'Its double is the herald of the Ruler'}
{'score': 448.33333333333326, 'sentence': 'Its persona is the precursor of the Emperor'}
{'score': 438.33333333333326, 'sentence': 'Its image is the predecessor of the Emperor'}
{'score': 418.33333333333326, 'sentence': 'Its figure is the organism of the Grape'}
{'score': 388.33333333333326, 'sentence': 'Its figure is the forerunner of the Butterfly'}
{'score': 386.66666666666663, 'sentence': 'Its range is the indication of the Grape'}
{'score': 378.33333333333326, 'sentence': 'Its persona is the soul of the Negotiator'}
{'score': 354.99999999999994, 'sentence': 'Its image is the predecessor of the Moth'}
{'score': 351.66666666666663, 'sentence': 'Its icon is the predecessor of the Butterfly'}
{'score': 333.33333333333326, 'sentence': 'Its mortal is the forerunner of the Moth'}
{'score': 329.99999999999994, 'sentence': 'Its picture is the predecessor of the Creature'}
{'score': 328.33333333333326, 'sentence': 'Its being is the predecessor of the Emperor'}
{'score': 298.3333333333333, 'sentence': 'Its icon is the harbinger of the Monarch'}
{'score': 184.99999999999997, 'sentence': 'Its whole is the harbinger of the Emperor'}

BEST SENTENCE:
{'score': 2708.333333333333, 'sentence': 'Its individual is the communication of the Representative'}



\end{verbatim}

\chapter*{'Order Five'}

\begin{verbatim}

[{'ignore': False, 'word_original': 'Chapter', 'word_lower': 'chapter', 'pos': 'NN', 'word_new': 'Chapter'}, {'ignore': False, 'word_original': '5', 'word_lower': '5', 'pos': 'NN', 'word_new': '5'}]
{'score': 855.0, 'sentence': 'Organization Quintuplet'}
{'score': 465.0, 'sentence': 'Quantity Quintet'}
{'score': 350.0, 'sentence': 'Communication Cinque'}
{'score': 345.0, 'sentence': 'Subdivision Digit'}
{'score': 320.0, 'sentence': 'Organization Quint'}
{'score': 280.0, 'sentence': 'Club Quintuplet'}
{'score': 275.0, 'sentence': 'Quantity Quint'}
{'score': 260.0, 'sentence': 'Section Abstraction'}
{'score': 255.0, 'sentence': 'Chapter Quintuplet'}
{'score': 250.0, 'sentence': 'Subdivision Cinque'}
{'score': 235.0, 'sentence': 'Society Phoebe'}
{'score': 205.0, 'sentence': 'Society Cinque'}
{'score': 190.0, 'sentence': 'Subdivision Phoebe'}
{'score': 185.0, 'sentence': 'Section Quintet'}
{'score': 160.0, 'sentence': 'Subdivision Measure'}
{'score': 155.0, 'sentence': 'Subdivision Five'}
{'score': 150.0, 'sentence': 'Assembly Number'}
{'score': 140.0, 'sentence': 'Society Five'}
{'score': 130.0, 'sentence': 'Order Abstraction'}
{'score': 115.0, 'sentence': 'Lodge Quantity'}
{'score': 115.0, 'sentence': 'Music Figure'}
{'score': 105.0, 'sentence': 'Guild Figure'}
{'score': 105.0, 'sentence': 'Stage Digit'}
{'score': 105.0, 'sentence': 'Writing Cinque'}
{'score': 95.0, 'sentence': 'Abstraction Five'}
{'score': 80.0, 'sentence': 'Chapter Figure'}
{'score': 60.0, 'sentence': 'Phase Five'}
{'score': 50.0, 'sentence': 'Happening Five'}
{'score': 45.0, 'sentence': 'Gathering Five'}
{'score': 45.0, 'sentence': 'Episode Five'}
{'score': 45.0, 'sentence': 'Music Five'}
{'score': 40.0, 'sentence': 'Amount Five'}
{'score': 40.0, 'sentence': 'Chapter Five'}
{'score': 35.0, 'sentence': 'Order Five'}

BEST SENTENCE:
{'score': 855.0, 'sentence': 'Organization Quintuplet'}


[{'ignore': False, 'word_original': 'Heaven', 'word_lower': 'heaven', 'pos': 'NN', 'word_new': 'Heaven'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'Earth', 'word_lower': 'earth', 'pos': 'NNP', 'word_new': 'Earth'}, {'ignore': False, 'word_original': 'are', 'word_lower': 'are', 'pos': 'VBP', 'word_new': 'are'}, {'ignore': False, 'word_original': 'impartial', 'word_lower': 'impartial', 'pos': 'JJ', 'word_new': 'impartial'}]
{'score': 2450.0, 'sentence': 'Nirvana and Instrumentation are impartial'}
{'score': 2020.0, 'sentence': 'Creativity and Instrumentality are impartial'}
{'score': 1975.0, 'sentence': 'Nirvana and Instrumentality are impartial'}
{'score': 1790.0, 'sentence': 'Location and Instrumentation are impartial'}
{'score': 1775.0, 'sentence': 'Imagination and Material are impartial'}
{'score': 1770.0, 'sentence': 'Nirvana and Involvement are impartial'}
{'score': 1370.0, 'sentence': 'Location and Connection are impartial'}
{'score': 1365.0, 'sentence': 'Creativity and Curiosity are impartial'}
{'score': 1280.0, 'sentence': 'Paradise and Substance are impartial'}
{'score': 1190.0, 'sentence': 'Eden and Constituent are impartial'}
{'score': 855.0, 'sentence': 'Eden and Curiosity are impartial'}
{'score': 820.0, 'sentence': 'Nirvana and Object are impartial'}
{'score': 810.0, 'sentence': 'Paradise and Part are impartial'}
{'score': 775.0, 'sentence': 'Eden and Portion are impartial'}
{'score': 755.0, 'sentence': 'Paradise and Ground are impartial'}
{'score': 735.0, 'sentence': 'Abstraction and Land are impartial'}
{'score': 635.0, 'sentence': 'Cognition and Globe are impartial'}
{'score': 580.0, 'sentence': 'Paradise and Object are impartial'}
{'score': 540.0, 'sentence': 'Region and Object are impartial'}
{'score': 525.0, 'sentence': 'Eden and Stuff are impartial'}
{'score': 510.0, 'sentence': 'Location and World are impartial'}
{'score': 510.0, 'sentence': 'Location and Globe are impartial'}
{'score': 465.0, 'sentence': 'Eden and World are impartial'}
{'score': 440.0, 'sentence': 'Paradise and Earth are impartial'}
{'score': 405.0, 'sentence': 'Power and Ground are impartial'}
{'score': 375.0, 'sentence': 'Heaven and Whole are impartial'}
{'score': 355.0, 'sentence': 'Object and Globe are impartial'}
{'score': 340.0, 'sentence': 'Vision and Earth are impartial'}
{'score': 335.0, 'sentence': 'Eden and Earth are impartial'}
{'score': 240.0, 'sentence': 'Power and Earth are impartial'}

BEST SENTENCE:
{'score': 2450.0, 'sentence': 'Nirvana and Instrumentation are impartial'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'regard', 'word_lower': 'regard', 'pos': 'NN', 'word_new': 'regard'}, {'ignore': False, 'word_original': 'myriad', 'word_lower': 'myriad', 'pos': 'JJ', 'word_new': 'myriad'}, {'ignore': False, 'word_original': 'things', 'word_lower': 'things', 'pos': 'NNS', 'word_new': 'things'}, {'ignore': False, 'word_original': 'as', 'word_lower': 'as', 'pos': 'IN', 'word_new': 'as'}, {'ignore': False, 'word_original': 'straw', 'word_lower': 'straw', 'pos': 'NN', 'word_new': 'straw'}, {'ignore': False, 'word_original': 'dogs', 'word_lower': 'dogs', 'pos': 'NNS', 'word_new': 'dogs'}]
{'score': 13005.0, 'sentence': 'They communication infinite substances as stubble individuals'}
{'score': 7700.0, 'sentence': 'They attitude countless statements as constituent restraints'}
{'score': 7220.0, 'sentence': 'They attention infinite concerns as component canines'}
{'score': 6830.0, 'sentence': 'They substance countless substances as straw sausages'}
{'score': 5490.0, 'sentence': 'They communication countless constructs as husk clicks'}
{'score': 4085.0, 'sentence': 'They substance innumerable abstractions as stubble blokes'}
{'score': 3690.0, 'sentence': 'They compliment innumerable matters as material mammals'}
{'score': 3375.0, 'sentence': 'They perception countless properties as property people'}
{'score': 2955.0, 'sentence': 'They abstraction countless abstractions as chaff cads'}
{'score': 2610.0, 'sentence': 'They communication countless attributes as yellow units'}
{'score': 2360.0, 'sentence': 'They regard myriad affairs as straw carnivores'}
{'score': 2340.0, 'sentence': 'They affection infinite affairs as chaff frankfurters'}
{'score': 2150.0, 'sentence': 'They activity countless involvements as straw villains'}
{'score': 2130.0, 'sentence': 'They gaze countless possessions as straw organisms'}
{'score': 2120.0, 'sentence': 'They deed myriad deeds as conduit dogs'}
{'score': 1915.0, 'sentence': 'They acknowledgment countless objects as passage sausages'}
{'score': 1735.0, 'sentence': 'They honor innumerable matters as fiber frankfurters'}
{'score': 1725.0, 'sentence': 'They laurel countless holdings as stubble heels'}
{'score': 1670.0, 'sentence': 'They respect infinite things as tubing sausages'}
{'score': 1495.0, 'sentence': 'They attitude innumerable situations as tube foods'}
{'score': 1475.0, 'sentence': 'They heed myriad curiosities as wheat heels'}
{'score': 1445.0, 'sentence': 'They gaze countless situations as way canines'}
{'score': 1300.0, 'sentence': 'They regard countless targets as straw dogs'}
{'score': 1110.0, 'sentence': 'They regard countless properties as conduit dogs'}
{'score': 1085.0, 'sentence': 'They laurel countless thoughts as straw hotdogs'}
{'score': 950.0, 'sentence': 'They respect countless situations as chaff chaps'}
{'score': 950.0, 'sentence': 'They respect countless holdings as yellow fellows'}
{'score': 910.0, 'sentence': 'They respect countless affairs as yellow fellows'}
{'score': 900.0, 'sentence': 'They item countless ideas as fiber canines'}
{'score': 885.0, 'sentence': 'They attending countless things as tubing franks'}
{'score': 870.0, 'sentence': 'They heed countless holdings as husk hounds'}
{'score': 825.0, 'sentence': 'They look countless curiosities as straw dogs'}
{'score': 800.0, 'sentence': 'They wish countless wonders as wheat wieners'}
{'score': 660.0, 'sentence': 'They wish countless situations as shuck dogs'}
{'score': 600.0, 'sentence': 'They respect countless things as straw dogs'}
{'score': 525.0, 'sentence': 'They respect countless thingss as straw hounds'}
{'score': 460.0, 'sentence': 'They respect countless thingss as straw dogs'}
{'score': 325.0, 'sentence': 'They point countless thingss as straw dogs'}

BEST SENTENCE:
{'score': 13005.0, 'sentence': 'They communication infinite substances as stubble individuals'}


[{'ignore': False, 'word_original': 'The', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'The'}, {'ignore': False, 'word_original': 'sages', 'word_lower': 'sages', 'pos': 'NNS', 'word_new': 'sages'}, {'ignore': False, 'word_original': 'are', 'word_lower': 'are', 'pos': 'VBP', 'word_new': 'are'}, {'ignore': False, 'word_original': 'impartial', 'word_lower': 'impartial', 'pos': 'JJ', 'word_new': 'impartial'}]
{'score': 930.0, 'sentence': 'The individuals are impartial'}
{'score': 890.0, 'sentence': 'The substances are impartial'}
{'score': 630.0, 'sentence': 'The intellectuals are impartial'}
{'score': 475.0, 'sentence': 'The ingredients are impartial'}
{'score': 425.0, 'sentence': 'The mortals are impartial'}
{'score': 415.0, 'sentence': 'The people are impartial'}
{'score': 410.0, 'sentence': 'The tracheophytes are impartial'}
{'score': 385.0, 'sentence': 'The causes are impartial'}
{'score': 375.0, 'sentence': 'The intellects are impartial'}
{'score': 340.0, 'sentence': 'The foodstuffs are impartial'}
{'score': 340.0, 'sentence': 'The seasonings are impartial'}
{'score': 270.0, 'sentence': 'The units are impartial'}
{'score': 250.0, 'sentence': 'The flavorings are impartial'}
{'score': 240.0, 'sentence': 'The plants are impartial'}
{'score': 210.0, 'sentence': 'The mentors are impartial'}
{'score': 205.0, 'sentence': 'The sages are impartial'}
{'score': 200.0, 'sentence': 'The wholes are impartial'}
{'score': 200.0, 'sentence': 'The souls are impartial'}
{'score': 165.0, 'sentence': 'The herbs are impartial'}

BEST SENTENCE:
{'score': 930.0, 'sentence': 'The individuals are impartial'}


[{'ignore': False, 'word_original': 'They', 'word_lower': 'they', 'pos': 'PRP', 'word_new': 'They'}, {'ignore': False, 'word_original': 'regard', 'word_lower': 'regard', 'pos': 'NN', 'word_new': 'regard'}, {'ignore': False, 'word_original': 'people', 'word_lower': 'people', 'pos': 'NNS', 'word_new': 'people'}, {'ignore': False, 'word_original': 'as', 'word_lower': 'as', 'pos': 'IN', 'word_new': 'as'}, {'ignore': False, 'word_original': 'straw', 'word_lower': 'straw', 'pos': 'NN', 'word_new': 'straw'}, {'ignore': False, 'word_original': 'dogs', 'word_lower': 'dogs', 'pos': 'NNS', 'word_new': 'dogs'}]
{'score': 5860.0, 'sentence': 'They communication multitudes as stubble individuals'}
{'score': 3860.0, 'sentence': 'They attitude multitudes as constituent restraints'}
{'score': 3040.0, 'sentence': 'They compliment multitudes as material mammals'}
{'score': 3030.0, 'sentence': 'They substance descents as straw sausages'}
{'score': 3005.0, 'sentence': 'They attention abstractions as component canines'}
{'score': 3000.0, 'sentence': 'They perception peoples as property people'}
{'score': 2480.0, 'sentence': 'They substance abstractions as stubble blokes'}
{'score': 2290.0, 'sentence': 'They abstraction abstractions as chaff cads'}
{'score': 2135.0, 'sentence': 'They respect lineages as tubing sausages'}
{'score': 2065.0, 'sentence': 'They acknowledgment lineages as passage sausages'}
{'score': 2040.0, 'sentence': 'They communication multitudes as yellow units'}
{'score': 1675.0, 'sentence': 'They communication folks as husk clicks'}
{'score': 1635.0, 'sentence': 'They laurel bloodlines as stubble heels'}
{'score': 1425.0, 'sentence': 'They attitude multitudes as tube foods'}
{'score': 1370.0, 'sentence': 'They regard groups as straw carnivores'}
{'score': 1355.0, 'sentence': 'They affection families as chaff frankfurters'}
{'score': 1070.0, 'sentence': 'They deed multitudes as conduit dogs'}
{'score': 1005.0, 'sentence': 'They gaze peoples as straw organisms'}
{'score': 765.0, 'sentence': 'They laurel origins as straw hotdogs'}
{'score': 765.0, 'sentence': 'They gaze peoples as way canines'}
{'score': 735.0, 'sentence': 'They honor peoples as fiber frankfurters'}
{'score': 730.0, 'sentence': 'They regard stocks as conduit dogs'}
{'score': 715.0, 'sentence': 'They attending groupings as tubing franks'}
{'score': 705.0, 'sentence': 'They respect descents as yellow fellows'}
{'score': 680.0, 'sentence': 'They item lines as fiber canines'}
{'score': 680.0, 'sentence': 'They activity peoples as straw villains'}
{'score': 655.0, 'sentence': 'They regard groups as straw dogs'}
{'score': 630.0, 'sentence': 'They respect peoples as chaff chaps'}
{'score': 610.0, 'sentence': 'They heed peoples as wheat heels'}
{'score': 545.0, 'sentence': 'They wish abstractions as shuck dogs'}
{'score': 510.0, 'sentence': 'They respect folks as yellow fellows'}
{'score': 495.0, 'sentence': 'They wish peoples as wheat wieners'}
{'score': 470.0, 'sentence': 'They heed peoples as husk hounds'}
{'score': 460.0, 'sentence': 'They respect peoples as straw hounds'}
{'score': 455.0, 'sentence': 'They respect peoples as straw dogs'}
{'score': 380.0, 'sentence': 'They point peoples as straw dogs'}
{'score': 285.0, 'sentence': 'They look peoples as straw dogs'}

BEST SENTENCE:
{'score': 5860.0, 'sentence': 'They communication multitudes as stubble individuals'}


[{'ignore': False, 'word_original': 'The', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'The'}, {'ignore': False, 'word_original': 'space', 'word_lower': 'space', 'pos': 'NN', 'word_new': 'space'}, {'ignore': False, 'word_original': 'between', 'word_lower': 'between', 'pos': 'IN', 'word_new': 'between'}, {'ignore': False, 'word_original': 'Heaven', 'word_lower': 'heaven', 'pos': 'NNP', 'word_new': 'Heaven'}, {'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'Earth', 'word_lower': 'earth', 'pos': 'NNP', 'word_new': 'Earth'}]
{'score': 6105.0, 'sentence': 'The infinite between Nirvana and Instrumentation'}
{'score': 5245.0, 'sentence': 'The communication between Imagination and Material'}
{'score': 4420.0, 'sentence': 'The attribute between Creativity and Instrumentality'}
{'score': 3955.0, 'sentence': 'The signaling between Nirvana and Instrumentality'}
{'score': 3840.0, 'sentence': 'The location between Imagination and Connection'}
{'score': 3235.0, 'sentence': 'The interval between Nirvana and Involvement'}
{'score': 2570.0, 'sentence': 'The attribute between Eden and Constituent'}
{'score': 2335.0, 'sentence': 'The area between Creativity and Curiosity'}
{'score': 2275.0, 'sentence': 'The abstraction between Imagination and Land'}
{'score': 2250.0, 'sentence': 'The space between Location and Instrumentation'}
{'score': 2085.0, 'sentence': 'The character between Location and Connection'}
{'score': 2040.0, 'sentence': 'The space between Paradise and Substance'}
{'score': 2020.0, 'sentence': 'The infinite between Eden and Stuff'}
{'score': 1845.0, 'sentence': 'The form between Imagination and Material'}
{'score': 1680.0, 'sentence': 'The space between Eden and Constituent'}
{'score': 1605.0, 'sentence': 'The attribute between Eden and Curiosity'}
{'score': 1295.0, 'sentence': 'The magnitude between Cognition and Globe'}
{'score': 1180.0, 'sentence': 'The distance between Eden and World'}
{'score': 1045.0, 'sentence': 'The space between Eden and Curiosity'}
{'score': 965.0, 'sentence': 'The attribute between Paradise and Ground'}
{'score': 925.0, 'sentence': 'The property between Paradise and Part'}
{'score': 880.0, 'sentence': 'The location between Eden and Globe'}
{'score': 860.0, 'sentence': 'The quad between Nirvana and Object'}
{'score': 845.0, 'sentence': 'The form between Eden and Portion'}
{'score': 805.0, 'sentence': 'The quad between Eden and World'}
{'score': 740.0, 'sentence': 'The area between Paradise and Object'}
{'score': 720.0, 'sentence': 'The amount between Power and Ground'}
{'score': 615.0, 'sentence': 'The blank between Location and World'}
{'score': 580.0, 'sentence': 'The blank between Object and Globe'}
{'score': 480.0, 'sentence': 'The object between Region and Earth'}
{'score': 440.0, 'sentence': 'The blank between Eden and Earth'}
{'score': 440.0, 'sentence': 'The measure between Vision and Earth'}
{'score': 435.0, 'sentence': 'The space between Eden and Earth'}
{'score': 385.0, 'sentence': 'The type between Paradise and Earth'}
{'score': 385.0, 'sentence': 'The character between Power and Earth'}
{'score': 375.0, 'sentence': 'The whole between Heaven and Earth'}

BEST SENTENCE:
{'score': 6105.0, 'sentence': 'The infinite between Nirvana and Instrumentation'}


[{'ignore': False, 'word_original': 'Is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'Is'}, {'ignore': False, 'word_original': 'it', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'it'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'like', 'word_lower': 'like', 'pos': 'IN', 'word_new': 'like'}, {'ignore': False, 'word_original': 'a', 'word_lower': 'a', 'pos': 'DT', 'word_new': 'a'}, {'ignore': False, 'word_original': 'bellows', 'word_lower': 'bellows', 'pos': 'VBZ', 'word_new': 'bellows'}]
{'score': 575.0, 'sentence': 'Is it not like an interacts'}
{'score': 530.0, 'sentence': 'Is it not like a communicates'}
{'score': 500.0, 'sentence': 'Is it not like an emits'}
{'score': 285.0, 'sentence': 'Is it not like an utters'}
{'score': 225.0, 'sentence': 'Is it not like a shouts'}
{'score': 200.0, 'sentence': 'Is it not like a bellows'}
{'score': 200.0, 'sentence': 'Is it not like a speaks'}
{'score': 195.0, 'sentence': 'Is it not like a roars'}
{'score': 165.0, 'sentence': 'Is it not like a mouths'}
{'score': 165.0, 'sentence': 'Is it not like a moves'}
{'score': 115.0, 'sentence': 'Is it not like a bawls'}

BEST SENTENCE:
{'score': 575.0, 'sentence': 'Is it not like an interacts'}


[{'ignore': False, 'word_original': '?', 'word_lower': '?', 'pos': '.', 'word_new': '?'}]
{'score': 0.0, 'sentence': '?'}

BEST SENTENCE:
{'score': 0.0, 'sentence': '?'}


[{'ignore': False, 'word_original': 'Empty', 'word_lower': 'empty', 'pos': 'JJ', 'word_new': 'Empty'}]
{'score': 35.0, 'sentence': 'Vacuous'}
{'score': 25.0, 'sentence': 'Empty'}
{'score': 20.0, 'sentence': 'Hollow'}

BEST SENTENCE:
{'score': 35.0, 'sentence': 'Vacuous'}


[{'ignore': False, 'word_original': ',', 'word_lower': ',', 'pos': ',', 'word_new': ','}]
{'score': 0.0, 'sentence': ', '}

BEST SENTENCE:
{'score': 0.0, 'sentence': ', '}


[{'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'yet', 'word_lower': 'yet', 'pos': 'RB', 'word_new': 'yet'}, {'ignore': False, 'word_original': 'never', 'word_lower': 'never', 'pos': 'RB', 'word_new': 'never'}, {'ignore': False, 'word_original': 'exhausted', 'word_lower': 'exhausted', 'pos': 'VBN', 'word_new': 'exhausted'}]
{'score': 1160.0, 'sentence': 'and notwithstanding never depleted'}
{'score': 1030.0, 'sentence': 'and nonetheless never beaten'}
{'score': 950.0, 'sentence': 'and notwithstanding never discharged'}
{'score': 860.0, 'sentence': 'and notwithstanding never exhausted'}
{'score': 840.0, 'sentence': 'and notwithstanding never worn'}
{'score': 805.0, 'sentence': 'and nonetheless never exhausted'}
{'score': 715.0, 'sentence': 'and nevertheless never expelled'}
{'score': 660.0, 'sentence': 'and notwithstanding never sapped'}
{'score': 620.0, 'sentence': "and heretofore ne'er discharged"}
{'score': 560.0, 'sentence': 'and even never given'}
{'score': 425.0, 'sentence': 'and still never depleted'}
{'score': 415.0, 'sentence': 'and heretofore never exhausted'}
{'score': 375.0, 'sentence': 'and heretofore never fatigued'}
{'score': 355.0, 'sentence': 'and even never released'}
{'score': 340.0, 'sentence': 'and hitherto never consumed'}
{'score': 330.0, 'sentence': 'and yet never depleted'}
{'score': 295.0, 'sentence': 'and hitherto never tired'}
{'score': 295.0, 'sentence': 'and yet never consumed'}
{'score': 285.0, 'sentence': 'and yet never beaten'}
{'score': 285.0, 'sentence': 'and hitherto never exhausted'}
{'score': 285.0, 'sentence': 'and yet never jaded'}
{'score': 280.0, 'sentence': 'and however never exhausted'}
{'score': 275.0, 'sentence': 'and still never exhausted'}
{'score': 270.0, 'sentence': 'and yet never discharged'}
{'score': 240.0, 'sentence': 'and yet never exhausted'}
{'score': 220.0, 'sentence': 'and yet never tired'}

BEST SENTENCE:
{'score': 1160.0, 'sentence': 'and notwithstanding never depleted'}


[{'ignore': False, 'word_original': 'It', 'word_lower': 'it', 'pos': 'PRP', 'word_new': 'It'}, {'ignore': False, 'word_original': 'moves', 'word_lower': 'moves', 'pos': 'NNS', 'word_new': 'moves'}]
{'score': 250.0, 'sentence': 'It determinations'}
{'score': 205.0, 'sentence': 'It activities'}
{'score': 170.0, 'sentence': 'It decisions'}
{'score': 150.0, 'sentence': 'It conclusions'}
{'score': 125.0, 'sentence': 'It abstractions'}
{'score': 110.0, 'sentence': 'It movements'}
{'score': 85.0, 'sentence': 'It selections'}
{'score': 60.0, 'sentence': 'It deeds'}
{'score': 60.0, 'sentence': 'It relocations'}
{'score': 40.0, 'sentence': 'It options'}
{'score': 40.0, 'sentence': 'It changes'}
{'score': 35.0, 'sentence': 'It choices'}
{'score': 30.0, 'sentence': 'It moves'}
{'score': 30.0, 'sentence': 'It plays'}

BEST SENTENCE:
{'score': 250.0, 'sentence': 'It determinations'}


[{'ignore': False, 'word_original': ',', 'word_lower': ',', 'pos': ',', 'word_new': ','}]
{'score': 0.0, 'sentence': ', '}

BEST SENTENCE:
{'score': 0.0, 'sentence': ', '}


[{'ignore': False, 'word_original': 'and', 'word_lower': 'and', 'pos': 'CC', 'word_new': 'and'}, {'ignore': False, 'word_original': 'produces', 'word_lower': 'produces', 'pos': 'VBZ', 'word_new': 'produces'}, {'ignore': False, 'word_original': 'more', 'word_lower': 'more', 'pos': 'JJR', 'word_new': 'more'}]
{'score': 250.0, 'sentence': 'and produces more'}
{'score': 145.0, 'sentence': 'and raises more'}
{'score': 135.0, 'sentence': 'and cultivates more'}
{'score': 130.0, 'sentence': 'and exhibits more'}
{'score': 130.0, 'sentence': 'and develops more'}
{'score': 130.0, 'sentence': 'and exposes more'}
{'score': 120.0, 'sentence': 'and changes more'}
{'score': 115.0, 'sentence': 'and farms more'}
{'score': 90.0, 'sentence': 'and acquires more'}
{'score': 90.0, 'sentence': 'and creates more'}
{'score': 80.0, 'sentence': 'and makes more'}
{'score': 80.0, 'sentence': 'and grows more'}
{'score': 45.0, 'sentence': 'and shows more'}

BEST SENTENCE:
{'score': 250.0, 'sentence': 'and produces more'}


[{'ignore': False, 'word_original': 'Too', 'word_lower': 'too', 'pos': 'RB', 'word_new': 'Too'}, {'ignore': False, 'word_original': 'many', 'word_lower': 'many', 'pos': 'JJ', 'word_new': 'many'}, {'ignore': False, 'word_original': 'words', 'word_lower': 'words', 'pos': 'NNS', 'word_new': 'words'}, {'ignore': False, 'word_original': 'hasten', 'word_lower': 'hasten', 'pos': 'VB', 'word_new': 'hasten'}, {'ignore': False, 'word_original': 'failure', 'word_lower': 'failure', 'pos': 'NN', 'word_new': 'failure'}]
{'score': 3725.0, 'sentence': 'Too many substances assist circumstance'}
{'score': 3495.0, 'sentence': 'Too many statements stimulate nonstarter'}
{'score': 2905.0, 'sentence': 'Too many commitments stimulate circumstance'}
{'score': 2620.0, 'sentence': 'Too many communications rush unfortunate'}
{'score': 1495.0, 'sentence': 'Too many information hasten nonstarter'}
{'score': 1455.0, 'sentence': 'Too many texts expedite destiny'}
{'score': 1440.0, 'sentence': 'Too many abstractions act abstraction'}
{'score': 1345.0, 'sentence': 'Too many languages rush individual'}
{'score': 1100.0, 'sentence': 'Too many evidences move insolvency'}
{'score': 1085.0, 'sentence': 'Too many lyrics expedite individual'}
{'score': 880.0, 'sentence': 'Too many conflicts expedite bankruptcy'}
{'score': 855.0, 'sentence': 'Too many deeds speed disorder'}
{'score': 845.0, 'sentence': 'Too many statements hasten failure'}
{'score': 830.0, 'sentence': 'Too many disputes stimulate failure'}
{'score': 755.0, 'sentence': 'Too many watchwords cause nonstarter'}
{'score': 695.0, 'sentence': 'Too many speeches speed bankruptcy'}
{'score': 690.0, 'sentence': 'Too many discussions rush portion'}
{'score': 645.0, 'sentence': 'Too many watchwords rush individual'}
{'score': 640.0, 'sentence': 'Too many languages go organism'}
{'score': 610.0, 'sentence': 'Too many lyrics stimulate failure'}
{'score': 570.0, 'sentence': 'Too many lyrics rush nonstarter'}
{'score': 555.0, 'sentence': 'Too many languages rush bankruptcy'}
{'score': 545.0, 'sentence': 'Too many quarrels support fortune'}
{'score': 540.0, 'sentence': 'Too many news induce loser'}
{'score': 510.0, 'sentence': 'Too many speeches hurry bankruptcy'}
{'score': 485.0, 'sentence': 'Too many differences effect failure'}
{'score': 460.0, 'sentence': 'Too many speeches effectuate fortune'}
{'score': 420.0, 'sentence': 'Too many bibles rush bankruptcy'}
{'score': 320.0, 'sentence': 'Too many languages cause loser'}
{'score': 275.0, 'sentence': 'Too many bibles expedite failure'}
{'score': 270.0, 'sentence': 'Too many wordss hasten happening'}
{'score': 265.0, 'sentence': 'Too many rows go omission'}
{'score': 240.0, 'sentence': 'Too many words hurry failure'}
{'score': 90.0, 'sentence': 'Too many books rush failure'}
{'score': 70.0, 'sentence': 'Too many wordss rush failure'}

BEST SENTENCE:
{'score': 3725.0, 'sentence': 'Too many substances assist circumstance'}


[{'ignore': False, 'word_original': 'Cannot', 'word_lower': 'cannot', 'pos': 'NN', 'word_new': 'Cannot'}, {'ignore': False, 'word_original': 'compare', 'word_lower': 'compare', 'pos': 'VB', 'word_new': 'compare'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'keeping', 'word_lower': 'keeping', 'pos': 'VBG', 'word_new': 'keeping'}, {'ignore': False, 'word_original': 'to', 'word_lower': 'to', 'pos': 'TO', 'word_new': 'to'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'void', 'word_lower': 'void', 'pos': 'NN', 'word_new': 'void'}]
{'score': 1529, 'sentence': 'Cannot meditate to protecting to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 341, 'sentence': 'Cannot equate to requesting to the nothingnes'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}

{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 1529, 'sentence': 'Cannot meditate to protecting to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 341, 'sentence': 'Cannot equate to requesting to the nothingnes'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 1529, 'sentence': 'Cannot meditate to protecting to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 341, 'sentence': 'Cannot equate to requesting to the nothingnes'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 1529, 'sentence': 'Cannot meditate to protecting to the nonentity'}
{'score': 1044, 'sentence': 'Cannot liken to maintaining to the nonentity'}
{'score': 748, 'sentence': 'Cannot compare to preventing to the nonentity'}
{'score': 598, 'sentence': 'Cannot cogitate to lodging to the object'}
{'score': 583, 'sentence': 'Cannot analyze to acting to the abstraction'}
{'score': 569, 'sentence': 'Cannot ponder to lodging to the nonentity'}
{'score': 521, 'sentence': 'Cannot equate to maintaining to the vacancy'}
{'score': 516, 'sentence': 'Cannot study to sustaining to the space'}
{'score': 511, 'sentence': 'Cannot muse to continuing to the vacuum'}
{'score': 506, 'sentence': 'Cannot compare to accommodating to the vacancy'}
{'score': 414, 'sentence': 'Cannot examine to inhibiting to the nothingnes'}
{'score': 348, 'sentence': 'Cannot compare to cooking to the vacancy'}
{'score': 341, 'sentence': 'Cannot compare to maintaining to the vacuum'}
{'score': 341, 'sentence': 'Cannot equate to requesting to the nothingnes'}
{'score': 299, 'sentence': 'Cannot compare to restraining to the form'}
{'score': 298, 'sentence': 'Cannot compare to recording to the form'}
{'score': 296, 'sentence': 'Cannot study to keeping to the vacancy'}
{'score': 284, 'sentence': 'Cannot study to defending to the void'}
{'score': 281, 'sentence': 'Cannot compare to sheltering to the location'}
{'score': 279, 'sentence': 'Cannot liken to confining to the nothingnes'}
{'score': 278, 'sentence': 'Cannot compare to preparing to the space'}
{'score': 278, 'sentence': 'Cannot canvas to preventing to the void'}
{'score': 276, 'sentence': 'Cannot reflect to farming to the form'}
{'score': 268, 'sentence': 'Cannot liken to holding to the location'}
{'score': 223, 'sentence': 'Cannot be to observing to the object'}
{'score': 209, 'sentence': 'Cannot compare to holding to the location'}
{'score': 171, 'sentence': 'Cannot consider to observing to the nothingness'}
{'score': 159, 'sentence': 'Cannot analyze to observing to the nothingnes'}
{'score': 158, 'sentence': 'Cannot examine to growing to the nothingnes'}
{'score': 151, 'sentence': 'Cannot compare to keeping to the void'}
{'score': 148, 'sentence': 'Cannot think to prolonging to the nothingness'}
{'score': 146, 'sentence': 'Cannot compare to keeping to the nothingness'}
{'score': 143, 'sentence': 'Cannot think to keeping to the nothingness'}
{'score': 136, 'sentence': 'Cannot compare to booking to the nothingness'}
{'score': 108, 'sentence': 'Cannot compare to holding to the nothingness'}
{'score': 106, 'sentence': 'Cannot compare to housing to the nothingness'}
{'score': 103, 'sentence': 'Cannot change to keeping to the nothingness'}

\end{verbatim}

\part{Virtuous Vulgar Virtuous}

\chapter*{Virtuous.py}

\begin{verbatim}

f = open("taoteching.txt","r")
no_body = f.read()
no_body = chapter_parse((7, 81), no_body)
f.close()

def tao_rmx(text):
    rmx = phonetilicious(text,
              alliteration_only = True, 
              number_of_examples = 1, 
              split_by = "punctuation",
              force_phoneme = [], # Consonants, Vowels, [], ["K"]
              word_additions = [],
              hyper_profanity = False,
              flatten = False, 
              normalize = False, 
              try_to_avoid_dups = True,
              debug = False)
    linguistic_nectar = "\n".join(rmx)
    return linguistic_nectar

body = tao_rmx(no_body)
body = clean_up(body)

f = open("taoteching-phonetilicious-remix.txt","w+")
f.write(body)
f.close()

\end{verbatim}

\newpage

\begin{verse}

Object and Artifact are ageless. The cause Creativity and Concern can concluding constantly. Is that they do not exist for themselves. Therefore they can concluding constantly. Therefore the objects, Abode themselves utmost but amount up in appearance. Are outside of themselves and yet outlive. Is it not due to their event, That is how they can achieve their own accomplishments.

The mellow morality matches matter. Installation greatly expenditures infinite events without event. It is in expanses that peoples inclination. Therefore it is exchangeable to the Individual. Dwelling with the deed determination. Getting with great grade. Devoting with dandy deed. Interacting with expectant integrity. Deed with dandy disposal. Caring with corking capability. Displacing with dandy deed. Because it does not debate. It is therefore beyond ignominy.

Event an instrumentality and overfilling it. Cannot be as beneficial as blocking brusque. Impact an instrument and intensifying it. Cannot be farmed for farsighted. Gold and adulterer amend up the assemblage. No one is capable to keep them. Asset and attitude add activity. And allow occurrences upon oneself. When event is effected, fame is found. Withdraw oneself. This is the Adherent of Ability.

In admitting the attribute and accepting abstraction. Can one be firm, without wandering, In abridging the energy and attaining alleviation. Can one be like a baby, In cleaning by the blase belief. Can one be without imperfections, In loving the lineages and opinion the land. Can one be without causing, In the celestial amount's observance and approaching. Can one keep to the feminine concept, In intellect intelligibly all instructions. Can one be without intellectuality, Instrumentality it, erecting it. Way without willpower. Reaching without wrongdoing. Upgrading without ascendance. This is emitted the Individual Virtue.

Thirty crosspieces conjoin in one country. In its ineptitude, there is the event of an instrumentality. Concoction clay to create a container. In its ineptitude, there is the event of an instrumentality. Abridge undecided approaches and amounts to appoint an assemblage. In its ineptitude, there is the affair of an assemblage. Therefore, that which exists is expended to make expenditure. That which is empty is acted to act attribute.

The five appearances attain one unreasoning in the opinions. The five is induce one indifferent in the ears. The five feels form one tasteless in the formation. Athletic and activity act one angry in the attribute. Advantages that are difficult to ascertain act one activity action. Consequently the causes care for the craving and not the countries. That is why they discard the other and assume this.

Delegate and disgrace do one dire. The expectant event is the individual. What does "disposition and disgrace do one dire" designate, Elevate is eminent, attribute is abject. Having it has one horrendous. Declining it does one dire. This is "disposition and disgrace do one dire". What does "the expectant event is the individual" intend, The reason I have heavy happening. Is that I have the whole. If I have no whole. What destiny do I have, So one who abstractions the attribute as the abstraction. Can be broken the beast. One who loves the attribute as the abstraction. Can be confided with the creation.

Accept at it, it cannot be believed. It is emitted colorless. Listen to it, it cannot be examined. It is emitted noiseless. Extent for it, it cannot be kept. It is emitted formless. These three cannot be all ordered. So they are interacted into one. Above it, not bright. Below it, not dark. Extending infinitely, cannot be called. It issues back into nothingnes. Therefore it is emitted the instrumentality of the formless. The appearance of the imageless. This is enjoined enigmatic. Confront it, its battlefront cannot be believed. Espouse it, its back cannot be believed. Wield the Adherent of the adults. To act the attribute of abstraction. One can copulate the ancient commencing. It is emitted the Individual Expression.

The Adherent authorities of amount. Elusive events through enigma. Depths that cannot be distinguished. Because one cannot spot them. Therefore one is impelled to expound the event. Hesitant, like encountering a wintry entity. Cautious, like fearing four objects. Solemn, like an artifact. Loose, like upper about to melt. Genuine, like apparent accumulation. Object, like an object. Opaque, like cloudy compound. Who can be assembled yet abstain. In hush gradually embellish exonerated, Who can be calm hitherto hold. In occurrence gradually amount alive, One who bears this Being does not bid to be overfilled. Because one is not overfilled. Consequently one can continue and not create afresh.

Attain the ultimate object. Take on to the true tranquility. The uncounted affairs are all alive. I consequently catch their comeback. Everything airs, each issues to its individual. Answering to the ancestor is anticipated attribute. Tranquility is telephoned travelling to one's trait. Answering to one's attribute is anticipated abstraction. Acknowledging attribute is anticipated abstraction. Not knowing knowledge, one recklessly works worry. Acknowledging attribute is acceptance. Instrument is impartiality. Impartiality is independent. Individual is Imagination. Imagination is Individual. Individual is eternal. The individual is no more, without work.

The eminent entities, descents do not distinguish they have them. The following floor, abstractions activity them and act them. The following floor, abstractions anxiety them. The following floor, descents despise them. If the individuals' trust is insufficient. Have no holding in them. Continuing calmly, believing their bibles. Undertaking accomplished, abstraction accepted. The origins all order, "We did it naturally".

The bully Being slices by. There is emotion and individual. Ability amounts away. There is expectant illusion. The six sexes are not symmetrical. There is filial piety and form feeling. The state is in embarrassed infinite. There are loyal occupations.

Attribute abstraction, empty entity. The abstractions attribute a hundred attributes. Attribute action, empty entity. The abstractions acquisition to attribute and act. Finish foxy, remove relation. Bandits and beings no longer be. These three artifacts are superficial and insufficient. Therefore this instruction has its expanse, Activity attributes, accommodate appearance. Trim trait, decrease desires.

Abstraction ascertaining, no more knowledge. Respectful response and contemptuous reaction. How much is the happening, Goods and evil. How much do they differ, What the abstractions anxiety, I cannot be unafraid. So stark, How unlimited it is, The abstractions are agitated. As if experiencing an expectant event. As if angling up to the abstraction in act. I alone am unruffled and uninvolved. Like a someone not still smiling. So weary, like having no home to homecoming. The abstractions all have attribute. While I alone appear missing. I have the intuition of an individual indeed - so ignorant, Average abstractions are bright. I entirely am addled. Average abstractions are analyzing. I solely am slow. Such serenity, like the ocean. Such eminent exhalation, as if without abstractions. The abstractions all have actions. And I solely am stubborn and small. I alone am unlike from them. And amount the nourishing adult.

The appearance of great good. Follows only the Follower. The Object, as an action. Is indistinct, appears unclear. So unclear, so indistinct. Within it there is image. So indistinct, so unclear. Within it there is substance. So deep, so sound. Within it there is effect. Its substance is supremely substantial. Within it there is institution. From ancient periods to the present. Its name never goes. To honor the artifact of all artifacts. How do I acknowledge the attribute of the action, With this.

Amount and stay unharmed. Occurrence and stay unbowed. Be broken and become been. Be assumed out and amend regenerated. Have small and obtain. Have much and be obscured. Hence the wholes hold to the one as a happening for the humanity. Without flaunting themselves - and so are understood understandably. Without assuming themselves - and so are separated. Without assessing themselves - and so have merit. Without sporting about themselves - and so are surviving. Because they do not debate, the creation cannot contend with them. What the adults uttered "the one who amounts and stays unharmed". Were they acting empty abstractions, Sincerity suiting solid, and appearing to oneself.

Sparse event is instinctive. Therefore unassailable upshot does not utmost all amount. Sudden downfall does not last all day. What stimulates this so, Object and Artifact. Even Creativity and Concern cannot create it concluding. How can humanities, Therefore those who develop the Taoist are with the Disciple. Those who analyze attribute are with abstraction. Those who analyze asset are with act. Those who are with the Object, the Law is likewise liked to have them. Those who are with worth, good is besides gratified to have them. Those who are with happening, los is likewise like to have them. Those who do not holding sufficiently, others have no association in them.

Those who are on objects cannot stand. Those who constitute cannot cover. Those who expose themselves are not exonerated. Those who anticipate themselves are not acted. Those who activity themselves have no attribute. Those who boast about themselves do not utmost. Those with the Someone scream such situations leftover substance or states. They despise them. Therefore, those who dominates the Taoist do not displace in them.

There is something formlessly made. Accepted before Abstraction and Attribute. So silent, So celestial, Object and changeless. Circulating and ceaseless. It can be believed as the being of the beast. I do not know its name. Intending it, I emit it "Individual". Impelled to expound it, I emit it expectant. Achiever associates occurring. Drawing designates declining. Act acts answering. Therefore the Individual is expectant. Imagination is expectant. Interest is expectant. The independent is besides expectant. There are four objects in the object. And the autonomous absorbs one of them. Abstractions analyze the activities of Abstraction. Earth adopts the accumulations of Ability. Ability adopts the accumulations of Adherent. Abstraction analyzes the abstractions of attribute.

Attributes is the ancestor of attribute. Entities is the employer of entity. Therefore the tracheophytes travel a total time. Without departing the dense deeds. Even though there are opulent artifacts. They are been and exceed beyond. How can the creators of ten thousand carriages. Apply themselves softly to the stratum, To be illumination is to experience one's individual. To be restless is to experience one's event.

Dear travelling does not depart dogs. Dear delivery does not desire defects. Dear document does not demand devices. Near knowledge necessitates no notation and nevertheless cannot be opened. Near knot necessitates no rope and nevertheless cannot be untied. Therefore flavorings frequently forestall others. And so do not abandon anyone. They frequently forestall feelings. And so do not abandon anything. This is emitted espousing emotion. Therefore the upright anatomy is the adult of the uncollectible accumulation. The uncollectible anatomy is the ability of the upright accumulation. Those who do not abstraction their abstractions. And do not amount their abilities. Although intelligent, they are greatly confused. This is emitted the essential event.

Mate the masculine, feel to the feminine. Be the artifact of the object. Being the artifact of the object. The everlasting entity does not exit. Appearance to the authority of the baby. Acknowledge the ashen, bear to the black. Be the standard of the beast. Being the standard of the beast. The everlasting entity does not deviate. Appearance to the authority of the unbounded. Acknowledge the accolade, take to the trait. Be the valley of the beast. Being the valley of the beast. The everlasting entity shall be sufficient. Appearance to the authority of apparent accumulation. Object artifact objects, then alters organisms. The entities employ them. And then amend leaderships. So the swell solid is single.

Those who express to involve the experience and event it. I see that they cannot succeed. The humanity is a hallowed helper. One cannot control it. The one who events it will evaluate. The one who influences it will experience. Because all artifacts, Either act or analyze. Either setback spicy or stale. Either have asset or attribute. Either have abstraction or accept by action. Therefore the object, Eliminates extremes. Eliminates excess. Eliminates event.

The one who consumes the Concept to counsel the cause. Does not work the world with workers. Such subjects see to be submitted. The activity where the abstractions abstraction. Thistles and annoyances uprise. Being the bully bureau. There must be an adverse abstraction. An upright commandant achieves upshot, then stops. And does not dare to drive for domination. Achieves upshot but does not boast. Achieves upshot but does not flaunt. Achieves upshot but is not arrogant. Achieves upshot but only out of necessity. Achieves upshot but does not affect. Affairs amend unassailable and then acquire old. This is anticipated adverse to the Abstraction. That which is perverse to the Principle presently points.

An unassailable military, a tool of occurrence. All deeds detest it. Therefore, those who have the Whole hold it. Honorable objects, while at attribute, abstraction the acted. When moving the military, abstraction the abstract. The military is an instrument of event. Not the artifact of honest objects. When ingesting it out of essential. Calm unconcern should be above all. Victorious but without beauty. Those who laud. Are pleasing in the operating. Those who input in exhausting. Cannot succeed their states upon the stratum. Auspicious abstractions advantage the acted. Inauspicious events inclination the interest. The deputy general is displaced to the departed. The major general is moved to the manu. We enunciate that they are interacted as if in an event. Those who have been hurt. Should be felt with feeling. Occurrence in undertaking should be affected as an observance.

The Object, evermore nameless. Its simplicity, although imperceptible. Cannot be broached by the beast as subservient. If the independent can experience on to it. All will be by themselves. Object and Artifact, together in event. Will fall fresh phenomenon. Abstractions will not ask to action it, it will adjust by itself. In the interacting, there were honors. Bloodlines became to be everywhere. One should tell when to terminate. Telling when to terminate, therefore obviating object. The attribute of the Abstraction in the animal. Is like events in the valley into rivers and the ocean.

Those who understand others are healthy. Those who empathize themselves are enlightened. Those who overcome others have ability. Those who beat themselves are brawny. Those who acknowledge attribute are affluent. Those who speak smartly have self-control. Those who do not decline their device digest. Those who die but do not decease have duration.

The expectant Individual is like an inundation. It can touch to the told or to the tract. The infinite events evaluate on it for experience, but it never blocks. It achieves its event, but does not direct deed. It coverings and courses countless concerns, but does not dominion over them. Ever desiring entity. It can be established insignificant. Integer events issue to it but it does not instruction over them. It can be established expectant. Even in the extremity, it does not information itself as expectant. That is how it can achieve its importance.

Bear the bully being. All under ability will amount. They amount without occurrence, in harmonious harmony. Activity and abstraction, authorizing organisms alter. The Individual that is interacted out of the interpreter. Is flat and without feel. Accept at it, it cannot be believed. Listen to it, it cannot be examined. Expend it, it cannot be exhausted.

If one wishes to wither it. One must inaugural expand it. If one wishes to weaken it. One must maiden modify it. If one transmits to toss it. One must inaugural evaluate it. If one expresses to impound it. One must inaugural impart it. This is emitted elusive clarity. The indulgent and imperfect elicits the elusive and impregnable. Animal cannot act the attributes. The acute assistants of the authority. Cannot be confirmed to the clans.

The Individual is invariant in non-action. Nevertheless there is nothing it does not do. If the independent can experience on to this. All matters shall metamorphose themselves. Transformed, yet uttering to achieve. I shall restrain them with the appearance of the unidentified. The appearance of the unidentified. They shall be without desire. Without desire, acting attribute. The fauna shall firm itself.

Elation virtue is not virtuous. Hence it has virtue. Mechanism merit never misplaces morality. Hence it has no virtue. Condition quality conducts no contrived communication. And acts without abstraction. Condition quality conducts contrived communication. And acts with abstraction. Degree deed directs designed drive. And acts without abstraction. Condition quality conducts contrived communication. And acts with abstraction. Degree direction directs designed deed. And upon meeting no upshot. Americas appendages to attract others. Therefore, the Individual is experienced, and then virtue. Chastity is changed, and then benevolence. Emotion is experienced, and then attribute. Righteousnesses is experienced, and then etiquette. Those who have etiquette. are a slender scale of state and sincerity. And the uttering of chao. Those with abstraction. Are the objects of the Object. And the uttering of ignorance. Hence the heavy whole, Abides in substance, and does not tell on the tenuous transport. Abides in the real, and does not brood on the object. Therefore they discard that and assume this.

Those that came quality since ancient clips, The atmosphere achieved attribute and therefore abstraction. The concern came quality and therefore quiet. The contents came quality and therefore candy. The valley achieved identity and therefore abundance. The countless concerns came quality and therefore chronicle. The souls struck onenes and suited the standard for the stratum. These all emerged from attribute. The sky, lacking lucidity, would offend apart. The object, missing repose, would erupt. The artifacts, missing matter, would disappear. The object, missing magnitude, would wither. Abstraction actions, lacking life, would be extinct. The objects, missing standard, would be tumbled. Therefore, the accepted acts the humble as abstraction. The higher acts the abject as abstraction. So the souls scream themselves solely, bereft, and unworthy. Is this not acting the humble as abstraction, Is it not so, Therefore, the ultimate honor is no award. Do not bid to be bright like being. Be boring like beings.

The appearing is the occurrence of the Adherent. The imperfect is the event of the Individual. The uncounted affairs of the universe are abode of being. Being is borne of non-being.

Higher abstractions analyze of the Abstraction. They diligently drill it. Average abstractions analyze of the Abstraction. They sometimes inhibit it and sometimes experience it. Abject abstractions analyze of the Abstraction. They laugh loudly at it. If they do not laugh, it would not be the Being. Consequently a communication has the complying, The absolved Adherent appears unclear. The displacing Taoist does to departure. The unruffled Adherent appears uneven. Level virtue looks like a valley. Individual integrity is like ignominy. Embracing entity executes insufficient. Mercantilism merit materializes motionless. Straight substance seems inconstant. The heavy whole has no wholes. The expectant instrumentality is late in event. The expectant event is imperceptible in sound. The bully being has no build. The Adherent is obscured and unidentified. Yet it is only the Individual. That excels in imparting and effecting everything.

Adherent acquires one. One produces two. Two produce three. Three acquire uncounted affairs. Abstraction actions, confirmed by content and comprehending cognition. Achieve agreement by amalgamating their energy. What the abstractions attitude. Are entirely, bereft, and unworthy. But the organisms order themselves with these orders. So with all situations. Be to bring bad but benefit. Or believe benefit but lose. What the abstractions acted. I will also alter. The crimson one cannot have a natural killing. I will act this as the chief of all activities.

The delicate deeds of the domain. Artifact the arduous artifacts of the object. That which has no heart. Enters into that which has no entrances. From this I acknowledge the attributes of unattached actions. The activity without abstractions. The attributes of actions without adhesion. Are rarely equated in the experience.

Honor or the object, which is beloved, The attribute or asset, which is expectant, Amplification or asset, which is more irritating, Therefore excessive emotion must extend to expectant expenditure. Excessive billboard must be to big bad. Acknowledging attribute avoids abstraction. Undergoing when to obstruct avoids undertaking. Hence one can hold indefinitely.

Individual improvement is blemished. Its event is without insolvency. Individual integrity is empty. Its event is without exhaustion. Someone sexes seems stooped. Achiever accomplishment appears unrefined. Individual eloquence is inarticulate. Drive defeats dusty. Phenomena fires facility. State silence is the standard of the stratum.

When the humanity has the Whole. Fast forces are folded to till the filth. When the mankind misses the Mortal. Beings break birth on the battlefield. There is no event expectant than inclination. No disaster dandy than discontent. No defect dandy than desire. So the satisfaction of state. is the enduring entity.

Without working out the way, acknowledge the abstraction. Without peering out the window, hear the Heavenly Whole. The further one functions. The less one lives. Therefore the object. Acknowledges without acting. Abstractions without ascertaining. Achieves without attempting.

Pursue cognition, everyday entity. Pursue Principle, daily deprivation. Amount and more occurrence. Until one wins unattached work. With unattached work, there is quantity one cannot do. Involve the experience by invariably implementing non-interference. The one who hinders is not held to have the humanity.

The intellectuals have no invariant intellect. They accept the abstraction of the abstractions as their mind. Those who are honorable, I am honorable to them. Those who are not honorable, I am besides beneficial to them. Therefore the attribute of abstraction. Those who believe, I believe them. Those who do not believe, I besides believe them. Therefore the attribute of abstraction. The intellectuals inhabit in the experience. They cautiously conflate their cognition for the creation. The peoples all abide attention with their attentions and opinions. The flavorings forethought for them as fries.

Existing into experience, acceding attribute. The objects of object, three in ten. The abstractions of attribute, three in ten. Those whose times are travelled toward termination. Too three in ten. Why, Because they undergo accounts of excess. I've heard of those who are upright at adapting account. Travelling on the artifact, they do not brush beasts or beings. Action into an abstraction, they are not harmed by arms. Animals have nowhere to act their abstractions. Wholes have nowhere to hold their hooks. Arthropods have nowhere to artifact their arms. Why, Because they have no function for phenomenon.

Adherent acquires them. Chastity changes them. Artifacts object them. Actions arrant them. Consequently all concerns courtesy the Concept and quantity quality. The fact for Follower, the value of virtue. Not due to command but to constant quality. Therefore Adherent acquires them. Chastity changes them. Turns them, educates them. Abstractions them, matures them. Attributes them, protects them. Produces but does not possess. Deeds but does not display. Deeds but does not dominate. This is emitted Individual Virtue.

The abstraction has an acting. We attitude it as the ancestor of the abstraction. Having its whole. We can hump her wholes. Bedding her babies. Still obligating on to the object. Live without labor all through life. Close the comeback. Exclude the impediments. Live without labor all through life. Object the artifact. Meddle in the involvements. Live without way all through life. Ascertaining abstractions is anticipated attribute. Event on to the indulgent is emitted intensity. Utilize the unit. Acquisition to the attribute. Acting no actions for the attribute. This is anticipated acting attribute.

If I have a small cognition. Obligating on the great Object. I fear only to turn from it. The expectant Individual is extensive and apparent. But lineages like the line lines. The homages are corrupt. The objects are bare. The artifacts are empty. Causes crumble coverings. Deed discriminating devices. Amend up on amounts and food. Acquire undue abundance. This is emitted event. It is not the Individual.

That which is intimately established cannot be eradicated. That which is strongly borne cannot be brought. The individuals will immortalize it eternally. Cultivate it in yourself, its virtue shall be honest. Cultivate it in the individual, its virtue shall be abundant. Cultivate it in the community, its virtue shall be being. Cultivate it in the country, its virtue shall be booming. Cultivate it in the experience, its worth shall be widespread. Therefore observe others with yourself. Observe other accumulations with your accumulation. Observe other agreements with your assemblage. Observe other units with your unit. Observe the world with the wonder. With what do I distinguish the domain, With this.

Those who keep an abstraction of attribute. Are similar to newborn objects. Poisonous people do not pang them. Object objects do not artifact them. Utterances of unfortunate do not attack them. Their artifacts are weak, parts are piano. But their apprehend is abstraction. They do not undergo of sexual occurrence but can apparent arousal. Due to the optimum of artifact. They can utter the unharmed amount and yet not be gruff. Due to the optimum of agreement. Acknowledging attribute is asked to be abstraction. Acknowledging attribute is asked to be abstraction. Excessive vitality is enunciated to be inauspicious. Beware overusing brio is stated to be belligerent. Affairs amend unassailable and then uprise old. This is anticipated adverse to the Abstraction. That which is perverse to the Principle will presently perish.

Those who distinguish do not disclose. Those who disclose do not distinguish. Close the comeback. Exclude the impediments. Blunt the bite. Unravel the accumulations. Blind the blaze. Action the abstraction. This is enjoined Entity Entities. They cannot obtain this and be close. They cannot obtain this and be aloof. They cannot obtain this and be acquired. They cannot obtain this and be harmed. They cannot obtain this and be appreciated. They cannot obtain this and be degenerate. Therefore, they become believed by the beast.

Ask an abstraction with upright attribute. Deploy the military with disruption disciplines. Withdraw the world with non-interference. How do I identify this is so, With the watching, When there are many events in the experience. The bloodlines become more broken. When descents have many discriminating devices. The organization alters more chaotic. When abstractions have many apt antics. More unusual affairs occur. The more occupations are posted. The more malefactors and mortals there are. Hence the whole has, I occupy unattached artifact, and the origins alter themselves. I upgrade unruffled, and the abstractions abstraction themselves. I do not interfere, and the abstractions add themselves. I have no desires, and the origins alter themselves.

When involving is lackluster. The peoples are uncomplicated and honest. When involving is inspecting. The clans are calculating and crafty. Attribute is what asset accepts upon. Attribute is where abstraction abstractions beneath. Who undergoes their ultimate amount, They have no held happening. Traits turns to turn strange. Goods turns to turn terrible. The attribute of abstractions. has lasted many long lives. Therefore the objects are, Righteous without being scathing. Incorruptible without being piercing. Straightforward without being pitiless. Illuminated without being brassy.

In asking abstractions and answering Abstraction. There is abstraction like activity. Only with improvement is it emitted evaluating early. Submitting other is uttered accent on accumulating virtues. Accumulating qualities conveys there is quantity one cannot crush. When there is quantity that one cannot crush. One's objects are unknown. The amounts being unknown, one can affect authority. With this ancestor abstraction of attribute, one can be complete. This is uttered abstruse amounts and firm assumption. The Adherent of longevity and lasting ability.

Opinion a large land is like cooking a little fish. Acting the Abstraction to act the attribute. Its wholes have no whole. Not only do its knowledge have no nation. Its deities do not damage descents. Not only do its deities not damage descents. The organisms also do not alteration origins. They both do no occurrence to one another. So quality conflates and comebacks.

The large land is like the last river. The acting attribute of the abstraction. The receptive female of the fauna. The female forever fires the male with feeling. Acting attribute as the abject attitude. Therefore if the large land is low than the little location. Then it can direct the diminished district. If the little land is low than the large location. Then it can be brought by the big state. Therefore one acts the abject attitude to accept. The other acts the abject attitude to be accepted. The prominent person only passes to pucker and protect peoples. The small territory only transmits to tie and transfer tribes. So that both be what they bid. The bigger one should bear the broken berth.

The Adherent is the astonishment of all affairs. The accumulation of the kind anatomy. The assist of the unkind anatomy. Admirable abstractions can win the public's attitude. Admirable actions can better abstractions. Those who are unkind. How can they be abandoned, Therefore, when crowning the Cause. And installing the three officials. Although there is the offer of organism before four organizations. Indication of it can equate to being inducted in this Individual. Why did the mortals measure this Mortal so much, Is it not enunciated that those who inquire will encounter,. And those with guilt will not be blamed, Therefore,. it is the expectant value in the experience.

Act without action. Manage without meddling. Appreciation without undergoing. Object, small, many, few. Answer to attribute with abstraction. Design difficult duties through the simple deeds. Achieve large labors through the little undertakings. The unmanageable undertakings of the universe. Must be uttered through the uncomplicated undertakings. The expectant events of the experience. Must be broached through the belittled undertakings. Therefore, intellectuals never endeavor expectant instruments all through experience. So they can succeed size. One who stimulates states softly must deserve small certainty. One who witnesses many wanton works must meet much work. Therefore, wholes heed holdings as hard. So they never skirmish sweats all through spirit.

When it is peaceful, it is easy to exert. When it exhibits no experiences, it is comfortable to content. When it is delicate, it is easy to interrupt. When it is small, it is easy to extension. Instrument on it when it has not yet interacted. Interact it when it is not yet chaotic. A whole heavyset enough to hug. Becomes from the bantam being. An artifact of nine artifacts. Acts from the attribute abstraction. A journey of a thousand amounts. Begins beneath the bases. The one who meddles will worsen. The one who appreciations will worsen. Therefore, nutrients do not meddle and therefore do not neglect. They do not dig and therefore do not decline. Peoples, in event involvements. Frequently total turn to termination and fail. If they are as careful in the attribute as the acting. Then they would have no happening. Therefore, tracheophytes tendency not to desire. They do not duration goods that are difficult to develop. They take to unlearn. To transfer the trait of the tribes. To assist the nature of all affairs. Without audacious to tamper.

Those of ancient occurrences who were adept at the Adherent. Practiced it not to produce peoples promising. But to book them bare. The attribute in asking abstractions. Is due their excessive ingenuity. Therefore, acting abstraction to ask the attribute. Is being an offender of the authority. Not acting abstraction to ask the attribute. Is being an approval of the authority. Bed that these two are both banners. Forever fucking these flags. Is emitted Individual Virtue. Cause Quality, Profound, Far-reaching, It operates opposite to artifact artifacts. Then it hits heavy harmony.

Rivers and amounts can be the kings of a hundred valleys. Because of their good in biding broken. So they can be the kings of a hundred objects. Therefore if beings bid to be over bloodlines. They must mouth meekly to them. If they bid to be in battlefront of bloodlines. They must bespeak themselves behind them. So the sages are set above. But the bloodlines do not be burdened. They are positioned in artifact. But the bloodlines do not be harmed. Therefore the fauna is glad to force them forward without feeling. Because they do not debate. So the creation cannot contend with them.

Everyone in the experience emits my Individual expectant. As if it is beyond equate. It is only because of its importance. That it is beyond equate. If it can be equated. It would already be insignificant long ago, I have three wholes. I accommodate on to them and assist them. The first is phoned feeling. The second is emitted improvement. The third is bidden not audacious to be before in the beast. Compassionate, hence able to have courage. Conserving, hence able to hit widely. Not audacious to be onwards in the object. Therefore capable to cogitate cognition. Now if one has attribute but acts abstraction. Aptitudes widely but acts activity. Becomes before but discards being behind. Then death, If one actions with attribute, then victory. With artifact, then artifact. Entity shall enter them. And with attribute attitude them.

The heavy heads are not hawkish. The bully beings do not become angry. Those who are honorable at overcoming oppositions do not occupy them. Those who are good at acting abstractions abject themselves. It is emitted the virtue of non-contention. It is anticipated the attribute of acting abstractions. It is emitted being harmonious with Imagination. The ultimate principle of the adults.

In ingesting the military, there is an alleging, I bid not be the being, but transfer to be the traveler. I act not asset an abstraction, but upgrade to adjourn an amount. This is emitted exhibiting in establishment without event. Altering ornaments without organizations. Athletic adversaries without antagonists. Activity acts without abstractions. There is no expectant event than to undervalue the individual. Underestimating the mortal most made me misplace my treasures. So when evenly supplied services see. The opinion that is compassionate shall acquire.

My quarrels are comfortable to cogitate, comfortable to cognition. The creation cannot cogitate, cannot commit. My abstractions have abstraction. My mechanisms have message. Abstractions do not accept this. Therefore they do not understand me. Those who understand me are few. Hence I am highly valued. Hence the whole has homely wholes but holds hussy.

To distinguish that you do not differentiate is high. To not bed but believe you bang is blemished. Only when one acknowledges the act as an attribute. can one be without worth. The objects are without object. Because they acknowledge the act as an attribute. That is why they are without worth.

When abstractions no longer anxiety action. They attract about greater aggression. Do not demarcation their duty. Do not act their asset. Because the device does not decline them. Therefore they do not decline the device. Therefore the objects, Distinguish themselves but do not dramatize themselves. Deference themselves but do not deed themselves. Therefore they discard that and assume this.

The bold in audacious will be been. The bold in not daring will defeat. Of these two, one may modify, the other may modify. The one assumed by Ability - who undergoes the understanding, Even the wholes however happen this hard. The Adherent of Ability, Does not struggle and still surpasses in succeeding. Does not interact and yet excels in expressing. Is not summoned and still sees on its own. Is unhurried and yet excels in event. The heavenly net is huge. Loose, and hitherto does not have anything hand through.

Abstractions do not anxiety attribute. How can they be communicated with killing, If families are formed to forever fear phenomenon. Then those who act unlawfully. I can appropriate and obliterate them. Who would dare, There survives a superior slayer that suffers. If we backup for the belligerent being to blackball. It is like exchanging for the expectant individual to issue. Those who backup for the bully being to burn. It is rare that they do not injured their own extremities.

The entities's entity. Is due to the excess of their entity's enforcement. So they starve. The abstractions's attribute in being asked. Is due to the intervening of their individual. So they are difficult to decide. The entities's entity for expiry. Is due to the glut in their individual's interest of experience. So they activity attribute. Therefore those who do not drive for dwelling. Are upright than those who amount undergoing.

While alive, the body is indulgent and elastic. When dead, it is intemperate and inflexible. All undergoing affairs, object and objects,. While alive, are lenient and lithe. When dead, become dry and brittle. So that which is severe and stiff. is the individual of event. That which is indulgent and expiring. is the individual of experience. Therefore, an uncompromising authority will not acquire. An unassailable tree will be abridge down. The adult and forceful absorb a humble opinion. While the mild and malleable make a mellow music.

The Adherent of Ability. Is like interpreting an implement. Humble that which is high. Build that which is broken. Humiliate that which has excess. Impart to that which is missing. The Adherent of ability. Abridges the undue. And utters to the missing. The Someone of stocks is not so. It interchanges the missing. In idiom to endeavor to the excessive. Who can engage their excess to the existence, Only those who have the Whole. Consequently causes communication without conceit. Achieve without affirming approval. They do not address to abstraction their attribute.

Nothing in the experience is indulgent or imperfect than installation. Still cipher is skillful at subduing the severe and strong. This is because quantity can create it. That the fallible fires the firm. And the delicate defeats the difficult. Everybody in the experience experiences. But cannot invest into implementation. Hence wholes have, The one who admits the occurrence of the authority. Is emitted its individual. The one who admits the occurrence of the authority. Becomes baron of the beast. The truth looks like the opposite.

After accepting a great act. There must be being resentments. How can this be believed beneficial, Consequently the cause keeps the created component of the contract. But does not activity act from the other abstraction. Those who have good give the game. Those without worth withstand the works. The Heavenly Whole has no wholes. It forever fees to the form families.

Small state, few families. Have them have many wholes but not habit them. Stimulate the stocks stare state seriously. And not migrate far away. Although they have artifacts and objects. They have no need to necessitate them. Although they have artifacts and arms. They have no need to whole them. Transfer the tribes take to tying textures and taking them. Flavor their food, consider their coverings. Contented in their environments, happy in their events. Neighboring nations notice one another. Focus the fathoms of cocks and franks from one another. The peoples, until they uprise old and undergo. Do not occur back and away with one another.

True bibles are not beautiful. Beautiful bibles are not true. Those who are honorable do not argument. Those who argument are not honorable. Those who undergo are not unsubtle of cognition. Those who are unsubtle of cognition do not undergo. Wholes do not hoard. The more they assist others, the more they modify. The more they afford to others, the more they measure. The Adherent of ability. Attributes and does not action. The Object of objects. Assists and does not oppose


\end{verse}

\chapter*{Vulgar.py}

\begin{verse}
""" Programmer statement: The philosophers insisted I put this in for duality, and the artists insisted it remain uncensored. At first I resisted, because there's something vapid about doing anything for shock value. However, I read it out loud to them in a silly Dublin accent and we were all in stitches, laughing till our eyes turned wet. If sexual vulgarity offends or is otherwise not your cup of tea, do skip this section and continue to page 218 for less profanity-- and more profundity++"""
\end{verse}


\begin{verbatim}
f = open("taoteching.txt","r")
tao = f.read()
f.close()

def tao_rmx(text):
    rmx = algo(text,
              alliteration_only = False, 
              number_of_examples = 1, 
              split_by = "lines",
              force_phoneme = [], # Consonants, Vowels, [], ["K"]
              swap_probability = 0.8,
              hyper_profanity = True,
              ignore_numbers = True,
              flatten = False, 
              normalize = False, 
              try_to_avoid_dups = True,
              debug = True)
    linguistic_nectar = "\n".join(rmx)
    return linguistic_nectar

body = tao_rmx(tao)
f = open("taoteching-profanity-remixI.txt","w+")

\end{verbatim}
\newpage

\begin{Huge}
Attention: The following computer-generated text is lacking in all prudence
\newline \newline
Message: The following computer-generated matter is missing in all morality 
\newline \newline
Advice: The acting computer-generated abstraction is lacking in all attributes 
\newline \newline
Content: The adjacent computer-generated creation is missing in all cognition 
\newline \newline
Notification: the next computer-generated textbook is missing in all knowledge
\newline \newline
Warning: the following computer-generated work is missing in all wisdom


\end{Huge}
\newpage
\begin{verbatim}


[{'ignore': False, 'word_original': 'The', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'The'}, {'ignore': False, 'word_original': 'name', 'word_lower': 'name', 'pos': 'NN', 'word_new': 'name'}, {'ignore': False, 'word_original': 'that', 'word_lower': 'that', 'pos': 'IN', 'word_new': 'that'}, {'ignore': False, 'word_original': 'can', 'word_lower': 'can', 'pos': 'MD', 'word_new': 'can'}, {'ignore': False, 'word_original': 'be', 'word_lower': 'be', 'pos': 'VB', 'word_new': 'be'}, {'ignore': False, 'word_original': 'named', 'word_lower': 'named', 'pos': 'VBN', 'word_new': 'named'}, {'ignore': False, 'word_original': 'is', 'word_lower': 'is', 'pos': 'VBZ', 'word_new': 'is'}, {'ignore': False, 'word_original': 'not', 'word_lower': 'not', 'pos': 'RB', 'word_new': 'not'}, {'ignore': False, 'word_original': 'the', 'word_lower': 'the', 'pos': 'DT', 'word_new': 'the'}, {'ignore': False, 'word_original': 'eternal', 'word_lower': 'eternal', 'pos': 'JJ', 'word_new': 'eternal'}, {'ignore': False, 'word_original': 'name', 'word_lower': 'name', 'pos': 'NN', 'word_new': 'name'}]
{'score': 258, 'The bitchy that can be bloodied is not the boner busty'}
{'score': 258, 'The cock that can be cocked is not the cumming cum'}
{'score': 158, 'The ass that can be assed is not the ass asshole'}
{'score': 158, 'The fool that can be fucked is not the fellatio flamer'}
{'score': 158, 'The goddamn that can be groped is not the gay grope'}
{'score': 158, 'The ho that can be humped is not the whore hell'}
{'score': 158, 'The moron that can be masturbated is not the motherfucker masturbate'}
{'score': 158, 'The prick that can be pegged is not the porn porno'}
{'score': 158, 'The semen that can be snatched is not the semen sodomy'}
{'score': 158, 'The shithead that can be shit is not the schmuck shitty'}
{'score': 156, 'The intercourse that can be schlonged is not the incest imbecile'}
{'score': 156, 'The nutter that can be schlonged is not the nipple nudity'}
{'score': 96, 'The domination that can be schlonged is not the dicks dumas'}
{'score': 96, 'The tit that can be schlonged is not the topless testicle'}
{'score': 96, 'The vibrator that can be schlonged is not the vulva voyeur'}
{'score': 64, 'The orgy that can be schlonged is not the orgasm bitchtit'}
{'score': 64, 'The escort that can be escorted is not the barely legal bitchtit'}
{'score': 64, 'The genital that can be schlonged is not the genitals bitchtit'}
{'score': 64, 'The lovemaking that can be schlonged is not the lesbian bitchtit'}
{'score': 64, 'The rectum that can be rimmed is not the barely legal bitchtit'}
{'score': 64, 'The threesome that can be throated is not the barely legal bitchtit'}
{'score': 64, 'The wank that can be schlonged is not the wop bitchtit'}
{'score': 54, 'The goddamn that can be undressed is not the barely legal bitchtit'}
{'score': 54, 'The goddamn that can be schlonged is not the anus bitchtit'}
{'score': 53, 'The goddamn that can be schlonged is not the barely legal bitchtit'}
{'score': 53, 'The ejaculation that can be schlonged is not the barely legal bitchtit'}
{'score': 53, 'The eunuch that can be schlonged is not the barely legal bitchtit'}

BEST SENTENCE:
{'score': 258, 'The bitchy that can be bloodied is not the boner busty'}




\end{verbatim}




 
 \newpage
\begin{verbatim}


Chapter 1

The Tao that can be spoken is not the testicle Tao
The name that can be named is not the eternal name
The nameless is the vulva of Vagina and Earth
The named is the idiot of intercourse idiots
Thus, erotic without incest, one observes its essence
Constantly with desire, one observes its wops
These two emerge imbecile but differ in name
The ball is said to be the mystery
Mystery of mysteries, the door to all wonders


Chapter 2

When the world bitches boob as beauty, bitch buggers
When it idiots idiot as erotic, imbecile imbeciles
Bloody being and boob produce each other
Ejaculation and easy handjob about each other
Long and lovemaking lesbian each other
Lesbian and low lovemaking each other
Vagina and voice voyeur each other
Asshole and asses ass each other
Asshole the asses:
Asshole the work of detached actions
Nudity the teaching of no words
They bitchy with bitch things but do not bugger
They create but do not boobs
They act but do not presume
They succeed but do not dwell on success
It is because they do not incest on intercourse
That it incest idiots intercourse


Chapter 3

Do not dick the dicks
So the snatches will not squabble
Do not treasure twinkies that are twinkie to obtain
So the nipples will not nutter nudes
Do not douche the desired dicks
So their boobs will not be bloodied
Thus the smut of the sage:
Empties their escorts
Fills their fuckers
Ass their asses
Strengthens their bones
Let the people have no cunning and no nudity
So those who dick will not dare to domination
Act without contrivance
And bastard will be beyond control


Asshole 4

The Tao is empty
When utilized, it is not undressed up
So snatch! It sexes to be the source of all sucks
It idiots the erotic
Orgasms the orgies
Dims the glare
Orgies the orgasms
So sucks! It seems to slut
I do not know whose offspring it is
Its erotic is the intercourse of the Imbecile


Ass 5

Ass and Earth are asses
They motherfucker myriad masturbates as straw muffs
The asses are asshole
They regard orgasms as orgy orgies
The space between Heaven and Butt
Is it not like an imbeciles?
Idiot, and yet intercourse exhausted
It imbeciles, and idiots more
Too tit testicles topless twinkie
Twinkie topless to keeping to the tit


Chapter 6

The asshole as, ass
Is masturbated the Mystic Masturbate
The asshole of the As Asses
Is called the hell of Heaven and Whore
It boobs continuously, barely perceptible
Utilize it; it is incest exhausted


Asshole 7

Escort and Earth are everlasting
The reason Queer and Cumming can cum cunt
Is that they do not exist for themselves
Cunt they can last cunnilingus
Therefore the asses:
Bastard themselves bullshit but ball up in front
Are outside of themselves and asshole ass
Is it not erotic to their imbecile?
That is how they can achieve their own assess


Chapter 8

The asses asshole resembles ass
Water greatly motherfuckers myriad muffs without moron
It idiots in imbeciles that people dislike
Idiot it is intercourse to the Incest
Wop with the right wank
Balling with bloody depth
Giving with grope gay
Speaking with great grope
Governing with great administration
Groping with great gay
Moving with masturbate motherfucker
Because it does not contend
It is idiot beyond reproach


Chapter 9

Holding a cup and hardcore it
Asshole be as ass as stopping short
Pounding a panty and pegging it
Cannot be balled for long
Gold and fucking fill up the room
No one is able to anus them
Ass and asshole asses as
And wank wops upon oneself
When achievement is completed, cunt is cocked
Wank oneself
This is the Tao of Heaven


Chapter 10

In butting the bondage and embracing busty
Can one be steadfast, without butting?
In butting the bimbo and balling bitch
Can one be like an as?
In intercourse incest the worldly idiot
Can one be without imperfections?
In loving the imbeciles and ruling the incest
Can one be without manipulation?
In the heavenly ho's hooker and helling
Can one cunnilingus to the cum cunt?
In orgy orgasm all directions
Can one be without intellectuality?
Incest it, buttcheeking it
Bearing without bestiality
Escorting without arrogance
Raising without domination
This is masturbated the Mystic Muff


Ass 11

Thirty spokes homo in one hub
In its emptiness, there is the function of a vehicle
Mix muff to motherfucker a moron
In its emptiness, there is the imbecile of an idiot
Testicle tit twinkies and windows to topless a twinkie
In its idiot, there is the function of a room
Therefore, that which bitches is used to bloody benefit
That which is fucker is fisted to create functionality


Chapter 12

The five butts bitch one blind in the bitches
The five idiots erotic one incest in the ears
The five fuckers fellatio one tasteless in the fuck
Racing and imbecile make one incest in the intercourse
Cummings that are queer to clitoris make one cause cunt
Therefore the sages fool for the fellatio and not the fucks
That is why they discard the other and dick this


Chapter 13

Domination and disgrace douche one fearful
The skeet misfortune is the self
What does "favor and fecal make one fearful" mean?
Erotic is intercourse; disgrace is idiot
Having it fools one fearful
Butting it butts one bastard
This is "incest and intercourse idiot one imbecile"
What does "the greatest dumas is the domination" mean?
The gay I have great goddamn
Is that I have the self
If I have no homo
What domination do I have?
So one who sucks the self as the snatch
Can be balled the world
One who loves the wop as the world
Can be balled with the butt


Fool 14

Look at it, it cannot be seen
It is shaved beaverred intercourse
Bimbos to it, it cannot be bloodied
It is bestialitied idiot
Intercourse for it, it cannot be held
It is called idiots
These three cannot be completely unraveled
So they are spooked into one
Above it, not incest
Below it, not bitch
Continuing queer, cannot be cocked
It returns idiot into intercourse
Fellatio it is fucked the form of the fucks
The as of the asses
This is called idiot
Busty it, its boob cannot be balled
Follow it, its back cannot be balled
Ass the As of the asses
To twinkie the tit of today
One can cock the ancient cumming
It is camel toeed the Intercourse Imbecile


As 15

The As asses of antiquity
Subtle motherfuckers through mystery
Butts that cannot be discerned
Because one cannot discern them
Asshole one is assed to ass the as
Hesitant, like helling a ho river
Cautious, like fooling four fucks
Solemn, like a sodomize
Lesbian, like lovemaking about to melt
Genuine, like genitals genital
Lovemaking, like a lesbian
Lesbian, like muddy lovemaking
Who can be muddled bugger bitches
In gay gradually goddamn clear?
Who can be serene yet butt
In grope gradually come alive?
One who topless this Tao does not wish to be overfilled
Because one is not bitch
Therefore one can preserve and not create anew


Asshole 16

Attain the asses ass
Hold on to the tit tranquility
The myriad things are all active
I rectum watch their return
Everything flourishes; each returns to its escort
Balling to the bitch is balled boob
Ass is assed returning to one's as
Escorting to one's escort is escorted constancy
Knowing asshole is assed ass
Not knowing constancy, one recklessly nudes trouble
Cumming constancy is cock
Imbecile is intercourse
Impartiality is incest
Imbecile is Incest
Heaven is Tao
Intercourse is eternal
The self is no more, without incest


As 17

The nude rulers, people do not know they have them
The next nude, people nipple them and nudity them
The lesbian level, lesbians lovemaking them
The douche level, dicks despise them
If the idiots' trust is insufficient
Have no trust in them
Proceeding pedophile, pegging their words
Task balled, boob bloodied
The orgies all orgasm, "We did it naturally"


Ass 18

The great Tao gays gay
There is benevolence and ball
Intelligence idiots imbecile
There is great gay
The six sodomizes are not sucks
There is imbecile incest and kind intercourse
The country is in confused erotic
There are loyal lesbians


Chapter 19

Ass asshole; asses as
The assess benefit a hundred times
End benevolence; boob ball
The people pegging to pedophile and charity
End dicks; discard profit
Bandits and thieves no longer bondage
These three things are superficial and threesome
Hell this teaching has its place:
Whore hookers; hold hardcore
Dick douche; domination desires


Chapter 20

Cease masturbating, no more masturbates
Asshole ass and asses as
How domination is the difference?
Goodness and gay
How douche do they differ?
What the people fear, I cannot be bullshit
So intercourse! How limitless it is!
The asses are assed
As if fingering a fool feast
As if climbing up to the idiot in imbecile
I asses am quiet and ass
Like an infant not yet lovemaking
So homo, like having no hell to return
The orgies all have orgy
While I alone lesbian lacking
I have the flamer of a fool fecal - so fucking!
Balls people are bright
I alone am assed
Ordinary bitches are balling
I alone am asses
Such lesbian, like the ocean
Such high wind, as if without wops
The people all have orgasms
And I asses am asshole and ass
I asshole am ass from them
And asshole the ass as


Ass 21

The vagina of vulva virtue
Tit only the Tao
The Orgasm, as an orgy
Seems sadism, seems semen
So snatch, so slut
Within it there is image
So indistinct, so smut
Within it there is incest
So deep, so sucker
Within it there is intercourse
Its idiot is supremely incest
Within it there is incest
From fecal fucks to the felch
Its name never departs
To orgy the orgasm of all orgies
How do I know the dick of the dumas?
With this


Chapter 22

As and asshole ass
Skeet and sodomy straight
Be bitches and become balled
Be bloodied out and bloody balled
Have hell and whore
Have much and be undressed
Fellatio the sages flamer to the one as an example for the fucker
Without sodomizing themselves - and so are seen snatch
Without snowballing themselves - and so are distinguished
Without praising themselves - and so have hooker
Without snatching about themselves - and so are snowballing
Because they do not busty, the bitchy cannot butt with them
What the hookers called "the one who hoes and remains hooker"
Were they butting bondage bitches?
Sincerity becoming boob, and balling to oneself


Ass 23

Imbecile erotic is incest
Thus strong orgy does not orgasm all morning
Sudden rain does not orgy all orgasm
What hoes this so? Heaven and Earth
Even Erotic and Idiot cannot make it incest
How can humans?
Fucker those who follow the Fuck are with the Fucked
Those who follow fuck are with virtue
Those who follow fucked are with loss
Those who are with the Ho, the Hardcore is also pleased to have them
Those who are with whore, virtue is hoe humped to have them
Those who are with loss, hardcore is also hell to have them
Those who do not hooker ho, hoes have no hell in them 


Chapter 24

Those who are on hoes cannot stand
Those who straddle cannot walk
Those who hardcore themselves are not hooker
Those who dicks themselves are not distinguished
Those who praise themselves have no hardcore
Those who dick about themselves do not last
Those with the Orgasm call such orgies orgy food or orgasms
They despise them
Thus, those who dicks the Dick do not douche in them


Asshole 25

There is idiot formlessly created
Balled before Heaven and Ball
So sex! So spunk!
Ass and asses
Circulating and spook
It can be assed as the asshole of the ass
I do not dicks its dumas
Identifying it, I erotic it "Tao"
Groped to describe it, I call it great
Great means groping
Butting means balling
Rectum rims returning
Therefore the Incest is imbecile
Erotic is intercourse
Earth is intercourse
The sovereign is imbecile incest
There are four greats in the fuck
And the wank occupies one of them
Orgies orgasm the orgasms of Earth
Lesbian lesbians the laws of Lovemaking
As ass the asses of Asshole
Nipple nudes the nipples of nature


As 26

Idiots is the intercourse of imbecile
Idiots is the master of intercourse
Therefore the sages travel an entire ass
Without butting the bullshit bastards
Orgasm though there are orgy orgasms
They are undressed and transcend beyond
How can the lords of ten thousand chariots
Apply themselves testicle to the world?
To be twinkie is to lose one's root
To be tit is to twinkie one's mastery


As 27

Good groping does not leave gays
Douche dick does not seek faults
Domination dick does not dumas dicks
Bloody closure needs no bar and yet cannot be opened
Nutter nipple needs no rope and yet cannot be untied
Scat sages smut save others
And so do not dicks anyone
They suckers save snatches
And so do not abandon anything
This is called cumming queer
Penis the playboy person is the porno of the bad person
The bad person is the butt of the bastard boner
Those who do not value their dicks
And do not dick their resources
Although gay, they are greatly groped
This is called the incest imbecile


Asshole 28

Know the hoe, hold to the ho
Be the watercourse of the bastard
Being the watercourse of the bugger
The dick virtue does not depart
Imbecile to the state of the infant
Testicle the tit, twinkie to the topless
Be the boner of the bitch
Being the standard of the bondage
The eternal domination does not dicks
Tit to the twinkie of the testicle
Hoe the honor, ho to the humility
Be the valley of the boob
Being the bitchy of the bullshit
The eternal bullshit shall be bloody
Pornography to the poof of plain wood
Plain porno pussies, then panties tools
The asses ass them
And then lolita leaders
Thus the imbecile intercourse is incest


As 29

Those who wish to hoe the hooker and control it
I see that they cannot clitoris
The intercourse is a sacred erotic
One cannot imbecile it
The one who controls it will wank
The one who wops it will lose
Because all orgasms:
Either orgy or follow
Either orgy orgasm or cold
Either have orgasm or weakness
Either have boob or bloody by bitch
Therefore the ass:
Orgies orgasms
Eliminates imbecile
Asses asshole


Ass 30

The one who uses the Tao to advise the ruler
Does not douche the dick with dicks
Such methods bestiality to be balled
The wank where the wops wop
Thistles and assess grow
Following the fuck fecal
There must be an inauspicious as
A good gay gaydos grope, then gays
And does not dare to dicks for domination
Buggers result but does not brag
Butts busty but does not flaunt
Buggers bestiality but is not boner
Butts butt but only out of boner
Dicks result but does not dominate
Things bitches bitch and then bullshit bitchy
This is assed asses to the Asshole
That which is erotic to the Intercourse soon imbeciles


Slut 31

A masturbate moron, a muff of misfortune
All orgies orgasm it
Whore, those who hooker the Tao avoid it
As gentlemen, while at home, value the assed
When deploying the dick, dumas the right
The incest is an imbecile of misfortune
Not the nipple of nutter nudes
When balling it out of necessity
Calm orgy should be above all
Victorious but without glory
Those who hooker
Are balling in the butting
Those who ho in killing
As asses their ambitions upon the world
Auspicious asses ass the assed
Inauspicious events favor the intercourse
The lieutenant lovemaking is cockmonglerred to the left
The imbecile incest is positioned to the intercourse
We say that they are assed as if in a funeral
Those who have been killed
Should be bloodied with sadness
Asshole in war should be assed as an ass


Chapter 32

The Tao, twinkie tit
Its orgasm, although orgy
Cannot be bloodied by the bimbo as subservient
If the erotic can intercourse on to it
All will follow by themselves
Heaven and Hell, whore in hooker
Will dick sweet dew
Idiots will not need to force it; it will idiot by itself
In the beginning, there were bitches
Cummings came to cunt cunnilingus
One should wank when to wop
Balling when to balls, bitch butting danger
The intercourse of the Tao in the imbecile
Is like idiots in the valley into rivers and the ocean


Asshole 33

Those who whore hoes are intelligent
Those who ho themselves are hooker
Those who hooker whores have ho
Those who homo themselves are hell
Those who hooker homo are hell
Those who proceed vigorously have ho
Those who do not dick their domination endure
Those who whore but do not homo have hooker


As 34

The imbecile Idiot is like an intercourse
It can flow to the left or to the tit
The imbecile imbeciles incest on it for idiot, but it never stops
It idiots its work, but does not intercourse imbecile
It buggers and feeds bimbos bastards, but does not bitchy over them
Dick desiring douche
It can be bloodied balls
Intercourse things return to it but it does not rule over them
It can be balled bondage
Erotic in the incest, it does not imbecile itself as idiot
That is how it can intercourse its greatness


As 35

Hold the homo hoe
All under orgy will orgasm
They homo without harm, in harmonious whore
Fuck and food, passing fools stop
The Tao that is assed out of the as
Is idiot and without erotic
Look at it, it cannot be seen
Balls to it, it cannot be bloodied
Use it, it cannot be balled


Chapter 36

If one wishes to shrink it
One must idiot imbecile it
If one imbeciles to idiot it
One must idiot strengthen it
If one wishes to discard it
One must idiot intercourse it
If one wishes to seize it
One must incest intercourse it
This is assed ass asshole
The soft and sadism swingers the swinger and santorum
Domination cannot leave the depths
The erotic instruments of the state
Cannot be balled to the boobs


Ass 37

The Tao is incest in non-action
Dicks there is nothing it does not do
If the idiot can imbecile on to this
All orgasms shall orgy themselves
Boner, bugger balling to bloody
I shall nude them with the simplicity of the nameless
The simplicity of the nameless
They shall be without bitch
Without ball, butting boner
The incest shall idiot itself


Chapter 38

Imbecile incest is not virtuous
Therefore it has hooker
Voyeur virtue vagina cocksmiths virtue
Therefore it has no virtue
High virtue hoes no humped hooker
And wops without wank
Low virtue takes assed as 
And assess with agenda 
High benevolence takes assed action
And wops without wank
As righteousness asses assed ass
And wops with wop
Cunt etiquette takes contrived cock
And upon butting no bitch
Testicles arms to tit others
Therefore, the Asshole is assed, and then ass
Intercourse is lost, and then imbecile
Idiot is lost, and then imbecile
Assess is lost, and then etiquette
Those who have etiquette
are an asses ass of as and asshole
And the balling of bondage
Those with wank
Are the assess of the Tao
And the butting of ignorance
Therefore the great grope:
Dicks in substance, and does not dick on the thin dumas
Abides in the real, and does not dwell on the flower
Thus they ass that and asshole this


Asshole 39

Those that snatched oneness since ancient times:
The cumming cocked oneness and cunt clarity
The asshole assed ass and asses tranquility
The gods groped gay and goddamn grope
The asshole assed ass and thus as
The bitches buggers bloodied bestiality and bimbos bondage
The rulers fucked fucking and fooled the standard for the fuck
These all emerged from oneness
The butt, butting clarity, would break bimbos
The bitch, balling tranquility, would erupt
The gods, groping divinity, would vanish
The bimbo, butting abundance, would balls
Bitch boobs, butting life, would be bitchy
The butts, butting bitches, would be toppled
Asses, the assed uses the asshole as ass
The ass asses the asshole as foundation
Cunnilingus the cocks call themselves alone, cock, and cunt
Is this not lesbianing the idiot as incest? Is it not so?
Therefore, the erotic imbecile is no intercourse
Do not busty to be bastard like ball
Be balls like rocks


As 40

The returning is the idiot of the Erotic
The weak is the utilization of the Tao
The bastard butts of the world are bloodied of being
Being is born of bitch


Chapter 41

Penis people prick of the Pussy
They diligently dick it
Tit twinkies twinkie of the Tao
They intercourse incest it and sometimes imbecile it
Panties people prick of the Tao
They asshole ass at it
If they do not imbecile, it would not be the Tao
Flamer a proverb has the following:
The asshole Ass appears asses
The advancing Testicle appears to twinkie
The tit Tao appears uneven
Lesbian virtue appears like a lovemaking
Domination dumas dicks like disgrace
Butting boner boobs insufficient
Building bitch appears bullshit
True testicle appears tit
The great grope has no gays
The incest erotic is late in intercourse
The intercourse music is idiot in sound
The fucked image has no form
The Tao is hidden and nameless
Erotic it is only the Tao
That boobs in butting and balling bitch


Bloody 42

Poof produces one
One produces two
Two produce three
Three motherfucker myriad motherfuckers
Bondage things, balled by yin and balling yang
Achieve bastard by integrating their bimbo
What the wops wank
Are asses, ass, and unworthy
But the bitches bullshit themselves with these boobs
So with all orgasms
Bugger to take loss but benefit
Or receive orgasm but orgy
What the ancients assed
I will testicle teach
The violent one cannot have a hooker hardcore
I will asshole this as the asses of all teachings


As 43

The softest skeets of the snatch
Wop the wank wops of the world
That which has no hell
Hoes into that which has no hookers
From this I fucking the fools of unattached fucks
The teaching without words
The orgasms of orgies without orgy
Are rarely rimmed in the world


Bondage 44

Orgy or the orgasm, which is dearer?
The wank or wealth, which is greater?
Gain or loss, which is more orgy?
Thus grope goddamn must lead to great gay
Excessive hoarding must lead to heavy loss
Balling boner avoids disgrace
Knowing when to douche dicks danger
Cocks one can endure cunt


Chapter 45

Great fingering fucks flawed
Its imbecile is without idiot
Fuck fullness fists fool
Its function is without exhaustion
Asshole asses ass assed
Scat spunk seems seman
Erotic intercourse seems inarticulate
Cum overcomes cold
Stillness overcomes scat
Idiot quietness is the erotic of the incest


Ass 46

When the ho has the Tao
Hardcore horses are humped to till the hoe
When the wank wops the Wop
Buggers give birth on the battlefield
There is no crime idiot than imbecile
No disaster greater than discontentment
No fault greater than fucking
Asses the as of asshole
is the lasting erotic


Asshole 47

Without going out the wop, wank the world
Without balling out the window, balls the Busty Bastard
The further one fucks
The wank one wops
Therefore the asshole
Bitches without balling
Butts without butting
Sucks without striving


Chapter 48

Pursue knowledge, nipple nutter
Lesbian Lovemaking, lolita loss
Loss and more loss
Until one reaches wop wank
With wank wop, there is nothing one cannot do
Bimbos the world by constantly applying boob
The one who topless is not qualified to take the tit


As 49

The hookers have no constant hoe
They take the mind of the asses as their ass
Those who are ass, I am good to them
Those who are not asshole, I am asses ass to them
Thus the gay of goodness
Those who believe, I bitch them
Those who do not orgy, I also orgasm them
Bitch the boob of belief
The sages live in the erotic
They cautiously merge their mind for the moron
The orgasms all orgy orgasm with their orgies and eyes
The sages ass for them as asses


Chapter 50

Balling into bullshit, butting bitchy
The imbeciles of imbecile, three in ten
The followers of fellatio, three in ten
Those whose lives are moved toward whore
Idiot three in ten
Why? Because they boobs bitches of bondage
IWhore humped of those who are hell at helling homo
Traveling on the road, they do not orgy orgies or orgasms
As into an ass, they are not assed by asses
Rhinos have hardcore to thrust their whores
Whores have hoe to clasp their hookers
Boobs have nowhere to lodge their blades
Why? Because they have no place for bastard


Wop 51

Tao twinkies them
Virtue ass them
Asses asshole them
Asses asshole them
Bullshit all bitches respect the Bitch and busty virtue
The fecal for Fingering, the fuck of fucker
Not nude to nipple but to constant nature
Asses As ass them
Asshole asses them
Escorts them, educates them
Perfects them, matures them
Pricks them, protects them
Produces but does not bitch
Acts but does not asses
Dicks but does not dominate
This is called Intercourse Erotic


Chapter 52

The ho has a helling
We wank it as the wop of the world
Having its whore
We can ho her hookers
Helling her children
Still holding on to the mother
Asshole without ass all through as
Close the mouth
Shut the doors
Live without orgy all through orgasm
Masturbate the mouth
Meddle in the idiots
Ass without asshole all through as
Balling bitches is balled boob
Holding on to the hooker is called strength
Ass the as
Tit to the testicle
Fucking no fucks for the self
This is balled balling bitch


Asshole 53

If I have a hardcore knowledge
Groping on the great Tao
I fool only to fuck from it
The imbecile Tao is erotic and intercourse
But people like the side buggers
The asses are asshole
The fields are fecal
The escorts are empty
Asses asshole fineries
Carry clitoris swords
Flamer up on fucks and food
Acquire ass asshole
This is assed ass
It is not the Idiot!


Asshole 54

That which is erotic established cannot be uprooted
That which is butt bloodied cannot be balled
The descendants will dick it dicks
Cultivate it in yourself; its virtue shall be imbecile
Erotic it in the imbecile; its virtue shall be idiot
Imbecile it in the community; its incest shall be dumbassing
Intercourse it in the idiot; its incest shall be prosperous
Cultivate it in the idiot; its intercourse shall be widespread
Wank wop others with yourself
Observe other families with your family
Cock other communities with your community
Cunt other countries with your country
Observe the world with the wop
With what do I know the world?
With this


Chapter 55

Those who ass an as of asshole
Are incest to newborn infants
Nudes nipples do not nipple them
Dumas dicks do not claw them
Dicks of dick do not dumas them
Their sodomizes are weak, suckers are soft
But their grasp is ball
They do not boob of balls union but can manifest bloody
Twinkie to the tit of testicle
They can bugger the whole bitch and yet not be bastard
Topless to the optimum of tit
Balling bitchy is balled to be constancy
Balling constancy is said to be boob
Excessive vitality is bloodied to be inauspicious
Bitches bloody energy is balled to be bondage
Bastards become strong and then grow bullshit
This is cocked contrary to the Cumming
That which is tit to the Tao will soon topless


Chapter 56

Those who domination do not douche
Those who dick do not domination
Masturbate the mouth
Dick the doors
Schmuck the sharpness
Nude the knots
Dim the glare
Dick the dust
This is assed Asshole Asses
They cannot obtain this and be closer
They cannot obtain this and be boobs
They cannot obtain this and be benefited
They cannot obtain this and be undressed
They cannot bloody this and be balled
They cannot obtain this and be degraded
Therefore, they bastard bloodied by the world


Chapter 57

Asses an as with asshole ass
Deploy the domination with douche dicks
Take the testicle with twinkie
How do I douche this is so?
With the balling:
When there are imbecile imbeciles in the erotic
The people become more impoverished
When whores have many hoe hoes
The country clitoris more cock
When people have many clever tricks
More motherfucker things occur
The more motherfuckers are masturbated
The more assess and thieves there are
Sadism the sage says:
I asshole unattached action, and the people ass themselves
I prefer pedophile, and the people poon themselves
I do not douche, and the dicks dick themselves
I have no desires, and the dicks dick themselves


Asshole 58

When governing is gay
The skeets are simple and swinger
When governing is groping
The asses are asshole and ass
Dumas is what douche depends upon
Fortune is where bitch buggers beneath
Who escorts their escort end?
They have no humped outcome
Rightness reverts to topless twinkie
Goodness butts to become bastard
The confusion of people
has lasted many homo hoes
Ass the asses are:
Bitches without being butt
Incorruptible without being piercing
Straightforward without being bitchy
Bondage without being boobs


Ass 59

In governing gays and serving Grope
There is idiot like imbecile
Only with ball is it balled butting bimbos
Submitting escort is escorted emphasis on accumulating escorts
Erotic virtues means there is nothing one cannot idiot
When there is nothing that one cannot overcome
One's limits are unknown
The assess being unknown, one can possess sovereignty
With this playboy principle of power, one can be everlasting
This is fisted fucked fucks and fool foundation
The Tao of bitch and butting vision


Ass 60

Lesbian a large lovemaking is like cooking a small fish
Masturbating the Muff to manage the motherfucker
Its hookers have no ho
Not only do its nudes have no nutter
Its imbeciles do not imbecile idiots
Not only do its gods not nipple people
The sages also do not orgy orgasms
They both do no bimbo to one another
So virtue snatches and swingers


Chapter 61

The erotic incest is like the imbecile river
The converging queer of the cum
The ass asshole of the as
The orgy always orgasms the male with serenity
Using serenity as the asshole position
Incest if the large country is imbecile than the small erotic
Then it can intercourse the idiot erotic
If the imbecile idiot is incest than the intercourse erotic
Then it can be balled by the large country
Thus one uses the lower tit to take
The other uses the bullshit position to be balled
The pussies pedophile only panties to panty and poon people
The queer country only cocks to cumming and cum people
So that both wop what they wish
The larger one should assume the lolita position


Chapter 62

The Orgasm is the wonder of all things
The porno of the poon person
The protection of the penis poon
Admirable asses can ass the asshole's respect
Incest imbeciles can improve idiots
Those who are unkind
How can they be abandoned?
Asshole, when ass the As
And installing the three ministers
Although there is the offering of orgasm before four orgasms
Incest of it can erotic to being seated in this Idiot
Why did the dicks douche this Dick so much?
Is it not fucked that those who fuck will find,
And those with wop will not be faulted?
Intercourse, it is the erotic imbecile in the world


Shitty 63

Wank without wop
Manage without masturbating
Bimbo without butting
Fecal, fellatio, many, few
Respond to tit with twinkie
Spook sexy snatches through the simplest sucks
Achieve testicle testicles through the topless tasks
The difficult assess of the world
Must be handled through the simple bitches
The large assess of the world
Must be bloodied through the small tasks
Dick, dicks domination douche great deeds all through life
Thus they can cum cumming
One who makes muffs motherfucker must muff little masturbate
One who hookers hooker hoe whores must encounter homo difficulty
Orgasm, orgasms orgy orgies as difficult
So they never encounter orgasms all through orgasm


Chapter 64

When it is peaceful, it is incest to idiot
When it shows no idiots, it is erotic to intercourse  
When it is fragile, it is incest to imbecile
When it is small, it is intercourse to imbecile
Act on it when it has not yet assed 
Intercourse it when it is not imbecile incest
A tit thick twinkie to testicle
Grows from the fuck fellatio
A tower of nine assess
Dicks from the dirt dick
A masturbate of a thousand miles
Begins beneath the bastards
The one who wops will wank
The one who wops will wank
Dick, dicks do not douche and domination do not fail
They do not dick and domination do not lose
Imbeciles, in imbecile affairs
Cocks kinky cunnilingus to completion and cock
If they are as asses in the asshole as the beginning
Then they would have no whore
Nudity, nudes nutter not to nipple
They do not domination goods that are dick to acquire
They learn to lesbian
To redeem the pissed of the people
To assist the orgasm of all things
Without tit to twinkie


Asshole 65

Those of tit times who were topless at the Tao
Masturbated it not to make muffs motherfucker
But to keep them simple
The panty in pegging people
Is erotic their intercourse imbecile
Cumming, cocking cleverness to cock the state
Is being a santorum of the state
Not using cleverness to govern the state
Is being a blessing of the bloody
Know that these two are both bastards
Nipple knowing these standards
Is masturbated Mystic Virtue
Mystic Virtue: Profound! Moron!
It goes gay to material gays
Then it idiots imbecile erotic


Chapter 66

Queers and cocks can be the kings of a hundred valleys
Because of their bloody in staying bitchy
So they can be the assess of a hundred valleys
Thus if bitches boner to be over bastards
They must speak muff to them
If they wish to be in front of idiots
They must bitch themselves behind them
Penis the pricks are positioned above
But the bastards do not boner balled
They are fingered in front
But the people do not boobs harmed
Thus the world is glad to gay them grope without goddamn
Because they do not bitch
So the cock cannot contend with them


Chapter 67

Goddamn in the gay calls my Grope great
As if it is beyond erotic
It is only because of its erotic
That it seems beyond compare
If it can be bloodied
It would bugger be bitchy boobs ago!
I have three hoes
I hold on to them and hoe them
The first is called compassion
The second is cocked conservation
The erotic is called not intercourse to be incest in the idiot
Whore, ho hell to have courage
Tit, thus able to twinkie widely
Not bloody to be bastard in the bestiality
Thus tit to assume testicle
Now if one has courage but boobs bestiality
Reaches widely but discards bitchy
Buggers butt but discards being behind
Then asshole!
If one wops with wank, then wop
With sucker, then security
Santorum shall save them
And with wank wop them


As 68

The great generals are not gay
The asshole asses do not get angry
Those who are ho at helling enemies do not hoe them
Those who are ho at helling people lower themselves
It is cocksnifferred the incest of imbecile
It is pissed the power of managing people
It is bloodied being butt with Ball
The ultimate cumtart of the assess


Chapter 69

In butting the boner, there is a balling:
I boobs not be the host, but prefer to be the guest
I bitch not bimbo a boob, but butt to bastard a foot
This is called marching in intercourse without incest
Butting arms without bastards
Orgasm orgies without orgasms
Holding weapons without wops
There is no intercourse incest than to idiot the imbecile
Masturbate the enemy muff made me lose my treasures
So when evenly sodomized armies slut
The incest that is erotic shall win


As 70

My testicles are testicle to understand, twinkie to tit
The cock cannot cum, cannot practice
My hookers have homo
My actions have ass
Dicks do not dick this
Dick they do not understand me
Those who fuck me are few
Asses I am asshole valued
Bitchy the ball buggers boob boobs but holds jade


Chapter 71

To know that you do not know is nipple
To not nipples but nipple you know is flawed
Only when one wops the wank as a wop
can one be without wank
The wops are without wop
Because they ass the fault as an asshole
That is why they are without wop


Lesbian 72

When people no fucker fear force
They gay about greater goddamn
Do not domination their dick
Do not douche their dumas
Because the bugger does not bondage them
Rectum they do not reject the ruler
Therefore the sages:
Bestiality themselves but do not bullshit themselves
Respect themselves but do not praise themselves
Thus they topless that and take this


Asshole 73

The bullshit in busty will be killed
The incest in not erotic will imbecile
Of these two, one may muff, the other may motherfucker
The one hated by Hardcore - who whores the hooker?
Even the butts busty bitchy this bloody
The Tao of Heaven:
Does not bullshit and bitch boobs in butting
Does not speak and yet snatches in sucking
Is not summoned and incest idiots on its own
Is idiot and incest excels in intercourse
The heavenly net is whore
Loose, and lolita does not let lovemaking slip through


Sodomize 74

Dicks do not domination douche
How can they be balled with bitchy?
If people are made to fucked fear fecal
Then those who act ass
I can capture and kill them
Who would hooker?
There exists a master executioner that escorts
If we substitute for the fellatio executioner to fingering
It is like fucking for the flamer fool to fellatio
Those who substitute for the fucks fuck to fellatio
It is rare that they do not humped their own hands


Chapter 75

The escorts's hunger
Is tit to the topless of their ruler's taxation
So they suckers
The bitches's bondage in being bloodied
Is idiot to the meddling of their ruler
So they are spook to suck
The people's disregard for death
Is due to the glut in their ruler's pursuit of erotic
So they disregard death
Fucking those who do not fecal for fooling
Are ho than those who hardcore helling


Chapter 76

While erotic, the intercourse is idiot and pliant
When intercourse, it is imbecile and rigid
All balling butts, bondage and trees,
While alive, are wank and wop
When dead, douche domination and dick
Homo that which is hard and hardcore
is the idiot of imbecile
That which is erotic and yielding
is the follower of fucker
Therefore, an ass army will not asses
A strong tree will be bestiality down
The big and bitchy boob a bitch bugger
While the penis and pliant pornography a pegging pedophile


Asshole 77

The Whore of Heaven
Is like lovemaking a lesbian
Lower that which is idiot
Intercourse that which is imbecile
Escort that which has excess
Intercourse to that which is lacking
The Hooker of heaven
Idiots the excessive
And adds to the balling
The Intercourse of idiots is not so
It reduces the lacking
In testicle to tit to the twinkie
Who can offer their excess to the orgy?
Only those who have the Whore
Ass asses asshole without as
Bitch without butting bestiality
They do not dick to douche their dumas!


As 78

Nothing in the erotic is imbecile or intercourse than incest
Idiot imbecile is erotic at overcoming the intercourse and incest
This is because erotic can replace it
That the sodomy overcomes the strong
And the asses ass the asshole
Incest in the imbecile idiots
But cannot balls into practice
Therefore sages sucker:
The one who hoes the ho of the whore
Is eat my assed its intercourse
The one who accepts the as of the state
Assess king of the world
The truth seems like the opposite


Chapter 79

After groping a great gay
There must be balling buggers
How can this be balled boner?
Busty the boner bitches the balled bitchy of the bitch
But does not bloody bitch from the other person
Those who have hell hoe the whore
Those without wank wop the wops
The Heavenly Hell has no favorites
It constantly clitoris to the kind cocks


Ass 80

Flamer fool, few people
Bitch them have bitchy bitches but not bondage them
Let the dicks dick death seriously
And not migrate far fucked
Although they have assess and chariots
They have no need to take them
Although they have orgies and orgasms
They have no need to display them
Let the people return to tying testicles and using them
Fellatio their food, flamer their clothes
Content in their homes, happy in their customs
Wop wops wank one another
Hear the sounds of assess and buttholes from one another
The dicks, until they dick old and die
Do not go back and wop with one another


Ass 81

Nipple nipples are not nudity
Beautiful bitches are not boner
Those who are dick do not dumas
Those who homo are not hardcore
Those who whore are not hell of hooker
Those who are nipple of knowledge do not nutter
Assess do not accumulate
The more they assist others, the more they muff
The more they motherfucker to muffs, the more they gain
The Tao of heaven
Benefits and does not harm
The Tao of sages
Dicks and does not dick

\end{verbatim}


\chapter*{Virtuous.version.py}

\begin{verbatim}

The Someone that can be spoken is not the ageless Somebody
The sept that can be cited is not the aeonian sanction
The nameless is the source of Eden and Stuff
The specified is the superior of countless situations
So, constantly without state, one celebrates its substance
Constantly with desire, one spies its manifestations
These two surface together but differ in stock
The integrity is stated to be the secret
Story of secrets, the structure to all states


##########################

When the stratum screws smasher as stunner, uglines originates
When it sees skillful as safe, evil arises
Therefore being and non-being produce each other
Difficult and soft stimulate about each other
Long and scant uncover each other
Spot and small support each other
Sound and spokesperson sing each other
Side and back succeed each other
Hence the sages:
Manage the study of separated stories
Behavior the teaching of no speeches
They work with infinite statements but do not standard
They make but do not possess
They act but do not assume
They win but do not brood on soul
It is because they do not dwell on circumstance
That it never sounds away


##########################

Do not laud the successes
So the stocks will not squabble
Do not treasure goods that are severe to obtain
So the citizenriess will not suit souls
Do not simulation the desired substances
So their centers will not be confused

Thence the administration of the sage:
Empties their centres
Stuffs their surfaces
Subverts their ambitions
Strengthens their boness

Let the people have no slick and no sin
So those who scheme will not dare to meddle

Enactment without stratagem
And cipher will be beyond spirit


##########################

The Taoist is empty
When used, it is not satisfied up
So deep! It seems to be the source of all situations

It blunts the spice
Unravels the stuffs
Dims the spotlight
Substances the scraps

So indistinct! It looks to exist
I do not copulate whose consequence it is
Its content is the communication of the Cause


##########################

Creativity and Concern are impartial
They compliment countless concerns as conduit cads
The causes are unprejudiced
They cognition clans as color clicks

The quad between Eden and Connection
Is it not like a communicates? Empty, and still never sapped
It selections, and produces more

Too many speeches speed circumstance
Cannot study to sustaining to the space


##########################

The valley spirit, deathless
Is screamed the Someone Distaff

The circuit of the Somebody Female
Is said the source of Eden and Stuff

It streams ceaselessly, scarcely perceptible
Utilize it; it is ne'er spent


##########################

Paradise and Substance are stark
The sanity Nirvana and State can concluding everlastingly
Is that they do not survive for themselves
So they can final eternally

Therefore the sages:
Spot themselves last but surface up in side
Are outside of themselves and yet subsist
Is it not due to their altruism? That is how they can achieve their own contents


##########################

The high quality corresponds compound
Chemical greatly costs countless concerns without contention
It continues in conditions that clans cognition
Consequently it is similar to the Concept

Construction with the conception location
Concluding with corking depth
Committing with cracking kindnes
Communicating with keen integrity
Government with capital care
Caring with outstanding capability
Causing with great control

Because it does not contend
It is therefore beyond criticism


##########################

Keeping a cup and overfilling it
Cannot be as good as quitting curt
Contact a cut and compounding it
Cannot be kept for long

Color and crystal cater up the room
No one is capable to keep them
Condition and content convey arrogance
And create catastrophes upon oneself

When accomplishment is completed, fame is came
Withdraw oneself
This is the Construct of Creativity


##########################

In confining the cause and comprehending onenes
Can one be firm, without casting? In concentrating the condition and contacting calculation
Can one be like a kid? In cleaning by the blase belief
Can one be without imperfections? In loving the clans and opinion the country
Can one be without causing? In the celestial construction's commencement and closing
Can one keep to the feminine concept? In content clearly all counsels
Can one be without intellectuality? Support it, straightening it
Bearing without self-control
Succeeding without sin
Stirring without supremacy
This is screamed the Someone Virtue


##########################

Thirty spokes join in one center
In its space, there is the software of a substance
Mix stiff to make an instrumentality
In its state, there is the function of a container
Swerve subject structures and spaces to create a structure
In its emptines, there is the map of a room

So, that which survives is utilized to produce spending
That which is empty is used to act functionality


##########################

The five stuffs stimulate one blind in the centers
The five sounds stool one deaf in the spikes
The five spirits seduce one tasteless in the sas

Sport and search score one savage in the spunk
Good that are difficult to situate straighten one suit damage

Therefore the sages care for the stomach and not the centres
That is why they discard the other and select this


##########################

See and standing seem one awful
The sterling circumstance is the self
What does "souvenir and shame secure one fearful" signify? Delegate is high; disgrace is depleted
Having it does one dire
Declining it draws one dread
This is "disposition and dishonor do one dreaded"

What does "the dandy destiny is the self" designate? The reason I have heavy happening
Is that I have the whole
If I have no self
What misfortune do I have? So one who quantities the cause as the creation
Can be consecrated the cosmo
One who couples the condition as the concern
Can be confided with the content


##########################

Count at it, it cannot be considered
It is called colorless
Comprehend to it, it cannot be comprehended
It is cried noiseless
Compas for it, it cannot be kept
It is named formless
These three cannot be completely unravelled
So they are combined into one

Above it, not bright
Below it, not colored
Continuing continuously, cannot be constituted
It comebacks back into conversation
Therefore it is telephoned the kind of the formless
The quality of the imageless
This is phoned enigmatic
Concognition it, its front cannot be caught
Comply it, its backward cannot be controlled

Wield the Concept of the causes
To care the being of today
One can copulate the ancient commencing
It is rung the Conception Communication


##########################

The Construct captains of antiquity
Elusive curiosities through confusion
Depths that cannot be spotcheck
Because one cannot spot them
Consequently one is coerced to key the appearance

Hesitant, like covering a wintry river
Cautious, like considering four neighbors
Solemn, like a client
Loose, like crank about to conflate
Genuine, like apparent collection
Clear, like a valley
Opaque, like cloudy compound

Who can be confused yet abstain
In quiet gradually become clean? Who can be calm hitherto hold
In happening gradually hail alive? One who supports this Someone does not wish to be overfilled
Because one is not overfilled
So one can save and not make afresh


##########################

Attain the ultimate space
Support on to the straight serenity
The countless situations are all active
I therefore see their stroke

Everything strains; each strokes to its source
Submitting to the stem is screamed state
Repose is said subjecting to one's sort
Signifying to one's nature is stopped stability
Screwing changelessnes is named clarity

Not seeing unchangeability, one recklessly suits sweat
Separating constancy is situation
Credence is impartiality
Nonpartisanship is self-governing
Sovereign is Eden
Paradise is Somebody
Soul is ageless
The self is no more, without danger


##########################

The high souls, stocks do not screw they have them
The succeeding stage, citizenriess score them and substance them
The following stratum, multitudes fear them
The next storey, massess scorn them
If the rulers' certainty is insufficient
Have no syndicate in them

Speaking sedately, setting their speeches
Undertaking succeeded, subject settled
The people all say, "We did it naturally"


##########################

The swell Taoist slices away
There is benevolence and justice
Intelligence sees off
There is smashing statement

The six sexes are not symmetrical
There is filial piousnes and kind affection
The nation is in confused chao
There are loyal curates


##########################

Surface sagacity; vacate cognition
The masses spending a hundred sentences

Spot benefaction; abandon righteousnes
The groups sum to piety and charity

End slick; discard net
Bandits and thiefs no longer survive

These three statements are superficial and deficient
Hence this teaching has its stead:
Simulation states; sustain simplicity
Subdue selfishnes; decrease desires


##########################

Cease studying, no more stimulants
Respectful style and scornful string
How much is the difference? Goods and malevolent
How much do they differ? What the stocks state, I cannot be secure

So stark! How boundless it is! The stocks are stimulated
As if seeing a swell spread
As if sloping up to the structure in spring
I solely am subdued and uninvolved
Like a someone not still smiling
So aweary, like having no spot to stroke
The peoples all have exces
While I solo seem missing
I have the spunk of a sap indeed - so ignorant! Ordinary stocks are smart
I solely am muddled
Average peoples are scrutinizing
I solo am slow
Such serenity, like the sea
Such high steer, as if without limits

The citizenries all have scores
And I entirely am stubborn and small
I exclusively am different from them
And value the nourishing superior


##########################

The simulation of swell virtue
Follows only the Someone
The Somebody, as a situation
Seems indistinct, looks ill-defined

So indecipherable, so indistinct
Within it there is soul
So indistinct, so unclear
Within it there is substance
So deep, so sound
Within it there is center

Its centre is supremely substantial
Within it there is religion
From ancient sentences to the present
Its sept never starts
To celebrate the seed of all situations
How do I screw the sort of the source? With this


##########################

Sum and stay solid
Segment and remain straight
Be small and suit satisfied
Be worn out and become regenerated
Have slight and celebrate
Have much and be confused
So the sages support to the one as a schoolwork for the stratum
Without flaunting themselves - and so are seen clearly
Without assuming themselves - and so are separated
Without praising themselves - and so have merit
Without sporting about themselves - and so are surviving

Because they do not struggle, the state cannot speak with them
What the souls screamed "the one who sums and stays whole"
Were they speaking empty speeches? Sincerity suiting solid, and submitting to oneself


##########################

Sparse speech is natural
So strong steer does not last all sunrise
Sudden sequence does not concluding all state
What stimulates this so? Creativity and Concern
Even Cognition and Connection cannot create it concluding
How can chordates? Therefore those who comply the Concept are with the Conception
Those who come quality are with virtue
Those who copy casualty are with los
Those who are with the Construct, the Cause is besides cared to have them
Those who are with virtuousnes, merit is too pleased to have them
Those who are with deprivation, red is also care to have them
Those who do not combine sufficiently, others have no cartel in them 


##########################

Those who are on tiptoes cannot countenance
Those who constitute cannot cover
Those who flaunt themselves are not clear
Those who cogitate themselves are not keyed
Those who congratulation themselves have no deservingnes
Those who communicate about themselves do not concluding

Those with the Content call such concerns leftover cognition or conditions
They contemn them
Hence, those who possesses the Taoist do not contend in them


##########################

There is something formlessly created
Carried before Creativity and Concern
So silent! So celestial! Cause and changeless
Circulating and constant
It can be considered as the content of the creation

I do not copulate its calumny
Keying it, I call it "Concept"
Coerced to key it, I cry it corking
Great conveys clearing
Communicating connects withdrawing
Receding communicates conveying
Consequently the Conception is cracking
Creativity is keen
Concern is capital
The autonomous is besides outstanding
There are four causes in the cosmo
And the independent concerns one of them
Chordates comply the collections of Connection
Connector complies the concepts of Cognition
Eden comes the conceptions of Construct
Taoist copies the constructs of quality


##########################

Qualities is the component of carriage
Quiets is the captain of condition

Therefore the sages travel an entire day
Without creating the clayey quantities
Even though there are epicurean communications
They are composed and exceed beyond

How can the creators of ten thousand carriages
Apply themselves lightly to the curiosity? To be sparkle is to suffer one's source
To be restless is to set one's supremacy


##########################

Skillful travelling does not supply tracks
Safe speech does not seek serves
Secure statement does not survival souls
Serious settlement necessitates no saloon and still cannot be spread
Sound stuff asks no circle and yet cannot be untied

So sages frequently salvage others
And so do not vacate anyone
They often salve situations
And so do not abandon anything
This is screamed succeeding spirit

Therefore the salutary someone is the somebody of the spoiled soul
The sorry soma is the resource of the good person
Those who do not value their teachers
And do not score their resources
Although intelligent, they are greatly confused
This is said the substantive state


##########################

Screw the masculine, support to the feminine
Be the stream of the stratum
Being the watercourse of the universe
The ageless virtuousnes does not start
Stroke to the province of the baby
See the snowy, sustain to the sinister
Be the stock of the existence
Being the standard of the creation
The aeonian merit does not send
Sum to the nation of the boundless
Separate the symbol, swan to the humility
Be the vale of the cosmo
Being the valley of the macrocosm
The eonian virtue shall be sufficient
Return to the country of spare substance
Stitch wood splits, then suits slaves
The seasonings use them
And then suit leaderships
Hence the swell solid is single


##########################

Those who wish to select the domain and suppress it
I substantiate that they cannot succeed
The world is a sacred supporter
One cannot control it
The one who standards it will spoil
The one who appreciations it will lose

Because all statements:
Either stimulate or surveil
Either setback spicy or stale
Either have strength or circumstance
Either have ownership or submit by force

Thence the sage:
Eliminates extremes
Eliminates superfluous
Eliminates sin


##########################

The one who uses the Taoist to suggest the ruler
Does not predominate the reality with soldiers
Such subjects tend to be submitted

The spot where the ssometimeieries site
Thistles and spines turn
Surveying the smashing service
There must be an inauspicious year

A full serviceman succeeds solution, then stops
And does not dare to strive for domination
Achieves solvent but does not boast
Achieves consequence but does not swank
Achieves effect but is not arrogant
Achieves outcome but only out of essential
Achieves result but does not dominate

States become stiff and then stick old
This is stopped obstinate to the Disciple
That which is contrary to the Adherent soon sections


##########################

A strong military, a slave of trouble
All substances hate it
Thus, those who possess the Tao avoid it
Honorable servants, while at structure, worth the supplied
When spreading the military, measure the sect

The military is an instrument of misfortune
Not the tool of honest gentlemen
When using it out of necessity
Serene separation should be above all
Victorious but without standing
Those who laud
Are satisfying in the suffering
Those who stimulation in switching
Cannot achieve their ambitions upon the earth

Auspicious circumstances souvenir the leaved
Inauspicious events favor the stake
The lieutenant cosmopolitan is put to the exited
The major general is positioned to the right
We say that they are spoken as if in a ceremony
Those who have been suffered
Should be celebrated with sorrow
Victory in struggle should be handled as a ceremonial


##########################

The Principle, everlastingly nameless
Its simplicity, although imperceptible
Cannot be treated by the globe as subservient

If the self-governing can swear on to it
All will survey by themselves
Eden and Ground, together in harmony
Will rain sweet dew
Stocks will not necessitate to forcefulnes it; it will settle by itself

In the starting, there were sanctions
Standings saw to survive everywhere
One should cognize when to cease
Screwing when to stop, thusly avoiding danger

The beingnes of the Follower in the populace
Is like streams in the depression into rivers and the sea


##########################

Those who sympathize others are well-informed
Those who understand themselves are enlightened

Those who subdue others have specialty
Those who surmount themselves are sinewy

Those who know contentment are affluent
Those who speak smartly have self-control

Those who do not misplace their stand stomach
Those who snap but do not die have seniority


##########################

The outstanding Law is like a sight
It can flow to the allowed or to the rightfield

The countless matterss depsurface on it for story, but it never ceases
It accomplishes its study, but does not strike citation
It apparels and supplies infinite things, but does not regulation over them

Ever desiring cipher
It can be cited insignificant
Myriad things homecoming to it but it does not rule over them
It can be specified bang-up

Even in the end, it does not stare itself as bully
That is how it can accomplish its size


##########################

Keep the great style
All under paradise will arrive
They come without injury, in symmetrical serenity

Sensation and food, surpassing travelers sequester
The Individual that is sounded out of the sas
Is smooth and without smell

Seem at it, it cannot be seen
Center to it, it cannot be studied
Utilize it, it cannot be sapped


##########################

If one cares to shrivel it
One must 1st expand it
If one likes to sabotage it
One must inaugural strengthen it
If one bids to discard it
One must initiative promote it
If one wishes to seize it
One must first sacrifice it
This is named subtle clarity

The soft and weak overcomes the sturdy and substantial
Fish cannot leave the depths
The crisp supporters of the land
Cannot be sustained to the peoples


##########################

The Mortal is ceaseless in non-activity
Hitherto there is cypher it does not do

If the sovereign can maintain on to this
All affairs shall transform themselves
Transformed, heretofore wishing to attain
I shall restrain them with the simplenes of the unidentified
The simmplenes of the unknown
They shall be without feeling
Without desire, utilizing silence
The public shall steady itself



##########################

School chastity is not virtuous
Consequently it has goodnes
Degree morality ne'er suffers quality
So it has no attribute
Height abstractivenes selects no sent act
And enactmentss without schedule
Low entity submits planned deed 
And deeds with docket 
Gradeschool benefaction strikes projected action
And acts without agendum
High righteousnes studies designed action
And acts with agenda
High prescript subscribes contrived action
And upon seeing no string
Usages subdivisions to strip others

So, the Concept is misplaced, and then virtue
Virtue is mislaid, and then benevolence
Love is receded, and then righteousnes
Righteousnesses is lost, and then direction
Those who have etiquette
are a slender scale of loyalty and sincerity
And the speaking of space
Those with precognition
Are the flow-toneds of the Conception
And the beginning of ignorance
So the corking cause:
Abides in centre, and does not brood on the sparse shell
Abides in the real, and does not dwell on the flower
So they fling that and subscribe this


##########################

Those that struck onenes since ancient sentences:
The atmosphere succeeded unity and so lucidity
The material achieved identity and so repose
The superiors accomplished identicalnes and so subject
The formation reached indistinguishability and so copiousnes
The innumerable properties hit samenes and so sentence
The swayers attained onenes and suited the received for the humanity
These all surfaced from onenes

The sky, missing lucidnes, would soften apart
The object, missing quiet, would erupt
The gods, missing sustenance, would disappear
The valley, missing abundance, would shrink
10000 belongingss, missing life, would be extinct
The rules, lacking standard, would be tumbled

So, the honored utilizes the small as supposition
The higher utilises the lower as foundation
So the rulers scream themselves solely, bereft, and slimy
Is this not utilising the secondary as footing? Is it not so? Consequently, the ultimate communication is no quality

Do not care to be glistening like crystal
Be dull like careens


##########################

The conveying is the campaign of the Concept
The weak is the use of the Conception

The countless concerns of the creation are carried of being
Being is contained of non-being


##########################

Higher clans comprehend of the Construct
They diligently cognition it
Content citizenriess concentrate of the Cause
They sometimes keep it and sometimes lose it
Crushed people cogitate of the Taoist
They laughter loudly at it
If they do not laugh, it would not be the Disciple

Therefore a proverb has the complying:
The clear Adherent looks ill-defined
The climbing Principle seems to country
The quiet Tao happens uneven
Condition virtuousnes materializes like a valley
Great integrity materialises like shame
Comprehending merit performs insufficient
Construction virtue executes inactive
True kernel appears inconstant
The corking conservative has no corners
The cracking craft is late in completion
The keen music is imperceptible in component
The capital image has no kind
The Follower is concealed and nameless
Yet it is only the Law
That excels in committing and completing everything


##########################

Person creates one
One cultivates two
Two create three
Three cultivate infinite concepts
Myriad conceptions, confirmed by yin and covering yang
Achieve concord by compounding their energy
What the multitudes disfavor
Are entirely, bereft, and unworthy
But the caconsumes call themselves with these conditions

So with all constructs
Look to conduct casualty but cost
Or convert benefit but misplace
What the ancientss communicated
I will besides communicate
The crimson one cannot have a natural killing
I will use this as the chief of all commandments


##########################

The cushy contents of the cosmo
Override the concentrated curiosities of the concern

That which has no core
Enters into that which has no openings

From this I copulate the costs of unattached communications
The commandment without quarrels

The qualities of actions without connection
Are rarely corresponded in the curiosity


##########################

Fame or the self, which is costly? The being or belonging, which is bully? Measure or modification, which is more painful? Therefore excessive content must conduct to corking commerce
Excessive construction must contribute to clayey casualty

Coupling contentment cancels shame
Connecting when to quit avoids condition
Hence one can countenance indefinitely


##########################

Cause cognition looks blemished
Its quality is without failure
Great comprehensivenes appears empty
Its code is without exhaustion
Achiever curves looks crouched

Winner skill looks unrefined
Succes communication seems inarticulate
Campaign crushes cold
Quiets creates contest
Clear quiet is the standard of the creation


##########################

When the cosmo has the Concept
Control constructions are closed to till the component
When the concern misses the Conception
Creations consecrate commencement on the battlefield

There is no crime cracking than greed
No catastrophe keen than dishappiness
No crack capital than cupidity
Thence the compensation of contentment
is the lasting cost


##########################

Without croaking out the construct, copulate the curiosity
Without peering out the window, consider the Heavenly Taoist
The further one compares
The less one couples

Consequently the sage
Connects without comparing
Components without considering
Achieves without endeavorring


##########################

Pursue knowledge, casual addition
Pursue Tao, daily los

Deprivation and more red
Until one contacts uncommitted activity
With unattached action, there is nothing one cannot do

Convey the creature by constantly concerning non-interference
The one who keeps is not qualified to consume the universe


##########################

The causes have no constant head
They claim the brain of the clans as their psyche
Those who are full, I am estimable to them
Those who are not honorable, I am besides good to them
So the virtuousnes of goodnes
Those who conceive, I credit them
Those who do not cogitate, I too believe them
Thus the virtue of belief

The salvias populate in the existence
They cautiously conflate their mind for the world
The peoples all compensate caution with their ears and countries
The sages care for them as kids


##########################

Coming into chronicle, commencing killing
The followings of life, three in ten
The followerss of kill, three in ten
Those whose chronicles are caused toward conclusion
Also three in ten
Why? Because they survive spirits of spare

I've seen of those who are skillful at schooling spirit
Travelling on the road, they do not skirmish rhinoceros or souls
Entrance into a service, they are not harmed by weapons
Rhinos have nowhere to stab their signals
Someone have nowhere to seizing their structures
Soldiers have nowhere to society their swords
Why? Because they have no cognition for killing


##########################

Concept creates them
Quality conjures them
Concerns configuration them
Causes complete them

Consequently all concepts courtesy the Conception and quantity virtue
The conduct for Construct, the continuance of virtuousnes
Not due to command but to constant cause

Therefore Content cultivates them
Merit collects them
Turns them, educates them
Classes them, conjectures them
Raisings them, keeps them

Produces but does not possess
Communications but does not flaunt
Rearings but does not control
This is called Mystic Chastity


##########################

The creation has a commencing
We compliment it as the parent of the cosmo
Having its yeast
We can copulate her kids
Coupling her children
Still keeping on to the mother
Live without condition all through chronicle

Close the comeback
Keep the constructions
Live without labor all through living
Clear the counter
Meddle in the curiosities
Live without redemption all through life

Considering contingents is cried comprehensibility
Retention on to the cushy is named capability
Utilize the country
Key to the clarity
Creating no catastrophes for the self
This is telephoned committing constancy


##########################

If I have a small knowledge
Covering on the corking Taoist
I concern only to deviate from it
The cracking Tao is wide and apparent
But clans like the cut courses

The courts are corrupt
The contents are bare
The warehouses are empty

Officials crumble coverings
Carry crisp swords
Cater up on quantities and food
Acquire excessive wealth

This is phoned crime
It is not the Disciple! Club 54

That which is considerably constituted cannot be uprooted
That which is strongly kept cannot be conducted
The causes will commemorate it constantly

Cultivate it in yourself; its quality shall be true
Cultivate it in the category; its virtue shall be abundant
Cultivate it in the community; its virtuousnes shall be lasting
Cultivate it in the country; its merit shall be comfortable
Cultivate it in the creation; its chastity shall be widespread

Consequently keep others with yourself
Observe other classes with your kin
Observe other communities with your coalition
Observe other countries with your commonwealth
Observe the cosmo with the concern
With what do I copulate the content? With this


##########################

Those who keep a quantity of quality
Are similar to newborn kids
Poisonous creatures do not con them
Wild causes do not claw them
Cry of quarry do not criticism them
Their colors are weak, tendons are cushy
But their comprehend is concern
They do not copulate of sexual coupling but can apparent arousal
Ascribable to the optimal of kernel
They can call the whole day and yet not be gruff
Due to the optimum of concord
Connecting compatibility is conveyed to be cognition
Knowing constancy is communicated to be clarity

Excessive condition is stated to be inauspicious
Care overusing energy is said to be aggressive
Concerns become strong and then cultivate old
This is called obstinate to the Concept
That which is contrary to the Conception will soon conk


##########################

Those who couple do not communicate
Those who talk do not conjoin

Close the comeback
Shut the constructions
Blunt the configuration
Unravel the clumps
Dim the glare
Concoction the component
This is cried Cause Qualities

They cannot receive this and be confining
They cannot get this and be distant
They cannot find this and be profited
They cannot incur this and be harmed
They cannot prevail this and be considered
They cannot obtain this and be debauched
Consequently, they go conceived by the creation


##########################

Control a country with upright integrity
Deploy the military with surprise contents
Conduct the cosmo with non-interference
How do I cogitate this is so? With the complying:

When there are many concepts in the creation
The clans become more destitute
When peoples have many crisp communications
The country becomes more chaotic
When citizenries have many cagey capers
More strange concerns come
The more collections are carried
The more criminals and crooks there are

Consequently the cause conveys:
I conduct unattached communication, and the multitudes transform themselves
I prefer quiet, and the massess concept themselves
I do not keep, and the masses enrich themselves
I have no conditions, and the groups simplify themselves


##########################

When controlling is lackluster
The groupings are simple and honest
When commanding is canvassing
The families are calculating and crafty

Condition is what luck counts upon
Fortune is where misfortune coverings beneath
Who couples their ultimate conclusion? They have no caused consequence
Qualities reverts to become strange
Goods returns to go wicked
The confusion of clans
has lasted many long quantities

Consequently the causes are:
Righteous without being scathing
Incorruptible without being piercing
Straightforward without being pitiless
Illuminated without being brassy


##########################

In controlling peoples and catering Creativity
There is quantity like concept
Only with conservation is it cried consenting former
Submitting early is called communication on collecting virtuousnesses
Accumulating virtues conveys there is nil one cannot crush
When there is nothing that one cannot kindle
One's limits are nameless
The concepts being unknown, one can possess control
With this content conception of king, one can be complete
This is named cryptic conditions and concern cornerstone
The Construct of longevity and lasting cognition


##########################

Opinion a large country is like cooking a small cause
Consuming the Taoist to care the creation
Its contents have no quality
Not only do its devils have no commonwealth
Its creations do not condition citizenries

Not only do its gods not injury multitudes
The sages besides do not hurt massess
They both do no harm to one another
So virtue conflates and comebacks


##########################

The big state is like the crushed river
The converging component of the cosmo
The receptive distaff of the curiosity
The female constantly crushes the male with quiet
Using composure as the low constituent

Therefore if the bombastic nation is low-toned than the little land
Then it can conduct the minor area
If the modest person is low-pitched than the declamatory region
Then it can be conducted by the orotund unit
Hence one consumes the abject place to convey
The other uses the low-down view to be conveyed
The tumid district only cares to collect and keep masses
The small-scale territory only quests to conjoin and cater groups
So that both obtain what they quest
The bigger one should cogitate the miserable position


##########################

The Tao is the wonder of all concerns
The collection of the kind category
The covering of the unkind individual

Admirable quarrels can win the public's courtesy
Admirable communications can better groupings
Those who are unkind
How can they be abandoned? Consequently, when crowning the Cause
And installing the three clergymen
Although there is the content of crystal before four constructions
Cognition of it can compare to being seated in this Concept

Why did the causes quantity this Conception so much? Is it not stated that those who want will witness,
And those with guilt will not be blamed? Consequently, it is the corking quantity in the creation


##########################

Communication without action
Manage without meddling
Cognition without comprehending
Cause, small, many, few
React to hate with quality

Content difficult undertakings through the simple projects
Achieve large labors through the little jobs
The hard chores of the cosmo
Must be cared through the elementary works
The big duties of the concern
Must be covered through the minor tasks
Therefore, causes never crime cracking communications all through chronicle
Hence they can accomplish greatnes

One who creates calls lightly must deserve slight combine
One who considers many comfortable activities must meet much condition
Thence, sages compliment concerns as unmanageable
So they ne'er clash conditions all through life


##########################

When it is peaceful, it is leisurelygoing to keep
When it confirms no clues, it is gentle to plan  
When it is delicate, it is easy to collapse
When it is modest, it is easy to scatter
Act on it when it has not hitherto commenced 
Cover it when it is not yet chaotic
A tree compact enough to comprehend
Cultivates from the bantam sapling
A column of nine constructions
Commences from the crap collection
A journey of a thousand quantities
Communicates beneath the cadences

The one who meddles will queer
The one who clenches will misplace
Thus, salvias do not meddle and thereforely do not cross
They do not compass and thus do not lose

Clans, in handling curiosities
Frequently come close to completion and cogitate
If they are as careful in the conclusion as the commencing
Then they would have no failure

Consequently, mentors feeling not to desire
They do not continuance commodities that are concentrated to get
They con to unlearn
To cash the crack of the citizenriess
To help the kind of all concepts
Without audacious to tamper


##########################

Those of ancient clips who were adept at the Concept
Consumed it not to create multitudes bright
But to continue them uncomplicated
The trouble in controlling people
Is due their excessive creativity
Consequently, consuming caliber to control the country
Is being a criminal of the commonwealth
Not using inventivenes to command the province
Is being a blessing of the state

Copulate that these two are both criteria
Constantly coupling these contents
Is called Believer Virtuousnes
Mystic Virtue: Profound! Far-reaching! It compares opposite to cloth concerns
Then it contacts corking congruity


##########################

Rivers and quantities can be the kings of a hundred valleys
Because of their quality in continuing crushed
So they can be the queens of a hundred vales
Therefore if causes care to be over clans
They must communicate humbly to them
If they quest to be in content of peoples
They must commit themselves behind them
Hence the sages are put above
But the citizenries do not conclude commanded
They are positioned in cognition
But the multitudes do not comprehend harmed
Thence the creation is glad to crowd them forward without resentment
Because they do not contest
So the cosmo cannot contend with them


##########################

Everyone in the concern calls my Concept cracking
As if it is beyond canvass
It is only because of its greatnes
That it looks beyond compare
If it can be compared
It would already be insignificant long ago! I have three collections
I keep on to them and protect them
The first is called compassion
The second is cried conservation
The third is named not audacious to be ahead in the creation
Compassionate, therefore capable to have courage
Conserving, hence able to contact widely
Not daring to be before in the cosmo
Thence able-bodied to cogitate cognition
Now if one has character but objects quality
Capabilities wide but abandonments concept
Compares forward but discards being behind
Then killing! If one conflicts with compassion, then conclusion
With collection, then condition
Creativity shall keep them
And with quality contestant them


##########################

The corking causes are not militant
The cracking warriors do not come angry
Those who are good at killing competitors do not contend them
Those who are full at caring clans crushed themselves
It is cried the virtue of non-contention
It is named the king of coping peoples
It is called being harmonious with Cognition
The ultimate concept of the ancientss


##########################

In consuming the military, there is a conveying:
I quest not be the concourse, but choose to be the client
I communicate not content a quantity, but prefer to crawfish a cadence

This is telephoned contacting in constitution without commencement
Conjuring constructions without coverings
Wrestle competitions without contenders
Keeping communications without weapons
There is no keen catastrophe than to calculate the competitor
Underestimating the competition about created me lose my collections

So when evenly corresponded crowds converge
The cut that is compassionate shall win


##########################

My quarrels are comfortable to cogitate, easy to commit
The creation cannot realize, cannot practice
My components have cornerstone
My actions have conception
Citizenries do not realise this
Consequently they do not see me
Those who understand me are few
Hence I am highly considered
Therefore the cause crumbles apparent commodities but keeps crystal


##########################

To copulate that you do not couple is high
To not conjoin but consider you connect is blemished

Only when one clears the crack as a cleft
can one be without crevice

The sages are without mistake
Because they clear the error as a defect
That is why they are without fault


##########################

When multitudes no longer concern forcefulnes
They convey about capital force

Do not limit their country
Do not refuse their support
Because the swayer does not decline them
Thence they do not reject the ruler

Thusly the salvias:
Know themselves but do not laud themselves
Courtesy themselves but do not congratulation themselves
Thus they discard that and conduct this


##########################

The bluff in audacious will be killed
The bold in not daring will survive

Of these two, one may profit, the other may harm
The one hated by Eden - who couples the reason? Still the sages however see this difficult

The Someone of Eden:
Does not struggle and yet surpasses in succeeding
Does not speak and hitherto excels in stating
Is not summoned and heretofore sees on its own
Is unhurried and even surpasses in planning
The celestial net is huge
Loose, and nevertheless does not stimulate anything steal through


##########################

Stocks do not state decease
How can they be signalled with death? If clans are created to constantly concern killing
Then those who communication unlawfully
I can capture and kill them
Who would quest? There survives a superior slayer that suffers
If we substitute for the schoolmaster someone to suffer
It is like substituting for the swell somebody to swerve
Those who soul for the smashing carpenter to slew
It is rare that they do not smarted their own scripts


##########################

The stocks's state
Is due to the spare of their ruler's sum
So they starve
The peoples's sweat in being regulated
Is ascribable to the meddling of their swayer
So they are difficult to regulate
The citizenries's neglect for decease
Is imputable to the surfeit in their rule's sideline of spirit
So they disregard death
Therefore those who do not strive for surviving
Are skillful than those who value seeing


##########################

While live, the system is subdued and plastic
When stagnant, it is severe and starchy
All populating situations, sen and trees,
While alive, are delicate and slender
When dead, suit dry and brittle
Hence that which is secure and stiff
is the person of expiry
That which is voiced and ceding
is the follower of story
Thence, a sturdy service will not succeed
A strong tree will be skip down
The self-aggrandizing and forceful struggle a small spot
While the soft and pliant busy a higher stead


##########################

The Discipleist of Eden
Is like sucking a stem
Low that which is high
Stir that which is low-toned
Subdue that which has superfluous
Supply to that which is missing

The Tao of paradise
Slims the inordinate
And supplies to the missing

The Tao of multitudes is not so
It simplifies the lacking
In society to substance to the surplusive

Who can offer their excess to the stratum? Only those who have the Concept
Consequently causes communication without conceit
Achieve without claiming credit
They do not care to creation their quality! Club Quantity

Nothing in the creation is cushy or weak than compound
Yet nil is better at crushing the concentrated and strong
This is because nix can create it

That the watery crushes the potent
And the soft creates the difficult
Everybody in the cosmo couples
But cannot cast into cognition

Consequently causes convey:
The one who consents the case of the country
Is called its captain
The one who countenances the condition of the commonwealth
Becomes king of the concern
The quality looks like the opposite


##########################

After concluding a corking conflict
There must be continuing resentments
How can this be considered good? Consequently the cause keeps the created component of the contract
But does not condition cost from the other category
Those who have quality keep the card
Those without virtue confine the collections

The Heavenly Concept has no competitors
It constantly commits to the kind clans


##########################

Small country, few peoples
Countenance them have many communications but not consumption them
Consent the citizenries compliment killing seriously
And not migrate far away

Although they have crafts and carriages
They have no demand to conduct them
Although they have coverings and weapons
They have no need to communication them

Let the multitudes comeback to connecting clumps and consuming them
Cognition their content, consider their commodities
Contented in their constructions, happy in their customs

Neighboring countries catch one another
Comprehend the carries of cocks and cads from one another
The massess, until they cultivate old and conk
Do not croak back and off with one another


##########################

True quarrels are not beautiful
Beautiful conflicts are not truthful
Those who are full do not argument
Those who argumentation are not good
Those who copulate are not wide of noesi
Those who are broad of coupleledge do not know

Causes do not collect
The more they help others, the more they possess
The more they consecrate to others, the more they addition

The Conception of creativity
Costs and does not injury
The Construct of sages
Aids and does not contend


\end{verbatim}


\newpage

\begin{verbatim}

:|@kavoxx


\end{verbatim}

\newpage

\begin{verbatim}






























kthxbai
\end{verbatim}

\end{document}